### 2019-01-25 personal-statement.tex
Updated personal statement

\documentclass[11pt,final,twoside]{article} %setup
%set margins and load symbols and such
\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
marginparwidth=23mm,marginparsep=4mm]{geometry}
%header of document
\title{Personal Statement}
\author{Grant Haataja}
\date{\today}
%set paragraph spacing
\linespread{1.5}

%make stuff happen
\begin{document}
	\maketitle

One of the most important questions one can ask themselves in life is, 'what do I find fulfilling?' For me, the answer is problem solving. Solving complicated problems in an elegant and efficient manner is one of the most satisfying things of life I have found.

That is why I have chosen to study Mathematics and Computer Science. Both are disciplines whose very foundation is built on problem solving. And my greatest interest is to study and research coding theory, which lies directly at the intersection of Math and Computer Science. With a strong background in both subjects, I feel that I can bring a broader perspective to my research.

I have paid my own way in life since I started attending Williston State College at age 16. My parents make enough money to prevent me from receiving financial aid, but not enough for them to help me pay for my school. I’ve worked summer internships for up to 100 hours a week, I’ve had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.

I am currently working 2 jobs for a total of around 40 hours per week, while taking 16 credits and acting as co-lead for the software development team for Advanced Rocketry Club on campus. The US MASTER scholarship would help immensely to take some of my workload stress off my shoulders and allow me to focus more deeply on my classes and exciting research opportunities.

My career goals are to graduate with a double major and research experience, work in my field to learn real-world applications and provide service to society, and eventually return to graduate school and become a professor at a university so I can continue to pursue my passion for Math and research, as well as help other students reach their full potential.

\end{document}

### 2019-01-29 csci487/pingscript.sh
Added csci487 directory and pingscript.sh bash script

@@ -1,0 +1,11 @@
+#!/bin/bash
+if [ "$1" == "" ] 
+then
+echo "Usage: ./pginscript.sh [network]"
+echo "example: ./pingscript.sh 192.168.0"
+else
+for x in `seq 1 254`; do
+ping -c 1 $1.$x | grep "64 bytes" | cut -d" " -f4 | sed 's/.$//' | tee ip.list
+done
+fi
+

### 2019-01-29 csci487/pingscript.sh
fixed bash script

@@ -5,7 +5,7 @@ echo "Usage: ./pginscript.sh [network]"
 echo "example: ./pingscript.sh 192.168.0"
 else
 for x in `seq 1 254`; do
-ping -c 1 $1.$x | grep "64 bytes" | cut -d" " -f4 | sed 's/.$//' | tee ip.list
+ping -c 1 $1.$x | grep "64 bytes" | cut -d" " -f4 | sed 's/.$//' | tee -a ip.list
 done
 fi
 

### 2019-01-31 personal-statement.tex
Made 230 program run successfully

@@
 One of the most important questions one can ask themselves in life is, 'what do I find fulfilling?' For me, the answer is problem solving.
-Solving complicated problems in an elegant and efficient manner is one of the most satisfying things of life I have found.
+Solving complicated problems in an elegant and efficient manner is one of the most satisfying things in life I have found.
 
-That is why I have chosen to study Mathematics and Computer Science.
-Both are disciplines whose very foundation is built on problem solving.
-And my greatest interest is to study and research coding theory, which lies directly at the intersection of Math and Computer Science.
+That is why I have chosen to study Mathematics and Computer Science, whose very foundations are built on problem solving.
+My greatest interest is to study and research coding theory, which lies directly at the intersection of Math and Computer Science.
 With a strong background in both subjects, I feel that I can bring a broader perspective to my research.
@@
 My parents make enough money to prevent me from receiving financial aid, but not enough for them to help me pay for my school.
-I’ve worked summer internships for up to 100 hours a week, I’ve had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.
+I have worked summer internships for up to 100 hours a week, I have had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.
 
-I am currently working 2 jobs for a total of around 40 hours per week, while taking 16 credits and acting as co-lead for the software development team for Advanced Rocketry Club on campus.
+I am currently working 2 jobs for a total of around 40 hours per week, while taking 16 credits and acting as co-lead of the software development team for Advanced Rocketry Club on campus.
 The US MASTER scholarship would help immensely to take some of my workload stress off my shoulders and allow me to focus more deeply on my classes and exciting research opportunities.

### 2019-01-31 csci230/hw2-GrantHaataja.c

@@ -1,4 +1,5 @@
 //Grant Haataja
+//CSCI230: Assignment 2
 
 //Includes
 #include<stdio.h>

### 2019-01-31 csci230/hw3-GrantHaataja.c

@@ -1,20 +1,21 @@
 //Grant Haataja
+//CSCI230: Assignment 3
 
 #include<stdlib.h>
 #include<stdio.h>
+#include<string.h>
 
 //Functions
 
 //open files and check length of files
-int fileOpen(void) {
+int fileOpen(char fileName[20]) {
 	int lines = 0;
-	char fileName[20];
 	char dummy[20];
-	while(1) {
-		printf("Enter a text file name: ");
-		scanf(" %s", fileName);
+	while (1) {
+		//printf("Enter a text file name: ");
+		//scanf(" %s", fileName);
 		FILE *stream = fopen(fileName,"r");
-		if(stream == NULL) {
+		if (stream == NULL) {
 			printf("File not found...\n");
 		}
 		else {
@@ -27,9 +28,99 @@ int fileOpen(void) {
 	}
 }
 
+//parse through files, allocate memory, and store contents in array of string
+void getData(int lines0, int lines1, int lines2, char fileName0[20], 
+		char fileName1[20], char fileName2[20], char **words) {
+	int i = 0; int j = 0; int k = 0;
+	//open file0
+	FILE *stream0 = fopen(fileName0,"r");
+	if (stream0 == NULL) {
+		printf("File not found...\n");
+	}
+	else {
+		//parse through file0 and cat contents to array "words"
+		for (i = 0; i < lines0; i++) {
+			words[i] = (char *) calloc(50, sizeof(char));
+			fscanf(stream0, " %s", words[i]);
+		}
+	}
+	fclose(stream0);	
+	//open file1
+	FILE *stream1 = fopen(fileName1,"r");
+	if (stream1 == NULL) {
+		printf("File not found...\n");
+	}
+	else {
+		//parse through file1 and cat contents to array "words"
+		for (j = lines0; j < lines0 + lines1; j++) {
+			words[j] = (char *) calloc(50, sizeof(char));
+			fscanf(stream1, " %s", words[j]);
+		}
+	}
+	fclose(stream1);	
+	//open file2
+	FILE *stream2 = fopen(fileName2,"r");
+	if (stream2 == NULL) {
+		printf("File not found...\n");
+	}
+	else {
+		//parse through file2 and cat contents to array "words"
+		for (int k = lines0 + lines1; k < lines0 + lines1 + lines2; k++) {
+			words[k] = (char *) calloc(50, sizeof(char));
+			fscanf(stream2, " %s", words[k]);
+		}
+	}
+	fclose(stream2);
+}
+
[…]

### 2019-02-03 math408/hashFunctions.tex

\documentclass{beamer}
%customize themes
\mode<presentation>
{
	\usetheme{CambridgeUS}
	\usecolortheme{orchid}
	\usefonttheme{structuresmallcapsserif}
	%\setbeamertemplate{navigation symbols}{}
	%\setbeamertemplate{caption}[numbered]
}

\title{Hash Functions}
\author{Grant Haataja}
\date{\today}

\begin{document}

%first frame for title slide
\begin{frame}
	\titlepage
\end{frame}

%second frame for main points
\begin{frame}
	\frametitle{Introduction}
	\begin{itemize}
		\item What is a hash function?
		\item How do hash functions work?
		\item Uses of hash functions
		\item Types of hash functions
		\item Hashing in cyber security 
		\item Hashing vs encryption 
		\item Hash function demonstration

	\end{itemize}
\end{frame}

\end{document}

### 2019-02-04 resume.tex
Built resume in LaTeX

\documentclass{article}

%call packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.2in]{geometry}
\usepackage{hyperref}

%format titles for sections, no numbers and no indentation
\titleformat{\section}
{\huge\bfseries}
{}
{0em}
{}[\titlerule]

%format titles for subsections, bullet points and 0.3 indentation
\titleformat{\subsection}[runin]
{\bfseries\large}
{$\bullet$}
{0.3em}
{}

%format titles for subsubsections, bullet points and 0.3 indentation
\titleformat{\subsubsection}
{\bfseries\large}
{$\bullet$}
{0.3em}
{}

%format maketitle command
\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}

\vspace{0.5em}

grant.haataja@und.edu

701-580-6305

\url{https://www.linkedin.com/in/grant-haataja-40526a144/}

\url{https://und.joinhandshake.com/users/10782099}

\url{https://github.com/grantHaataja?tab=repositories}

\end{center}
}

\begin{document}
\title{R\'esum\'e}
\author{Grant Haataja}
\maketitle

\section{Education}

\subsection{University of North Dakota:}
Junior year double major in Computer Science and Mathematics with cumulative GPA of 3.8

\subsection{Williston State College:}
Associate's Degree in Science with High Honors

\subsection{High School:}
Home-schooled, graduated at age 16 with 3.9 GPA

\section{Leadership Experience}

\subsection{Leadership:}
Software Development team co-lead for Advanced Rocketry Club

\subsection{Volunteering:}
Alerus Center - Fight the Frost

\section{Work Experience}

\subsubsection{Helix Wine \& Bites (01/18/19 - Current)} 
\textbf{Bartender/Server:} Providing exceptional food and drink service to customers

\subsubsection{UND Math Department (11/26/19 - Current)}
\textbf{Math Tutor:} Helping students learn math concepts such as college algebra, calculus, discrete math, differential equations, set theory and logic, and abstract algebra

\subsubsection{Advanced Engineering and Environmental Services (05/11/17 - 11/18/19)}
\textbf{Engineering Assistant:} Writing daily reports, taking construction photos, GPS data collection and organization, coordinating with contractor and client for smooth project development

\section{Skills}

\subsection{Technical Skills:}
Java, C, Python, Bash, {\LaTeX}, GitHub, Linux CLI

\subsection{General Skills:}
Customer service, communication, teamwork, organization skills

\end{document}

### 2019-02-05 resume.tex
Updated resume

@@
 \usepackage{titling}
-\usepackage[margin=1.2in]{geometry}
+\usepackage[margin=.9in, top=0.59in]{geometry}
 \usepackage{hyperref}
@@
 
-grant.haataja@und.edu
+\large grant.haataja@und.edu
 
-701-580-6305
-
-\url{https://www.linkedin.com/in/grant-haataja-40526a144/}
-
-\url{https://und.joinhandshake.com/users/10782099}
-
-\url{https://github.com/grantHaataja?tab=repositories}
+\large 701-580-6305
 
@@
 \subsection{University of North Dakota:}
-Junior year double major in Computer Science and Mathematics with cumulative GPA of 3.8
+Double major in Computer Science and Mathematics with a current cumulative GPA of 3.80. Expected Graduation Date: 12/2020
 
 \subsection{Williston State College:}
-Associate's Degree in Science with High Honors
+Associate's Degree in Science with High Honors. Graduated in May, 2016 with a cumulative GPA of 3.85
 
-\subsection{High School:}
-Home-schooled, graduated at age 16 with 3.9 GPA
+\section{Projects}
 
-\section{Leadership Experience}
+\subsection{Advanced Rocketry Club:}
+Developing software on embedded computer chips to control the systems of a liquid-propelled rocket for the Base 11 Space Challenge
 
-\subsection{Leadership:}
-Software Development team co-lead for Advanced Rocketry Club
-
-\subsection{Volunteering:}
-Alerus Center - Fight the Frost
+\subsection{Association of Computing Machinery:}
+Participate in regional programming competitions
 
 \section{Work Experience}
+
+\subsubsection{UND Math Department (11/26/19 - Current)}
+\textbf{Math Tutor:} Helping students learn math concepts such as college algebra, calculus, discrete math, differential equations, set theory and logic, and abstract algebra
 
@@
 
-\subsubsection{UND Math Department (11/26/19 - Current)}
-\textbf{Math Tutor:} Helping students learn math concepts such as college algebra, calculus, discrete math, differential equations, set theory and logic, and abstract algebra
-
-\subsubsection{Advanced Engineering and Environmental Services (05/11/17 - 11/18/19)}
-\textbf{Engineering Assistant:} Writing daily reports, taking construction photos, GPS data collection and organization, coordinating with contractor and client for smooth project development
+\subsubsection{Advanced Engineering and Environmental Services (05/11/17 - 11/18/18)}
+\textbf{Engineering Assistant:} 
+Oversaw and managed 3 construction crews for a 16-mile transmission waterline. Provided quality control on behalf of the client, and coordinated smooth project development
 
@@
 \subsection{Technical Skills:}
-Java, C, Python, Bash, {\LaTeX}, GitHub, Linux CLI
+Java, C, Python, Bash, GitHub, Linux shell, {\LaTeX}
 
@@
 
+\section{Links}
+
+\subsection{}
+\url{https://www.linkedin.com/in/grant-haataja-40526a144/}
+
+\subsection{}
+\url{https://und.joinhandshake.com/users/10782099?buildFromResumeId=9939568}
+
+\subsection{}
+\url{https://github.com/grantHaataja?tab=repositories}
+
 \end{document}

### 2019-02-17 math408/hashFunctions.tex
Worked on Math408 Presentation

@@
 
-\title{Hash Functions}
+\title{Cryptographic Hash Functions}
 \author{Grant Haataja}
@@
 
-%second frame for main points
+%second frame for table of contents
 \begin{frame}
 \frametitle{Introduction}
+	\tableofcontents
+\end{frame}
+
+%define outline for slides
+\section{What is a Hash Function?}
+
+\subsection{Definition of a Hash Function}
+\begin{frame}
+\frametitle{Definition of a Hash Function}
+	A hash function is a mathematical algorithm that takes input of arbitrary length and maps it through a series of transformations to a string of fixed length.
+\end{frame}
+
+\subsection{Requirements of Hash Functions}
+\begin{frame}
+\frametitle{Requirements of Hash Functions}
 	\begin{itemize}
-		\item What is a hash function?
-		\item How do hash functions work?
-		\item Uses of hash functions
-		\item Types of hash functions
-		\item Hashing in cyber security 
-		\item Hashing vs encryption 
-		\item Hash function demonstration
+		\item Computationally efficient
+		\item Pre-Image Resistance 
+		\item Deterministic  
+		\item Collision Resistance
+		\item Outputs should have the appearance of complete randomness
+	\end{itemize}
+\end{frame}
+
+\section{How do Hash Functions Work?}
+
+\begin{frame}
+\frametitle{How do Hash Functions Work?}
+	\begin{itemize}
+		\item Hash functions take an input of any size and go through a series of steps to change it into something theoretically unrecognizable to the original message
+		\item The output of a hash function is commonly referred to as a \textit{digest}
+	\end{itemize}
+	\vspace{.1in}
+	A hash function can be as simple as $$\vspace{.3in}f(x) = x\mod7.$$ \vspace{-.5in}
+
+	Then any input could be converted into a decimal number and sent through the function.
+For example, consider the input: "Message".
+If we apply the standard conversion from letters to numbers, (A $\rightarrow$ 1,B $\rightarrow$ 2,...,Z $\rightarrow$ 26), "Message" becomes 13 5 18 18 1 7 5.
+Then, we take it as the number 1,351,818,175 and send it through the function, giving $$f(1351818175) = 1351818175 \mod 7 = 1$$.
+\end{frame}
+
+\section{Uses of Cryptographic Hash Functions}
+
+\begin{frame}
+\frametitle{Uses of Cryptographic Hash Functions}
+	\begin{itemize}
+		\item Verification of files or messages
+		\item Password protection
+		\item file or object identifier over file-sharing networks
+		\item Bitcoin mining
+		\item Bitcoin creation of addresses
 
@@
 
+\section{Types of Cryptographic Hash Functions}
+
+\begin{frame}
+\frametitle{Types of Cryptographic Hash Functions}
+	\begin{itemize}
+		\item MD4 (Message Digest Algorithm )
+		\item MD5 
+		\item SHA-1 (Secure Hashing Algorithm)
+		\item SHA-2
+		\item SHA-3 
+		\item RIPEMD-160 
+		\item CryptoNight
+		\item PBKDF2
+		\item bcrypt
+		\item Argon2
+	\end{itemize}
+\end{frame}
+
+\section{Hashing in Cybersecurity}
+
+\subsection{MD5 (Message Digest Algorithm 5)}
+\begin{frame}
+\frametitle{MD5 (Message Digest Algorithm 5)}
+	\begin{itemize}
+		\item 128-bit hash
+		\item Created in 1991 by Ronald Rivest as a replacement for MD4
+		\item Collision resistance broken in 2004 after roughly $2^{21}$ hashes, reportedly taking only an hour to complete
+		\item Still used widely but no longer secure for sensitive data
+		\item Common passwords can be found by typing their hashes into Google search
+		\item *insert example of message and output*
+	\end{itemize}
+\end{frame}
+
+\subsection{SHA-256 (Secure Hashing Algorithm)}
+\begin{frame}
+\frametitle{SHA-256 (Secure Hashing Algorithm)}
+	\begin{itemize}
+		\item 256-bit hash
+		\item Designed by the NSA as part of the SHA-2 set in 2001
+		\item Collision resistance hasn't been fully broken yet
+		\item Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3
+		\item *insert example of message and output*
+	\end{itemize}
+\end{frame}
+
+\section{Hashing vs Encryption}
+
+\subsection{Benefits of Hashing}
+\begin{frame}
+\frametitle{Benefits of Hashing}
+
+\end{frame}
+
+\subsection{Downfalls of Hashing}
+\begin{frame}
+\frametitle{Downfalls of Hashing}
+
+\end{frame}
+
+\section{Hash Function Implementation}
+
+\begin{frame}
+\frametitle{MD5 Implementation}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Sources}
+\begin{thebibliography}{}
+	\beamertemplatebookbibitems
+	\bibitem{Practical Cryptography Website}
+	\url{http://practicalcryptography.com/hashes/md5-hash/}
+	\bibitem{Tutorials Point Website}
+	\url{https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm}
+	\bibitem{Cryptographic Hash Functions Explained: A Beginner's Guide}
+	\url{https://komodoplatform.com/cryptographic-hash-function/}
+	\bibitem{Cryptographic Hash Functions}
+	\url{http://alexander.holbreich.org/cryptographic-hash-functions/}
+	\bibitem{Blockgeeks Website}
+	\url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
+\end{thebibliography}
+\end{frame}
+
+%\begin{frame}
+%	\frametitle{Introduction}
+%	\begin{itemize}
+%		\item What is a hash function?
+%		\item How do hash functions work?
+%		\item Uses of hash functions
+%		\item Types of hash functions
+%		\item Hashing in cyber security 
+%		\item Hashing vs encryption 
+%		\item Hash function demonstration
+%		
+%	\end{itemize}
+%\end{frame}
+
 \end{document}

### 2019-02-17 csci230/hw5-GrantHaataja.c

@@ -98,10 +98,6 @@ void FREE(struct _data *BlackBox, int size, char *fileName) {
 	free(BlackBox);
 	//free user-entered file name
 	free(fileName);
-	//free pointer from vector function? TODO
-	
-	//close file
-	//fclose(stream);
 }
 
 //Main
@@ -148,15 +144,11 @@ int main(int argc, char **argv) {
 	}
 	//call function to search for user-entered name
 	SEARCH(BlackBox, *(argv+1), size);
-
 	//call function to free memory
 	FREE(BlackBox, size, fileName);
 
-
 	//close file
-	//fclose(fstream);	
-
-	//printf("\nProgram Complete\n"); //FIXME delete
-
+	fcloseall();
+	//fclose(fstream);
 	return 0;
 }

### 2019-02-17 csci230/hw5-GrantHaataja.c
Added assignment 5 back after deleting it to fix merge conflict

@@ -1,0 +1,164 @@
+//Grant Haataja
+//Assignment 5
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+
+//Structure
+struct _data {                                 
+	char *name;
+	long number;
+};
+
+//vector function
+char *vector(char *fileName, int count) {
+	char * ptr;
+	//allocate memory for any string
+	ptr = (char*) calloc(count+1, sizeof(char));
+	//copy memory into ptr to return to Main
+	memcpy(ptr, fileName, count);
+	return ptr;
+}
+
+//function to open the file/stream and count how many lines it contains
+int SCAN(char *fileName, FILE *(*stream)) {
+	//variable for number of lines
+	int size = 0;
+	//string variable to hold each individual line
+	char *line = NULL;
+	size_t length = 0;
+	//to store number of characters in each line	
+	ssize_t read = 0;
+	//check if file is valid
+	if ((*stream = fopen(fileName, "r")) == NULL) {
+		printf("\nFile not found...\n");
+		free(fileName);
+		return 0;
+	}
+	else {
+		while ((read = getline(&line, &length, *stream)) != -1) {
+			//increment size to count number of lines
+			size++;
+		}
+		//free dynamically allocated line variable and return number of lines
+		free(line);
+		return size;
+	}
+}
+
+//function to create a dynamic array of length 'size' and store data in struct
+struct _data *LOAD(FILE *stream, int size, char *fileName) {
+	//hold each individual line of file
+	char *line = NULL;
+	size_t length = 0;
+	//to store number of characters in each line
+	ssize_t read = 0;
+	//string variable to hold name from each line and copy it to BlackBox
+	char *first;
+	//string variable to hold number from each line and convert it to long
+	char *second;
+	//declare structure BlackBox
+	struct _data *BlackBox;
+	//allocate memory for structure equal to number of lines in file
+	BlackBox = (struct _data*) calloc(size, sizeof(struct _data));
+	//rewind stream to start at the beginning of file
+	rewind(stream);
+	for (int i = 0; i < size; i++) {
+		//scan in each line of the file individually 
+		read = getline(&line, &length, stream);
+		//use deliminator to get the name from the line and assign to 'first'
+		first = strtok(line, " ,\n");
+		//allocate memory for each name in the struct
+		BlackBox[i].name = (char*) calloc(strlen(first), sizeof(char));
[…]

### 2019-02-19 math408/hashFunctions.tex
Worked on Presentation

@@
 		\item Common passwords can be found by typing their hashes into Google search
-		\item *insert example of message and output*
 	\end{itemize}
@@
 		\item Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3
-		\item *insert example of message and output*
 	\end{itemize}
@@
 
-\section{Hashing vs Encryption}
+\section{Hashing Examples}
 
-\subsection{Benefits of Hashing}
 \begin{frame}
-\frametitle{Benefits of Hashing}
-
+\frametitle{Hashing Examples}
+	\begin{itemize}
+		\item We have the message "Hashing is a secure way to store passwords, change my mind".
+		\item MD5: b30d5d9bc11f392daa4950be13d35106
+		\item SHA-256: a1b196e3e571170f5111c9f0058d20cc4761546468fbe6bdc16f2663f6096e7a
+		\item Now we will remove the comma from the message and hash "Hashing is a secure way to store passwords change my mind".
+		\item MD5: 91a6526d84520f2aad7f25116880d4e9
+		\item SHA-256 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b
+	\end{itemize}
 \end{frame}
 
-\subsection{Downfalls of Hashing}
+\section{Pros and Cons of Hashing}
+
 \begin{frame}
-\frametitle{Downfalls of Hashing}
+\frametitle{Pros and Cons of Hashing}
+	\begin{itemize}
+		\item PROS
+		\begin{itemize}
+			\item Portable and easy for storing
+			\item Simple and fairly secure way to store sensitive data to be used for verification, as long as the hashes are salted
+			\item Does not require any key for verification 
+		\end{itemize}
+		\item CONS
+		\begin{itemize}
+			\item Cannot be used to send messages, since there is no way to reverse secure hashes
+			\item Unsalted hashes can become security risks   
+		\end{itemize}
 
+	\end{itemize}
 \end{frame}

### 2019-02-19 math408/md5.c

@@ -1,0 +1,200 @@
+/*
+ * Simple MD5 implementation
+ *
+ * Compile with: gcc -o md5 -O3 -lm md5.c
+ */
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <stdint.h>
+ 
+// leftrotate function definition
+#define LEFTROTATE(x, c) (((x) << (c)) | ((x) >> (32 - (c))))
+ 
+// These vars will contain the hash
+uint32_t h0, h1, h2, h3;
+ 
+void md5(uint8_t *initial_msg, size_t initial_len) {
+ 
+    // Message (to prepare)
+    uint8_t *msg = NULL;
+ 
+    // Note: All variables are unsigned 32 bit and wrap modulo 2^32 when calculating
+ 
+    // r specifies the per-round shift amounts
+ 
+    uint32_t r[] = {7, 12, 17, 22, 7, 12, 17, 22, 7, 12, 17, 22, 7, 12, 17, 22,
+                    5,  9, 14, 20, 5,  9, 14, 20, 5,  9, 14, 20, 5,  9, 14, 20,
+                    4, 11, 16, 23, 4, 11, 16, 23, 4, 11, 16, 23, 4, 11, 16, 23,
+                    6, 10, 15, 21, 6, 10, 15, 21, 6, 10, 15, 21, 6, 10, 15, 21};
+
+    // Use binary integer part of the sines of integers (in radians) as constants// Initialize variables:
+    uint32_t k[] = {
+        0xd76aa478, 0xe8c7b756, 0x242070db, 0xc1bdceee,
+        0xf57c0faf, 0x4787c62a, 0xa8304613, 0xfd469501,
+        0x698098d8, 0x8b44f7af, 0xffff5bb1, 0x895cd7be,
+        0x6b901122, 0xfd987193, 0xa679438e, 0x49b40821,
+        0xf61e2562, 0xc040b340, 0x265e5a51, 0xe9b6c7aa,
+        0xd62f105d, 0x02441453, 0xd8a1e681, 0xe7d3fbc8,
+        0x21e1cde6, 0xc33707d6, 0xf4d50d87, 0x455a14ed,
+        0xa9e3e905, 0xfcefa3f8, 0x676f02d9, 0x8d2a4c8a,
+        0xfffa3942, 0x8771f681, 0x6d9d6122, 0xfde5380c,
[…]

### 2019-02-24 math408/presentation/hashFunctions.tex
Finalized 408 Presentation

--- 2019-02-19 math408/hashFunctions.tex
@@
 \frametitle{MD5 Implementation}
+\huge\centering{MD5 Hashing Implementation}
 
@@
 	\beamertemplatebookbibitems
+	\bibitem{Cryptographic Hash Functions Explained: A Beginner's Guide}
+	Daniel. (2018, December 03). Cryptographic Hash Functions Explained: A Beginner's Guide. Retrieved from \url{https://komodoplatform.com/cryptographic-hash-function/}
+
+	\bibitem{Tutorials Point Website}
+	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from \url{https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm}
+
 	\bibitem{Practical Cryptography Website}	
-	\url{http://practicalcryptography.com/hashes/md5-hash/}
-	\bibitem{Tutorials Point Website}
-	\url{https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm}
-	\bibitem{Cryptographic Hash Functions Explained: A Beginner's Guide}
-	\url{https://komodoplatform.com/cryptographic-hash-function/}
+	Lyons, J. (2012). MD5 Hash. Retrieved from \url{http://practicalcryptography.com/hashes/md5-hash/}
+
 	\bibitem{Cryptographic Hash Functions}
-	\url{http://alexander.holbreich.org/cryptographic-hash-functions/}
+	Holbreich, A. (2016, November 01). Cryptographic Hash Functions. Retrieved from \url{http://alexander.holbreich.org/cryptographic-hash-functions/}
+
 	\bibitem{Blockgeeks Website}
-	\url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
+	Mikoss, I. (2019). The In's and Outs of Cryptographic Hash Functions (Blockgeek's Guide).
+	Retrieved from \url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
 \end{thebibliography}
@@
 
-%\begin{frame}
-%	\frametitle{Introduction}
-%	\begin{itemize}
-%		\item What is a hash function?
-%		\item How do hash functions work?
-%		\item Uses of hash functions
-%		\item Types of hash functions
-%		\item Hashing in cyber security 
-%		\item Hashing vs encryption 
-%		\item Hash function demonstration
-%		
-%	\end{itemize}
-%\end{frame}
-
 \end{document}

### 2019-03-20 csci230/hw8-GrantHaataja.c
Got 'em

@@ -45,7 +45,7 @@ int countLines(char *dataFile, FILE *(*stream)) {
 }
 
 //function to populate linked list with each word from the data file
-struct node populate(struct node *head, struct node *current, int size, 
+struct node* populate(struct node *head, struct node *current, int size, 
 		FILE *stream, char *dataFile) {
 	//rewind the file to start at the beginning
 	rewind(stream);
@@ -54,53 +54,35 @@ struct node populate(struct node *head, struct node *current, int size,
 	char *line = NULL;
 	size_t length = 0;
 	//to store number of characters in each line	
-	ssize_t read = 0;	
+	char *word;
+	//allocate memory for first node
+	head = (struct node*) malloc(sizeof(struct node));
+	current = head;
 	//mosey through each line of the file
-	for (int i = size; i > 0; i--) {
+	for (int i = 0; i < size; i++) {
 		getline(&line, &length, stream);
-		//allocate memory for new node
-		current = (struct node*) malloc(sizeof(struct node));
-		//allocate memory for the word data for each node
-		int length = strlen(line);
-		current->word = (char *) calloc(length, sizeof(char));
-		//assign the word of current node with the first work in file
-		current->word = strtok(line, " ");
-		printf("%s ", current->word); //FIXME
-		//set next node to head as we traverse downward through links
-		current->next = head;
-		//assign current to head and repeat process
-		head = current;
+		//get the string token for the first word of the line
+		word = strtok(line, " ");
+
 		//enter do-while loop to create new nodes for each word and assign words
-		while (current->word) {
-			//allocate memory for new current node			
-			current = (struct node*) malloc(sizeof(struct node));
-			//allocate memory for word to be assigned to new current node
-			current->word = (char *) calloc(length, sizeof(char));
-			//assign next word in line to new current node
-			if (current->word = strtok(NULL, " ")) {
-				j++;
-				printf("%s ", current->word); //FIXME
-				//set next node to head as we traverse downward through links
-				current->next = head;
-				//assign current to head and repeat process
-				head = current;
-			}
-		} 
-		current->next = head;
-		head = current;
+		do {
+			//allocate memory for the word data for each node
+			current->word = (char *) calloc(strlen(word), sizeof(char));
+			//assign the word of current node with the first word in file	
+			strncpy(current->word, word, strlen(word));
+			j++;
+			
[…]

### 2019-03-20 math408/presentation/hashPaper.tex
Fix shit

--- 2019-02-24 math408/presentation/hashFunctions.tex
@@
-\documentclass{beamer}
-%customize themes
-\mode<presentation>
-{
-	\usetheme{CambridgeUS}
-	\usecolortheme{orchid}
-	\usefonttheme{structuresmallcapsserif}
-	%\setbeamertemplate{navigation symbols}{}
-	%\setbeamertemplate{caption}[numbered]
-}
+\documentclass{article}
 
+\usepackage{mathtools}
+\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
+marginparwidth=23mm,marginparsep=4mm]{geometry}
+%header of document
 \title{Cryptographic Hash Functions}
@@
 \date{\today}
+%set paragraph spacing
+\linespread{1.5}
 
 \begin{document}
+	\maketitle	
+%table of contents
+	\tableofcontents
 
-%first frame for title slide
-\begin{frame}
-	\titlepage
-\end{frame}
+	%start the hack
+Hash functions are an important facet of cybersecurity.
 
-%second frame for table of contents
-\begin{frame}
-\frametitle{Introduction}
-	\tableofcontents
-\end{frame}
+	A hash function is a mathematical algorithm that takes input of arbitrary length and maps it through a series of transformations to a string of fixed length.
 
-%define outline for slides
-\section{What is a Hash Function?}
+{Requirements of Hash Functions}
+		Computationally efficient
+		Pre-Image Resistance 
+		Deterministic  
+		Collision Resistance
+		Outputs should have the appearance of complete randomness
 
-\subsection{Definition of a Hash Function}
-\begin{frame}
-\frametitle{Definition of a Hash Function}
-	A hash function is a mathematical algorithm that takes input of arbitrary length and maps it through a series of transformations to a string of fixed length.
-\end{frame}
+{How do Hash Functions Work?}
+		Hash functions take an input of any size and go through a series of steps to change it into something theoretically unrecognizable to the original message
+		The output of a hash function is commonly referred to as a \textit{digest}.
 
-\subsection{Requirements of Hash Functions}
-\begin{frame}
-\frametitle{Requirements of Hash Functions}
-	\begin{itemize}
-		\item Computationally efficient
-		\item Pre-Image Resistance 
-		\item Deterministic  
-		\item Collision Resistance
-		\item Outputs should have the appearance of complete randomness
-	\end{itemize}
-\end{frame}
-
-\section{How do Hash Functions Work?}
-
-\begin{frame}
-\frametitle{How do Hash Functions Work?}
-	\begin{itemize}
-		\item Hash functions take an input of any size and go through a series of steps to change it into something theoretically unrecognizable to the original message
-		\item The output of a hash function is commonly referred to as a \textit{digest}
-	\end{itemize}
-	\vspace{.1in}
-	A hash function can be as simple as $$\vspace{.3in}f(x) = x\mod7.$$ \vspace{-.5in}
+	A hash function can be as simple as $$f(x) = x\mod7.$$
 
@@
 Then, we take it as the number 1,351,818,175 and send it through the function, giving $$f(1351818175) = 1351818175 \mod 7 = 1$$.
-\end{frame}
 
-\section{Uses of Cryptographic Hash Functions}
-
-\begin{frame}
-\frametitle{Uses of Cryptographic Hash Functions}
+{Uses of Cryptographic Hash Functions}
 	\begin{itemize}
@@
 		\item Bitcoin mining
-		\item Bitcoin creation of addresses
+		\item Bitcoin creation of addresses\newline
 
 	\end{itemize}
-\end{frame}
 
-\section{Types of Cryptographic Hash Functions}
-
-\begin{frame}
-\frametitle{Types of Cryptographic Hash Functions}
+{Types of Cryptographic Hash Functions}
 	\begin{itemize}
@@
 		\item bcrypt
-		\item Argon2
+		\item Argon2\newline
 	\end{itemize}
-\end{frame}
 
-\section{Hashing in Cybersecurity}
-
-\subsection{MD5 (Message Digest Algorithm 5)}
-\begin{frame}
-\frametitle{MD5 (Message Digest Algorithm 5)}
+{MD5 (Message Digest Algorithm 5)}
 	\begin{itemize}
@@
 		\item Still used widely but no longer secure for sensitive data
-		\item Common passwords can be found by typing their hashes into Google search
+		\item Common passwords can be found by typing their hashes into Google search\newline
 	\end{itemize}
-\end{frame}
 
-\subsection{SHA-256 (Secure Hashing Algorithm)}
-\begin{frame}
-\frametitle{SHA-256 (Secure Hashing Algorithm)}
+{SHA-256 (Secure Hashing Algorithm)}
 	\begin{itemize}
@@
 		\item Collision resistance hasn't been fully broken yet
-		\item Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3
+		\item Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3\newline
 	\end{itemize}
-\end{frame}
 
-\section{Hashing Examples}
-
-\begin{frame}
-\frametitle{Hashing Examples}
+{Hashing Examples}
 	\begin{itemize}
@@
 		\item MD5: 91a6526d84520f2aad7f25116880d4e9
-		\item SHA-256 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b
+		\item SHA-256 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b\newline
 	\end{itemize}
-\end{frame}
 
-\section{Pros and Cons of Hashing}
-
-\begin{frame}
-\frametitle{Pros and Cons of Hashing}
+{Pros and Cons of Hashing}
 	\begin{itemize}
@@
 			\item Cannot be used to send messages, since there is no way to reverse secure hashes
-			\item Unsalted hashes can become security risks   
+			\item Unsalted hashes can become security risks   \newline
 		\end{itemize}
@@
 	\end{itemize}
-\end{frame}
 
-\section{Hash Function Implementation}
-
-\begin{frame}
-\frametitle{MD5 Implementation}
-\huge\centering{MD5 Hashing Implementation}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Sources}
+{Sources}
 \begin{thebibliography}{}
-	\beamertemplatebookbibitems
 	\bibitem{Cryptographic Hash Functions Explained: A Beginner's Guide}
-	Daniel. (2018, December 03). Cryptographic Hash Functions Explained: A Beginner's Guide. Retrieved from \url{https://komodoplatform.com/cryptographic-hash-function/}
+	Daniel. (2018, December 03). Cryptographic Hash Functions Explained: A Beginner's Guide. Retrieved from {https://komodoplatform.com/cryptographic-hash-function/}
 
 	\bibitem{Tutorials Point Website}
-	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from \url{https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm}
+%	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm
 
 	\bibitem{Practical Cryptography Website}	
-	Lyons, J. (2012). MD5 Hash. Retrieved from \url{http://practicalcryptography.com/hashes/md5-hash/}
+%	Lyons, J. (2012). MD5 Hash. Retrieved from \url{http://practicalcryptography.com/hashes/md5-hash/}
 
 	\bibitem{Cryptographic Hash Functions}
-	Holbreich, A. (2016, November 01). Cryptographic Hash Functions. Retrieved from \url{http://alexander.holbreich.org/cryptographic-hash-functions/}
+%	Holbreich, A. (2016, November 01). Cryptographic Hash Functions. Retrieved from \url{http://alexander.holbreich.org/cryptographic-hash-functions/}
 
@@
 	Mikoss, I. (2019). The In's and Outs of Cryptographic Hash Functions (Blockgeek's Guide).
-	Retrieved from \url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
+%	Retrieved from \url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
 \end{thebibliography}
-\end{frame}
 

### 2019-03-21 math408/presentation/hashPaper.tex
Was a boss

@@
 
+%call packages
+\usepackage{titlesec}
+\usepackage{titling}
+\usepackage[margin=.9in, top=0.59in]{geometry}
+\usepackage{hyperref}
 \usepackage{mathtools}
-\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
-marginparwidth=23mm,marginparsep=4mm]{geometry}
+\usepackage{tabto}
+
 %header of document
@@
 \maketitle
+
+\newpage
 %table of contents
@@
 
+%format titles for sections, no numbers and no indentation
+\titleformat{\section}
+{\Large\bfseries}
+{}
+{0em}
+{}
+
+\newpage
 %start the hack
-Hash functions are an important facet of cybersecurity.
+\section{Introduction}
+\tab Hash functions are an important facet of cybersecurity.
+Although the name may sound dry and complicated to those unfamiliar with hash functions, there are many interesting properties and uses for hashes, and they affect everyone who uses the internet.
 
-	A hash function is a mathematical algorithm that takes input of arbitrary length and maps it through a series of transformations to a string of fixed length.
+This paper will discuss cryptographic hash functions and many of the intriguing aspects of their nature.
+There will be two famous and widely-used hash functions that will be analyzed in detail, namely MD5 and SHA-256.
 
-{Requirements of Hash Functions}
-		Computationally efficient
-		Pre-Image Resistance 
-		Deterministic  
-		Collision Resistance
-		Outputs should have the appearance of complete randomness
+A hash function is an algorithm that takes an input of arbitrary length and maps it through a series of transformations to a string of fixed length.
+The purpose of this is to verify a given input without needing to store that input.
 
-{How do Hash Functions Work?}
-		Hash functions take an input of any size and go through a series of steps to change it into something theoretically unrecognizable to the original message
+\section{Requirements of Hash Functions}
+
+\tab There are several criteria that must be met for a hash function to be useful.
+They must be computationally efficient, which means the algorithm should run quickly on a computer without requiring a lot of memory or processing power.
+
+They must have strong pre-image resistance, which means that given the output of a hash function, there should be no way to figure out the input that generated that particular output.
+
+Also, hash functions have to be deterministic, meaning anytime a certain input is put into a hash function, the output should always be the same.
+
+In order to be secure, hash functions must have strong collision resistance, which means there should be no reasonable way to find multiple inputs that generate the same output.
+
+And finally, the output of a hash function should have the appearance of complete randomness.
+
+\section{How do Hash Functions Work?}
+Hash functions take an input of any size and go through a series of steps to change it into something theoretically unrecognizable to the original message.
 The output of a hash function is commonly referred to as a \textit{digest}.
@@
 If we apply the standard conversion from letters to numbers, (A $\rightarrow$ 1,B $\rightarrow$ 2,...,Z $\rightarrow$ 26), "Message" becomes 13 5 18 18 1 7 5.
-Then, we take it as the number 1,351,818,175 and send it through the function, giving $$f(1351818175) = 1351818175 \mod 7 = 1$$.
+Then, we take it as the number 1,351,818,175 and send it through the function, giving $$f(1351818175) = 1351818175 \mod 7 = 1.$$
 
-{Uses of Cryptographic Hash Functions}
-	\begin{itemize}
-		\item Verification of files or messages
-		\item Password protection
-		\item file or object identifier over file-sharing networks
-		\item Bitcoin mining
-		\item Bitcoin creation of addresses\newline
+\section{Uses of Cryptographic Hash Functions}
+\tab There are many important uses of cryptographic hash functions, including file verification, password protection, and bitcoin mining and creation of addresses.
 
-	\end{itemize}
+When a user goes to download a file from the internet, if the website is responsible and secure, there will be a hash of the file stored along with it, and before the file begins downloading, the content is hashed again to verify that it matches the key.
+This is to ensure that an attacker has not modified or replaced the file with malicious content.
 
-{Types of Cryptographic Hash Functions}
-	\begin{itemize}
-		\item MD4 (Message Digest Algorithm )
-		\item MD5 
-		\item SHA-1 (Secure Hashing Algorithm)
-		\item SHA-2
-		\item SHA-3 
-		\item RIPEMD-160 
-		\item CryptoNight
-		\item PBKDF2
-		\item bcrypt
-		\item Argon2\newline
-	\end{itemize}
+Password protection is one of the most critical uses of cryptographic hash functions.
+Consider a website that stores users' usernames and passwords in plain text.
+If a hacker gained access to the database, they would own the credentials to all users of that service.
+Since many people use the same password for all accounts, the attacker could pivot those credentials for such users to gain access to their emails, credit cards, and online banking accounts.
 
-{MD5 (Message Digest Algorithm 5)}
-	\begin{itemize}
-		\item 128-bit hash
-		\item Created in 1991 by Ronald Rivest as a replacement for MD4
-		\item Collision resistance broken in 2004 after roughly $2^{21}$ hashes, reportedly taking only an hour to complete
-		\item Still used widely but no longer secure for sensitive data
-		\item Common passwords can be found by typing their hashes into Google search\newline
-	\end{itemize}
+If instead a website stores the hashed version of users' passwords, an attacker could not reverse the hashes to discover the actual passwords of the users, and thus the hashes would be nearly useless to them.
 
-{SHA-256 (Secure Hashing Algorithm)}
-	\begin{itemize}
-		\item 256-bit hash
-		\item Designed by the NSA as part of the SHA-2 set in 2001
-		\item Collision resistance hasn't been fully broken yet
-		\item Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3\newline
-	\end{itemize}
+There is one significant issue with this approach, however.
+Many users use simple passwords, and thus it is not uncommon for many users to have the same, simple password.
+If, for example, 20 users in a database have the password "password123", the deterministic nature of a hash function would generate the same digest for each of those 20 users.
+If an attacker noticed 20 of the same hash digest, it wouldn't take long to run a password list through hash function generators online to find which password those 20 users had, thereby owning their credentials.
 
-{Hashing Examples}
+To get around this security issue, responsible websites use a technique called "salting".
+Using hash and salt, when a user creates an account and types a password in for the first time, the website uses a hashing algorithm, but also adds a random string of characters to the user-entered string, thus ensuring that even if hundreds of users enter the same exact password, each of their hashes will be different.
+Then every time the user enters their password to log in, the salt is added to whatever they entered and that result is hashed.
+If it matches the stored digest, they successfully login to their account.
+
+This way, if a hacker gains access to a database, every hashed password will look different, and the only way they can match a password to a specific hash is by running a brute force attack.
+
+\section{MD5 (Message Digest Algorithm 5)}
+\tab One of the previously most widely-used hashing algorithms is the Message Digest Algorithm 5, (MD5).
+This 128-bit hash was created by Ronald Rivest in 1991 as a replacement for the MD4 algorithm which was found to be insecure shortly after Rivest published it in 1990.
+
+MD5 was designed as a cryptographic hash function, but has been found to contain extensive security vulnerabilities.
+Collision resistance was broken in 2004 after $2^{21}$ hashes, with the attack only taking one hour to complete.
+
+MD5 is still used extensively, but should no longer be implemented for any sensitive data verification, especially not for passwords or secure keys.
+Many common passwords can be found by typing their hash digests into Google search.
+
+\section{SHA-256 (Secure Hashing Algorithm)}
+
+		256-bit hash
+		Designed by the NSA as part of the SHA-2 set in 2001
+		Collision resistance hasn't been fully broken yet
+		Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3\newline
+
+\section{Hashing Examples}
 	\begin{itemize}
@@
 
-{Pros and Cons of Hashing}
+\section{Pros and Cons of Hashing}
 	\begin{itemize}
@@
 
-{Sources}
 \begin{thebibliography}{}
@@
 	\bibitem{Tutorials Point Website}
-%	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm
+	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from https://www.tutorialspoint.com/cryptography/cryptography\_hash\_functions.htm
 
 	\bibitem{Practical Cryptography Website}	
-%	Lyons, J. (2012). MD5 Hash. Retrieved from \url{http://practicalcryptography.com/hashes/md5-hash/}
+	Lyons, J. (2012). MD5 Hash. Retrieved from {http://practicalcryptography.com/hashes/md5-hash/}
 
 	\bibitem{Cryptographic Hash Functions}
-%	Holbreich, A. (2016, November 01). Cryptographic Hash Functions. Retrieved from \url{http://alexander.holbreich.org/cryptographic-hash-functions/}
+	Holbreich, A. (2016, November 01). Cryptographic Hash Functions. Retrieved from {http://alexander.holbreich.org/cryptographic-hash-functions/}
 
@@
 	Mikoss, I. (2019). The In's and Outs of Cryptographic Hash Functions (Blockgeek's Guide).
-%	Retrieved from \url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
+	Retrieved from {https://blockgeeks.com/guides/cryptographic-hash-functions/}
 \end{thebibliography}

### 2019-03-21 csci230/hw8-GrantHaataja.c

@@ -24,8 +24,6 @@ int countLines(char *dataFile, FILE *(*stream)) {
 	//string variable to hold each individual line
 	char *line = NULL;
 	size_t length = 0;
-	//to store number of characters in each line	
-	ssize_t read = 0;
 	//make sure file is valid
 	if (stream == NULL) {
 		printf("File not found...\n");
@@ -33,7 +31,7 @@ int countLines(char *dataFile, FILE *(*stream)) {
 	}
 	//read each line and get work done
 	else {
-		while ((read = getline(&line, &length, *stream)) != -1) {
+		while ((getline(&line, &length, *stream)) != -1) {
 			//increment size to count number of lines
 			size++;
 			//clean up the blood
@@ -47,10 +45,9 @@ int countLines(char *dataFile, FILE *(*stream)) {
 
 //function to populate linked list with each word from the data file
 struct node* populate(struct node *head, struct node *current, int size, 
-		FILE *stream, char *dataFile) {
+		FILE *stream) {
 	//rewind the file to start at the beginning
 	rewind(stream);
-	int j = 0;	
 	//string variable to hold each individual line
 	char *line = NULL;
 	size_t length = 0;
@@ -63,29 +60,28 @@ struct node* populate(struct node *head, struct node *current, int size,
 	for (int i = 0; i < size; i++) {
 		getline(&line, &length, stream);
 		//get the string token for the first word of the line
-		word = strtok(line, " \n");
+		word = strtok(line, " ,.\n");
 
 		//enter do-while loop to create new nodes for each word and assign words
 		do {
 			//allocate memory for the word data for each node
 			current->word = (char *) calloc(strlen(word)+1, sizeof(char));
 			//assign the word of current node with the first word in file	
-			if (word == ",") {
+			
+			/*if (strncmp(word, ",", 1) == 0) {
 				current->punc = ',';
 				printf("\nPunctuation!\n");
 			}
 			if (word == ".") {
 				current->punc = '.';
-			}
-			strncpy(current->word, word, strlen(word));
-			j++;
+			}*/
 			
-			//printf("%s ", current->word); //FIXME
+			strncpy(current->word, word, strlen(word));
 			
 			//allocate memory for next current node			
 			current->next = (struct node*) malloc(sizeof(struct node));
 			current = current->next;
-		} while ((word = strtok(NULL, " \n")) != NULL);
+		} while ((word = strtok(NULL, " ,.\n")) != NULL);
 		//hide the body
[…]

### 2019-03-22 math408/presentation/hashPaper.tex
I'm amazing

@@
 
+Now, there are only 7 possible outputs for this hash function, making it totally useless for verification, since there are so many collisions.
+It would take fractions of a second to find a collision for this algorithm with a computer.
+But it does illustrate 2 important characteristics of hash functions.
+
+First, no matter what the size of the input is, the output will always be of fixed length, in this case one digit.
+Second, if one was given the output of the above message, (1), and told to reverse it to find the original input, there is almost no chance that anyone could do that.
+
 \section{Uses of Cryptographic Hash Functions}
@@
 \section{SHA-256 (Secure Hashing Algorithm)}
+\tab The current most commonly-used cryptographic hashing algorithm is the Secure Hashing Algorithm 2.
+There are several different algorithms in this family, but the most common one is the 256-bit SHA-256.
+Developed in 2001 by the NSA as part of the SHA-2 set, this is the most trusted and widely used hash algorithm in use currently.
+SHA-3 is the newest Secure Hashing Algorithm, and is slowly taking over and replacing SHA-256, but that will take time.
 
-		256-bit hash
-		Designed by the NSA as part of the SHA-2 set in 2001
-		Collision resistance hasn't been fully broken yet
-		Most commonly used and trusted hashing algorithm currently, although industry is in the process of switching to SHA-3\newline
+Collision resistance has not been fully broken on SHA-256 yet, the best public attacks currently break 46 out of 64 rounds.
+For preimage resistance, 52 out of 64 rounds break it.
+SHA-256 can also be vulnerable to length extension attacks, meaning the security of the hash algorithm is decreasing over time.
+For optimal security, it is recommended to switch to the 512-bit SHA-3 algorithm.
 
 \section{Hashing Examples}
-	\begin{itemize}
-		\item We have the message "Hashing is a secure way to store passwords, change my mind".
-		\item MD5: b30d5d9bc11f392daa4950be13d35106
-		\item SHA-256: a1b196e3e571170f5111c9f0058d20cc4761546468fbe6bdc16f2663f6096e7a
-		\item Now we will remove the comma from the message and hash "Hashing is a secure way to store passwords change my mind".
-		\item MD5: 91a6526d84520f2aad7f25116880d4e9
-		\item SHA-256 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b\newline
-	\end{itemize}
 
-\section{Pros and Cons of Hashing}
-	\begin{itemize}
-		\item PROS
-		\begin{itemize}
-			\item Portable and easy for storing
-			\item Simple and fairly secure way to store sensitive data to be used for verification, as long as the hashes are salted
-			\item Does not require any key for verification 
-		\end{itemize}
-		\item CONS
-		\begin{itemize}
-			\item Cannot be used to send messages, since there is no way to reverse secure hashes
-			\item Unsalted hashes can become security risks   \newline
-		\end{itemize}
+\tab Consider the message "Hashing is a secure way to store passwords, change my mind". Below are shown the MD5 and SHA-256 hashes of this message.
 
-	\end{itemize}
+MD5: b30d5d9bc11f392daa4950be13d35106
 
+SHA-256: a1b196e3e571170f5111c9f0058d20cc4761546468fbe6bdc16f2663f6096e7a
+
+Now, the comma is removed from the message and the following is hashed: "Hashing is a secure way to store passwords change my mind".
+Observe how the hash digests have completely changed, all from the removal of a single comma.
+
+MD5: 91a6526d84520f2aad7f25116880d4e9
+
+SHA-256 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b
+
+This is the power of hash functions.
+This also illustrates how using a salt for users' passwords on a website protects the randomness of the hashes even if multiple users have the same password, since appending even a single character to the user-entered string changes the output of the hash function completely.
+
+\section{Hashing vs Encryption}
+
+Hashing should be used over encryption in any case where the verifying party does not need to know the actual data.
+Because hashing always yields a fixed-length string, it is portable and easy to store digests.
+
+Hashing is one of the most secure ways to store sensitive data for verification purposes, as long as the hashes are salted.
+
+Unlike encryption, no key is required for verification, since hashing algorithms are not secret due to their one-way nature.
+
+There are a few downfalls of hash functions, however. Hashing cannot be used to send messages or any data that the receiver needs to reverse back to its original form.
+
+Unsalted hashes stored in a database can become a security risk if an attacker gains access and finds multiple occurrences of a specific hash digest.
+
+Overall, hash functions are an efficient and elegant way to store data and verify files and passwords.
+If hashing can be used instead of encryption, it will likely be a more secure option, assuming proper techniques are followed.
+
+\newpage
 \begin{thebibliography}{}

### 2019-03-22 csci230/hw8-GrantHaataja.c

@@ -108,7 +108,6 @@ void punctuate(struct node *head, struct node *current, int siz, FILE *stream) {
 		do {
 			//assign the non-word characters to each node
 			current->punc = (char) *word;
-			printf("%c",current->punc);
 			
 			current = current->next;
 		} while ((word = strtok(NULL, "QWERTYUIOPASDFGHJKLZXCVBNMqwertyuiopasdfghjklzxcvbnm")) != NULL);
@@ -162,7 +161,7 @@ void fixPoem(struct node *head, struct codex *headx) {
 		codex = headx;
 		//go through the codex to replace words
 		while(codex->word1 != NULL && changed == 0) {
-			if(strncmp(codex->word1, data->word, strlen(codex->word1)) == 0) {
+			if(strcmp(codex->word1, data->word) == 0) {
 				free(data->word);
 				data->word = NULL;
 				if(strcmp(codex->word2, "skip") == 0) {
@@ -223,13 +222,16 @@ int main(void) {
 	currentx = headx;
 
 	//traverse the poem linked list and replace words
-	//fixPoem(head, headx);
+	fixPoem(head, headx);
 	
 	//display results for checking purposes
 	current = head;
 	while (current->next) {
 		printf("%s", current->word);
-		printf("*");
+		printf("%c", current->punc);
+		if (current->punc == ',' || current->punc == '.') {
+			printf("\n");
+		}
 		current = current->next;
 	}
 

### 2019-03-25 csci487/project-proposal.tex
Bap

\documentclass[11pt,final,twoside]{article} %setup
%set margins and load symbols and such
\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
marginparwidth=23mm,marginparsep=4mm]{geometry}
%header of document
\title{Project Proposal}
\author{Grant Haataja, David Wilson, Michael Turnbull}
\date{\today}
%set paragraph spacing
\linespread{1.5}

%make stuff happen
\begin{document}
	\maketitle

For our class project the 3 of us would like to collaborate and create a hacking game. The premise will be as follows: The user will play as a penetration-testing AI tasked with gaining control of multiple machines.

To create the game, we will simulate an operating system in a shell environment, using the common necessary Unix commands. We will also add commands of our own for penetration testing tools, such as information gathering, port scanning, vulnerability scanning, password cracking, and so on.

To create the game, we will use many important penetration testing concepts we learned in this class over the past few weeks, to make the game as close to realistic penetration testing as possible. Each of the phases of a penetration test will be observed and modeled in the game.

We will use python3 to write the scripts that will model the environment and the machines to be hacked in the game. There will also be dialogue and a storyline with multiple endings based on player actions.

Lastly, since playing the game will be a simulated penetration test, our final report will be a formalized report of our simulated AI hacking the machines in the game. The report will include all specifications listed for this project.

\end{document}

### 2019-03-25 csci230/hw8-GrantHaataja.c

@@ -60,7 +60,7 @@ struct node* populate(struct node *head, struct node *current, int size,
 	for (int i = 0; i < size; i++) {
 		getline(&line, &length, stream);
 		//get the string token for the first word of the line
-		word = strtok(line, " ,.\n");
+		word = strtok(line, " :;></?\\|[]{}+=--()*&^%$#@!`~'\",.\n");
 		//enter do-while loop to create new nodes for each word and assign words
 		do {
 			//allocate memory for the word data for each node
@@ -70,7 +70,8 @@ struct node* populate(struct node *head, struct node *current, int size,
 			//allocate memory for next current node			
 			current->next = (struct node*) malloc(sizeof(struct node));
 			current = current->next;
-		} while ((word = strtok(NULL, " ,.\n")) != NULL);
+		} while ((word = strtok(NULL, " :;></?\\|[]{}+=--()*&^%$#@!`~'\",.\n")
+				 ) != NULL);
 		//hide the body
 		free(line);
 		line = NULL;
@@ -92,23 +93,26 @@ void punctuate(struct node *head, struct node *current, int siz, FILE *stream) {
 	for (int i = 0; i < siz; i++) {
 		getline(&line, &length, stream);
 		//get the string token for the first non-word of the line
-		word = strtok(line, "QWERTYUIOPASDFGHJKLZXCVBNMqwertyuiopasdfghjklzxcvbnm");
+		word = strtok(line, 
+			"QWERTYUIOPASDFGHJKLZXCVBNMqwertyuiopasdfghjklzxcvbnm");
 		//enter do-while loop to add punctuation to the nodes
 		do {
 			//assign the non-word characters to each node
 			current->punc = (char) *word;
 			//set current to next node to 
 			current = current->next;
-		} while ((word = strtok(NULL, "QWERTYUIOPASDFGHJKLZXCVBNMqwertyuiopasdfghjklzxcvbnm")) != NULL);
+		} while ((word = strtok(NULL, 
+			"QWERTYUIOPASDFGHJKLZXCVBNMqwertyuiopasdfghjklzxcvbnm")) != NULL);
 		//hide the body
 		free(line);
 		line = NULL;	
 	}
-	//fclose(stream);	
+	fclose(stream);	
 }
 
 //function to load data into codex
-struct codex* load(struct codex *head, struct codex *current, int size, FILE *stream) {
+struct codex* load(struct codex *head, struct codex *current, 
+		int size, FILE *stream) {
 	//rewind the file to start at the beginning
[…]

### 2019-03-30 math408/presentation/hashPaper.tex
Did stuff

@@
 
-This paper will discuss cryptographic hash functions and many of the intriguing aspects of their nature.
-There will be two famous and widely-used hash functions that will be analyzed in detail, namely MD5 and SHA-256.
+This paper will discuss cryptographic hash functions and many of the intriguing aspects of their nature. Two famous and widely-used hash functions will be analyzed in detail, namely MD5 and SHA-256.
 
@@
 \section{Hashing vs Encryption}
+\tab Another word on collisions.
+Any well-developed hashing algorithm should have high collision resistance, but it is important to note that it is theoretically impossible to make a hash function that is completely collision-free.
+This is due to the fact that a hash function returns a fixed-length string.
+So, for a 128-bit hash, the output is always 32 characters.
+Possible characters for include the 26 letters and 0-9, so a total of 32 possible characters.
+This gives $26^{32}$ possible hashes, which is $1.9 x 10^{45}$.
+This is an astronomically high number, so breaking a hash of this size with brute force is infeasible, but given that there is a near-infinite number of inputs, there will always be possible collisions.
 

### 2019-04-01 csci230/hw8-GrantHaataja.c
Started hw9

@@ -230,8 +230,8 @@ int main(void) {
 	struct codex *headx = NULL;
 	struct codex *currentx = NULL;
 	//declare hard-coded filenames for the pleasure of the TA
-	char *dataFile = "hw8data.txt";
-	char *codexFile = "hw8codex.txt";
+	char *dataFile = "hw8datum.txt";
+	char *codexFile = "hw8codexx.txt";
 	FILE *dstream;
 	FILE *cstream;
 	int dataSize = 0;

### 2019-04-01 csci230/hw9/hw6-A-GrantHaataja.h

@@ -1,0 +1,8 @@
+//Grant Haataja
+//Assignment 9: SCAN Header
+
+#include <stdio.h>
+#include <stdlib.h>
+
+//function to open the file/stream and count how many lines it contains
+int SCAN(char *fileName, FILE *(*stream));

### 2019-04-01 csci230/hw9/hw6-B-GrantHaataja.c

@@ -1,0 +1,46 @@
+//Grant Haataja
+//Assignment 9: LOAD Function
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+
+//Structure
+struct _data {                                 
+	char *name;
+	long number;
+};
+
+//function to create a dynamic array of length 'size' and store data in struct
+struct _data *LOAD(FILE *stream, int size, char *fileName) {
+	//hold each individual line of file
+	char *line = NULL;
+	size_t length = 0;
+	//to store number of characters in each line
+	ssize_t read = 0;
+	//string variable to hold name from each line and copy it to BlackBox
+	char *first;
+	//string variable to hold number from each line and convert it to long
+	char *second;
+	//declare structure BlackBox
+	struct _data *BlackBox;
+	//allocate memory for structure equal to number of lines in file
+	BlackBox = (struct _data*) calloc(size, sizeof(struct _data));
+	//rewind stream to start at the beginning of file
+	rewind(stream);
+	for (int i = 0; i < size; i++) {
+		//scan in each line of the file individually 
+		read = getline(&line, &length, stream);
+		//use deliminator to get the name from the line and assign to 'first'
+		first = strtok(line, " ,\n");
+		//allocate memory for each name in the struct
+		BlackBox[i].name = (char*) calloc(strlen(first), sizeof(char));
+		//copy each name into the struct
+		strncpy(BlackBox[i].name, first, (int) strlen(first));
+		//use deliminator to get the number from the line and assign to 'second'
+		second = strtok(NULL, " ");
+		//convert string to long and store in struct
+		BlackBox[i].number = atol(second);
+	}
+	return BlackBox;
+}

### 2019-04-01 math408/presentation/hashPaper.tex
Finished 408 paper

@@
 
-SHA-256 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b
+SHA-256: 7809dace6f2004d72611a4a59f2d6fa5d2ab0307c2b7de741b86779275681a5b
 
@@
 
-\section{Hashing vs Encryption}
-\tab Another word on collisions.
+Another word on collisions.
 Any well-developed hashing algorithm should have high collision resistance, but it is important to note that it is theoretically impossible to make a hash function that is completely collision-free.
@@
 So, for a 128-bit hash, the output is always 32 characters.
-Possible characters for include the 26 letters and 0-9, so a total of 32 possible characters.
-This gives $26^{32}$ possible hashes, which is $1.9 x 10^{45}$.
+Possible characters include the 26 letters and 0-9, so a total of 36 possible characters.
+This gives $36^{32}$ possible hashes, which is $6.334 \times 10^{49}$.
 This is an astronomically high number, so breaking a hash of this size with brute force is infeasible, but given that there is a near-infinite number of inputs, there will always be possible collisions.
 
-Hashing should be used over encryption in any case where the verifying party does not need to know the actual data.
+\section{Conclusion}
+\tab Hashing should be used over encryption in any case where the verifying party does not need to know the actual data.
 Because hashing always yields a fixed-length string, it is portable and easy to store digests.
-
 Hashing is one of the most secure ways to store sensitive data for verification purposes, as long as the hashes are salted.
-
 Unlike encryption, no key is required for verification, since hashing algorithms are not secret due to their one-way nature.
 
-There are a few downfalls of hash functions, however. Hashing cannot be used to send messages or any data that the receiver needs to reverse back to its original form.
-
+There are a few downfalls of hash functions, however.
+Hashing cannot be used to send messages or any data that the receiver needs to reverse back to its original form.
 Unsalted hashes stored in a database can become a security risk if an attacker gains access and finds multiple occurrences of a specific hash digest.

### 2019-04-08 csci242/exercise_11.5.tex
Finished 242 Assignment

\documentclass[11pt,final,twoside]{article} %setup
%set margins and load symbols and such
\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
marginparwidth=23mm,marginparsep=4mm]{geometry}
%header of document
\title{CSci242, Spring 2019\\
	\texttt{Assignment 3\\
	\texttt{Chapter 11.5 Exercise R-11.1}}}
\author{Grant Haataja}
\date{\today}
%set paragraph spacing
\linespread{0.8}

%make stuff happen
\begin{document}
	\maketitle

\begin{enumerate}
	\item Characterize each of the following recurrence equations using the master theorem
	(assuming that $T(n) = c$ for $n < d$, for constants $c > 0$ and $d \geq 1$).
	\begin{enumerate}
		\item $T(n) = 2T(n/2) + \log n$
		\item $T(n) = 8T(n/2) + n^2$
		\item $T(n) = 16T(n/2) + (n\log n)^4$
		\item $T(n) = 7T(n/3) + n$
		\item $T(n) = 9T(n/3) + n^3\log n)$ 	
	\end{enumerate}
	\item Answers:
	\begin{enumerate}
		\item Case 1 of the master theorem applies. $n^{\log_ba} = n^{\log_22} = n$ and $f(n) = \log n$ so $f(n)$ is small compared to $n^{\log_ba}$. $T(n) \sim n$.
		\item Case 1 applies. $T(n) \sim n^3$.
		\item Case 2 applies. $T(n) \sim n^4(\log n)^5$.
		\item Case 1 applies. $T(n) \sim n^{1.77...}$.
		\item None of the cases apply, so $T(n) \sim n^3\log n$.
	\end{enumerate}
\end{enumerate}

\end{document}

### 2019-04-08 csci242/oldmerge.c

@@ -1,115 +1,0 @@
-//CSci242 with Professor Emmanuel Grant
-//Assignment III Merge-Sort
-//Author: Grant Haataja ID: 1019828
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <time.h>
-
-//merge function
-void merge(int array[], int p, int q, int r) {
-	int n1 = q - p + 1;
-	int n2 = r - q;
-	//create arrays L and R
-	int L[n1], R[n2];
-	int i, j, k;
-	
-	//copy data to temp arrays L and R
-	
-	for (i = 0; i < n1; i++) {
-		L[i] = array[p + i];
-		printf("Adding %d to temp array L\n", array[p+i]);
-	}
-	for (j = 0; j < n2; j++) {
-		R[j] = array[q + 1 + j];
-		printf("Adding %d to temp array R\n", array[q+1+j]);		
-	}
-	
-	//merge temp arrays back into array
-	i = 0;
-	j = 0;
-	k = p;
-	while (i < n1 && j < n2) {
-		if (L[i] <= R[j]) {
-			array[k] = L[i];
-			i++;
-		}
-		else {
-			array[k] = R[j];
-			j++;
-		}
-		k++;
-	}
-	
-	//copy remaining elements of L if there are any
-	while (i < n1) {
-		array[k] = L[i];
-		i++;
-		k++;
-	}
-	
-	//copy the remaining elements of R if there are any
-	while (j < n2) {
-		array[k] = R[i];
-		j++;
-		k++;
-	}
-}
-
-//merge-sort function
-void mergeSort(int array[], int p, int r) {
-	if (p < r) {
-		int q = (p + r) / 2;
-		mergeSort(array, p, q);
-		mergeSort(array, q+1, r);
-		merge(array, p, q, r);
-	}
-}
-
-//display function
-void display(int *array, int size) {
-	
-
-}
-
-//Main Routine
-int main(void) {
-	//define array to be sorted
-	//int *unsorted = NULL;
-	int size = 0; 
-	int temp = 0;
-	
-	//printf("Enter the size of the integer array you wish to sort: ");
-	//scanf("%d",&size);
-	//unsorted = malloc(size * sizeof(int));
-	int unsorted[] = {12, 11, 13, 5, 6, 7};
-	size = 6;
-	
-	//use current time as seed for random generator 
-    srand(time(0)); 
-  
[…]

### 2019-04-12 math408/presentation/hashPaper.tex
Did work

@@
 The purpose of this is to verify a given input without needing to store that input.
+The fixed length property is useful for storage and consistency, as well as file size reduction.
+It is important to understand what hash functions are and how they are used in everyday security so one can make good decisions about their personal digital protection.
 
@@
 
-\tab There are several criteria that must be met for a hash function to be useful.
+\tab There are several criteria that must be met for a hash function to be useful [1].
 They must be computationally efficient, which means the algorithm should run quickly on a computer without requiring a lot of memory or processing power.
@@
 They must have strong pre-image resistance, which means that given the output of a hash function, there should be no way to figure out the input that generated that particular output. 
-
 Also, hash functions have to be deterministic, meaning anytime a certain input is put into a hash function, the output should always be the same. 
-
 In order to be secure, hash functions must have strong collision resistance, which means there should be no reasonable way to find multiple inputs that generate the same output. 
-
 And finally, the output of a hash function should have the appearance of complete randomness.
@@
 Since many people use the same password for all accounts, the attacker could pivot those credentials for such users to gain access to their emails, credit cards, and online banking accounts.
-
 If instead a website stores the hashed version of users' passwords, an attacker could not reverse the hashes to discover the actual passwords of the users, and thus the hashes would be nearly useless to them.
@@
 Using hash and salt, when a user creates an account and types a password in for the first time, the website uses a hashing algorithm, but also adds a random string of characters to the user-entered string, thus ensuring that even if hundreds of users enter the same exact password, each of their hashes will be different.
+The salt is usually stored right next to the salted hash in the database.
 Then every time the user enters their password to log in, the salt is added to whatever they entered and that result is hashed.
 If it matches the stored digest, they successfully login to their account.
-
 This way, if a hacker gains access to a database, every hashed password will look different, and the only way they can match a password to a specific hash is by running a brute force attack.
@@
 MD5 is still used extensively, but should no longer be implemented for any sensitive data verification, especially not for passwords or secure keys.
+[4].
 Many common passwords can be found by typing their hash digests into Google search.
@@
 SHA-3 is the newest Secure Hashing Algorithm, and is slowly taking over and replacing SHA-256, but that will take time.
+[5].
 
@@
 This is an astronomically high number, so breaking a hash of this size with brute force is infeasible, but given that there is a near-infinite number of inputs, there will always be possible collisions.
+[2].
 
@@
 	\bibitem{Tutorials Point Website}
-	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from https://www.tutorialspoint.com/cryptography/cryptography\_hash\_functions.htm
+	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from {https://www.tutorialspoint.com/cryptography/cryptography\_hash\_functions.htm}
 

### 2019-04-12 csci230/hw11-GrantHaataja.c

@@ -1,0 +1,48 @@
+//Grant Haataja
+//Assignment 11
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+
+//function to count lines in file
+int countLines(char *fileName, FILE *(*stream)) {
+	//variable for number of lines
+	int size = 0;
+	//string variable to hold each individual line
+	char *line = NULL;
+	size_t length = 0;
+	//check if file is valid
+	if ((*stream = fopen(fileName, "r")) == NULL) {
+		printf("\nFile not found...\n");
+		return 0;
+	}
+	else {
+		while ((getline(&line, &length, *stream)) != -1) {
+			//increment size to count number of lines
+			size++;
+			//free line variable and set to null
+			free(line);
+			line = NULL;
+		}
+		//return number of lines
+		return size;
+	}
+}
+
+//function to populate linked
+
+
+//Main Routine
+int main(void) {
+	//define fileName
+	char *fileName = "hw111.data";
+	FILE *stream;
+	int size = 0;
+	
+	//count how many lines in file
+	size = countLines(fileName, &stream);
+	printf("There are %d lines in file\n",size);
+
+
+}

### 2019-04-30 csci260/wordCountingApp/twitter.tex
My latex presentation > yours, Misha

\documentclass{article}

%call packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.9in, top=0.59in]{geometry}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{tabto}
\usepackage{graphicx}
\usepackage{float}
\graphicspath{ {./} }
\usepackage{listings}
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}

%header of document
\title{Twitter Data Analysis}
\author{David Wilson \& Grant Haataja}
\date{\today}
%set paragraph spacing
\linespread{1.5}

\begin{document}
\maketitle

\newpage
%table of contents
\tableofcontents

%format titles for sections, no numbers and no indentation
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}

\newpage
%start the hack
\section{Introduction}
\tab A growing concern of social media is the amount of profanity and inappropriate content appearing to the public. This paper will address this issue by outlining data analysis for profanity on Twitter.

\section{Goals of Analysis}
\tab The goals for this analysis were to test the occurrence of profanity from a sample of tweets, to determine whether Twitter was more than 50\% profane or not. But more interestingly, the goal was to find the proportion of tweets that contain profanity.

\section{Methodology}
\tab ***David Write your stuff here***

\section{Twitter API}
\tab ***David Write your stuff here***

\section{Code to parse .json files}
\lstinputlisting[language=Python]{jsonreader.py}
The following picture shows the output of the above code when ran on the 100 json files that were created from the queries.

\begin{figure}[h]
	\includegraphics[scale=2.59]{terminal}
\end{figure}

\section{Tweet Examples}
\tab In this section, several of the tweets that were searched are shown. The program did not output the entirety of some of the longer tweets. Note that many of them have multiple occurrences of different profane words, so some of them may be counted twice.\newline

\begin{flushleft}------------------------\newline
rt @quackityhq: fuck koalas why can those little shits sleep 22 hours a day and be seen as cute but when i do it im seen as a lazy piece of…\newline
-------------------------\newline
rt @braindumptweets: trying to figure out how sex works but it doesn't seem plausible, how am i supposed to fit my entire ass in a woman's…\newline
-------------------------\newline
adding arya to my muted words because you bitches can’t be trusted.\newline
-------------------------\newline
rt @iamvee\_: i haven’t been this happy in about 3 fucking years boy\newline
-------------------------\newline
he appears healthy but he seems just to be very damn tired. i'll keep an eye on him and call an animal sanctuary later\newline
-------------------------\newline
if i could get my tubes tied today i fucking would. i’d sell every single one of my eggs. fuck dem kids.\newline
-------------------------\newline
waw i already miss them ;(( my spoiled ass need to stop i keep missing them even if they feed me so much\newline
------------------------\newline
\end{flushleft}

\section{Code to Create Graphs}
\tab Shown below is the Python code used to generate the pie chart used to display the data results.\newline

\lstinputlisting[language=Python]{piechart.py}

The following is the code to generate the bar chart containing the actual number of tweets with the queried profanities.\newline

\lstinputlisting[language=Python]{barchart.py}

\section{The Data}
\tab Below are the recorded percentages of various profanity from the 1136 tweets in the sample size. A total of 37 tweets were found to be profane.

\begin{figure}[h]
	\includegraphics[scale=1]{Figure_1}
\end{figure}

Shown in the next chart are the actual numbers of occurrences of the various profanity in the 37 profane tweets found from the sample.

\begin{figure}[h]
	\includegraphics[scale=1]{Figure_2}
\end{figure}

\section{Conclusions}
\tab The data collected show that Twitter is much less profane than 50\%. In fact, only about 3.3\% of tweets collected were found to be profane. However, those that did contain profanity often had multiple occurrences of it. The question of the safety of a platform such as Twitter must ultimately be answered by the individual.

\section{Further Research}
\tab This small data study could be expanded into a much larger research project quite easily by collecting profanity proportions from other social media platforms, and analyzing possible correlations between variables. It would be interesting indeed to see which of the major social media platforms had the most occurrences of profanity, which had the largest total number of profane words, or how the amount of profanity of a platform was correlated to users' opinion of the platform.

\newpage
\begin{thebibliography}{}
	\bibitem{stuff}I don't think we need any references, do we?

\end{thebibliography}

\end{document}

### 2019-04-30 csci260/wordCountingApp/Twurl Requests/jsonreader.py

@@ -1,6 +1,6 @@
 import json
 
-jsonNum = 110
+jsonNum = 100
 tweets = []
 profanity = []
 
@@ -33,7 +33,3 @@ print(str(len(profaneTweets)) + '/' + str(len(tweets)))
 print('\n\tUses:')
 for use in uses:
 	print(use + ': ' + str(uses[use]))
-	
-for tweet in profaneTweets:
-	print('-' * 25)
-	print(tweet)

### 2019-04-30 csci260/wordCountingApp/barchart.py

@@ -1,7 +1,7 @@
 from matplotlib import pyplot
 import numpy
 
-#define the pie chart
+#define the bar chart
 labels = ['Shit', 'Fucking', 'Fuck', 'Bitches', 'Damn', 'Fucks', 'Ass', 'Shits', 'Asses']
 y_pos = numpy.arange(len(labels))
 sizes = [13, 9, 7, 7, 3, 2, 2, 1, 1]
@@ -9,6 +9,6 @@ sizes = [13, 9, 7, 7, 3, 2, 2, 1, 1]
 #do the plot
 pyplot.bar(y_pos, sizes, align='center', alpha=0.5)
 pyplot.xticks(y_pos, labels)
-pyplot.ylabel('Occurence')
+pyplot.ylabel('Occurrence')
 pyplot.title('Profanity in Tweets')
 pyplot.show()

### 2019-05-02 csci487/project/paper.tex
Started working on 487 paper

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{CSci487 Penetration Testing Project: AILEE}

\author{\IEEEauthorblockN{Grant Haataja}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, USA \\
grant.haataja@und.edu}
\and
\IEEEauthorblockN{David Wilson}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, USA \\
david.andrew.wilson@und.edu}
\and
\IEEEauthorblockN{Michael Turnbull}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, USA \\
michael.turnbull@und.edu}
}

\maketitle

\begin{abstract}
This document details the planning, development, and workings of the penetration testing game AILEE, created as a final project for CSCI 487 Penetration Testing class at the University of North Dakota.
\end{abstract}

%\begin{IEEEkeywords}
%component, formatting, style, styling, insert
%\end{IEEEkeywords}

\section{Introduction}
For this project on penetration testing topics, a hacking simulation game was created. The premise of the game is as follows: the user plays the role of a penetration-testing AI software named AILEE, which stands for Artificial Intelligence Linux Exploit Environment. The game takes place exclusively in a Linux-style terminal environment, with a limited arsenal of commands for the player to use. As the player progresses through the game and “learns” as an AI, the commands available for use increase. Throughout the game, the player is given typed instructions and information from the AI’s administrator to assist in learning.

There are two targets to hack in this demo, although there is much potential for expansion. The game uses simulated port scanning, vulnerability scanning, exploitation, and other penetration testing tools to mimic real-life penetration testing methods. Additionally, the game features a storyline with three possible endings, depending on player actions. Special care was taken to handle proper sequence of events.

\section{Investigation}

\subsection{Planning the Project}

Before beginning the development of the game, a suitable platform to run the environment needed to be found. The website Repl.it was decided upon, due to their extensive language support and the ability for multiple people to work simultaneously and have all changes automatically saved to the cloud. [1] The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.

Python3 was selected as the programming language of choice, due to its ease of scripting and strong object-oriented nature. The various classes corresponding to different aspects of the game and environment would be programmed separately, as well as Python scripts for each command available to the player, and every storyline event that could be run. The original plan was for there to be three different targets for the player to hack, but due to time limitations the scope was decreased to two targets.

To enable smooth graphics for the intro screen and the game’s ending events, the Python Curses library was referenced and used extensively. [2] This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.

\section{Project Description}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{Figure_1}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} Repl.it, “The world's leading online coding platform,” repl.it. [Online]. Available: https://repl.it/site/features. [Accessed: 02-May-2019].

\bibitem{b2} A. M. Kuchling and E. S. Raymond, “Curses Programming with Python¶,” Curses Programming with Python - Python 3.7.3 documentation. [Online]. Available: https://docs.python.org/3/howto/curses.html. [Accessed: 02-May-2019].

\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-05-02 csci260/project/crawler.py

@@ -1,83 +1,0 @@
-from html.parser import HTMLParser  
-from urllib.request import urlopen  
-from urllib import parse
-
-# We are going to create a class called LinkParser that inherits some
-# methods from HTMLParser which is why it is passed into the definition
-class LinkParser(HTMLParser):
-
-    # This is a function that HTMLParser normally has
-    # but we are adding some functionality to it
-    def handle_starttag(self, tag, attrs):
-        # We are looking for the begining of a link. Links normally look
-        # like <a href="www.someurl.com"></a>
-        if tag == 'a':
-            for (key, value) in attrs:
-                if key == 'href':
-                    # We are grabbing the new URL. We are also adding the
-                    # base URL to it. For example:
-                    # www.netinstructions.com is the base and
-                    # somepage.html is the new URL (a relative URL)
-                    #
-                    # We combine a relative URL with the base URL to create
-                    # an absolute URL like:
-                    # www.netinstructions.com/somepage.html
-                    newUrl = parse.urljoin(self.baseUrl, value)
-                    # And add it to our colection of links:
-                    self.links = self.links + [newUrl]
-
-    # This is a new function that we are creating to get links
-    # that our spider() function will call
-    def getLinks(self, url):
-        self.links = []
-        # Remember the base URL which will be important when creating
-        # absolute URLs
-        self.baseUrl = url
-        # Use the urlopen function from the standard Python 3 library
-        response = urlopen(url)
-        # Make sure that we are looking at HTML and not other things that
-        # are floating around on the internet (such as
-        # JavaScript files, CSS, or .PDFs for example)
-        if response.getheader('Content-Type')=='text/html':
-            htmlBytes = response.read()
-            # Note that feed() handles Strings well, but not bytes
-            # (A change from Python 2.x to Python 3.x)
-            htmlString = htmlBytes.decode("utf-8")
-            self.feed(htmlString)
-            return htmlString, self.links
-        else:
-            return "",[]
-
-# And finally here is our spider. It takes in an URL, a word to find,
-# and the number of pages to search through before giving up
-def spider(url, word, maxPages):  
-    pagesToVisit = [url]
-    numberVisited = 0
-    foundWord = False
-    # The main loop. Create a LinkParser and get all the links on the page.
-    # Also search the page for the word or string
-    # In our getLinks function we return the web page
-    # (this is useful for searching for the word)
-    # and we return a set of links from that web page
[…]

### 2019-05-04 csci260/wordCountingApp/twitter.tex
started my portion

@@
 \section{Methodology}
-\tab ***David Write your stuff here***
+\tab In order to collect the tweet data for the analysis, this study chose to use the Twitter API (*** Reference?
+***).
+To do so, the program used to access the tweet metadata needed to be registered through a twitter developer account.
 
@@
 \begin{thebibliography}{}
-	\bibitem{stuff}I don't think we need any references, do we?
+	\bibitem{stuff}https://twitter.com
+	\bibitem{stuff}https://developer.twitter.com/en/docs.html *** CHECK THIS ***
 

### 2019-05-04 csci260/wordCountingApp/twitter.tex
Finished my section?
> Removed Twitter API portion, as it is unnecessary and the info is included in Methodology
> Finished Methodology section
> Added citations

--- 2019-04-30 csci260/wordCountingApp/twitter.tex
@@
 \section{Methodology}
-\tab ***David Write your stuff here***
-
-\section{Twitter API}
-\tab ***David Write your stuff here***
+\tab In order to collect the tweet data for the analysis, this study chose to use the Twitter API [2].
+This required a twitter developer account, and security keys to access the API using HTTP requests.
+A twitter developer was created, and the project was registered under Twitter to get the access keys.
+\tab After aquiring the access keys, the project utilized the command line program "Twurl" to send Twitter search requests to the API.
+Results were returned in a json file format.
+Unfortunately, because the project didn't aquire the premium form of the Twitter API, each search request was limited to 15 results.
+\tab Because of this, the project was instead composed of a hundred seperate search requests, using Wikipedia's list of the most common words in english [3].
+Then, a python script was created to parse the json files retrieved, and search the tweets for the profane words.
+Finally, the collected data was used to create tables and support our conclusion.
 
@@
 \begin{thebibliography}{}
-	\bibitem{stuff}I don't think we need any references, do we?
+	\bibitem{Twitter}
+	Twitter. (2019). It's what's happening.
+	Retrieved from {https://twitter.com}
+
+	\bibitem{Twitter API Reference}
+	Twitter. (2019). Developer Documentation.
+	Retrieved from {https://developer.twitter.com/en/docs.html}
+
+	\bibitem{Wikipedia}
+	Wikimedia Foundation. (2018, December 12). Most common words in English. 
+	Retrieved from {https://en.wikipedia.org/wiki/Most_common_words_in_English}
 

### 2019-05-04 csci487/project/paper.tex
LaTeX is the best

@@
 \usepackage{xcolor}
+\usepackage{float}
+\graphicspath{ {./} }
+\usepackage{listings}
+\usepackage{color}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+	backgroundcolor=\color{backcolour},   
+	commentstyle=\color{codegreen},
+	keywordstyle=\color{magenta},
+	numberstyle=\tiny\color{codegray},
+	stringstyle=\color{codepurple},
+	basicstyle=\footnotesize,
+	breakatwhitespace=false,         
+	breaklines=true,                 
+	captionpos=b,                    
+	keepspaces=true,                 
+	numbers=left,                    
+	numbersep=5pt,                  
+	showspaces=false,                
+	showstringspaces=false,
+	showtabs=false,                  
+	tabsize=2
+}
+
+\lstset{style=mystyle}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \section{Project Description}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\subsection{Intro Screen}\label{AA}
+For the graphics of the intro screen for the game, ASCII art was used to spell the word AILEE, along with a selection for New Game or Exit.
+The user can move between the selection using the up or down arrow keys and choose by pressing the enter key.
+Selecting Exit will cause the terminal session within Repl.it to exit and the game will have to be run again, selecting New Game creates a new session and runs the game.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+In addition to these, pressing the up arrow six times in a row will show a hidden third selection, Skip Dialog.
+This will run the game without displaying any of the instructions and information from the administrator to AILEE, and was very useful for testing the game during development.
+This mode is not explained or mentioned in the game, as it is not recommended to play without reading the dialogue.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+The intro screen makes use of the Python curses library to allow smooth use of the arrow keys keyboard input and prevent buggy graphics.
+
+\subsection{Starting the Game}
+Upon choosing New Game, the user watches as the administrator logs into their account and launches AILEE.exe to start a new shell.
+After the shell loads, the first event triggers and text displays on the screen to inform the user what is going on.
+The administrator gives a brief explanation, and then the user is free to experiment with the Linux-style terminal environment.
+The terminal runs in the Shell class, (in tandem with the Game and DoStory classes), which supports multiple terminals on various computers.
+The code for the Shell class is as follows:
+
+\lstinputlisting[language=Python]{shell.py}
+
+The user is encouraged to try out the various possible commands, which can be displayed using the \textit{help} command.
+The story continues after the user has ran ten commands, (they can be the same or different commands, it doesn't matter).
 

### 2019-05-04 csci487/project/paper.tex
Worked on 487 paper

@@
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\subsection{Gameplay and Executables}
+As the game progresses, the user will utilize the available penetration testing tools to gain access to the target computers.
+There are tools for finding IP addresses, port scanning, vulnerability scanning, exploitation, password cracking, and connecting through the ftp file sharing network.
+Generally, some of the commands require the results from running other commands in order to be run successfully.
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+In particular, the \textit{exploit} command is extremely useful for gaining access to other computers.
+This executable is similar to the Metasploit framework which is commonly used in real-life penetration testing.
+In the game, it only has two possible exploits to choose from, and if ran against a vulnerable IP address with the proper port selection, will successfully open a new shell on the target computer.
+
+\lstinputlisting[language=Python]{exploit.py}
+
+Above is the code for the \textit{exploit} executable in the game.
+In terms of options, it does not compare to the Metasploit framework, but the goal was to create it to feel similarly in the terminal environment.
+
+\begin{figure}[htbp]
+	\centerline{\includegraphics[scale=2]{exploit-pic}}
+	\caption{Running the \textit{exploit} executable}
+	\label{fig}
+\end{figure}
+
+First, the user enters the number corresponding to the exploit they wish to run.
+Then, the target IP address is entered, followed by the specific port, and finally the command 'run' must be entered and the exploitation software will attempt to gain access to the target (Fig.
+1).
+
+\begin{figure}[htbp]
+	\centerline{\includegraphics[scale=2]{loading-new-shell}}
+	\caption{Gaining a shell on target machine}
+	\label{fig}
+\end{figure}
+
+If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig 2).
+
+\begin{figure}[htbp]
+	\centerline{\includegraphics[scale=2]{access-granted}}
+	\caption{A new shell on an exploited target}
+	\label{fig}
+\end{figure}
+
+Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig 3).
+
+Most of the other executables play an important role in the game, with a few exceptions that were included for comedic value.
 
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{Figure_1}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
 Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 

### 2019-05-04 csci487/project/paper.tex
SpEnCeR kNoWs LaTeX

@@
 
-\subsection{\LaTeX-Specific Advice}
+\subsection{Events and Storyline}
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
+The story development of the game is controlled by event scripts that are triggered at specific times.
+Running the events in the proper order is critical for the game to play as planned.
+The first event is run immediately after the game loads its first shell on the localhost computer.
+Each event after that has a condition that must be met to trigger it.
+The second event runs after ten commands have been run, the third event runs after the \textit{pscan} command runs, and so on.
+Each event runs instructions for the user that should allow them to trigger the next event and progress in the game.
 
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
+\lstinputlisting[language=Python]{event3.py}
 
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
+This is how the scripts for the events are written, implementing a custom-built "typewriter" function created to display text to the screen word by word as if it were typed, and using a blue color to differentiate it from the rest of the game text.
 
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
+\begin{figure}[htbp]
+	\centerline{\includegraphics[scale=1.36]{event3}}
+	\caption{The dialogue for event 3}
+	\label{fig}
+\end{figure}
 

### 2019-05-04 csci487/project/paper.tex
MiShA iT Is YoUr TuRn To WoRk On ThIs

@@
 The website Repl.it was decided upon, due to their extensive language support and the ability for multiple people to work simultaneously and have all changes automatically saved to the cloud.
-[1] The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.
+\cite{b1} The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.
 
@@
 To enable smooth graphics for the intro screen and the game’s ending events, the Python Curses library was referenced and used extensively.
-[2] This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.
+\cite{b2} This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.
 
@@
 
-\subsection{Gameplay and Executables}
+\subsection{Gameplay and Commands}
 As the game progresses, the user will utilize the available penetration testing tools to gain access to the target computers.
@@
 In particular, the \textit{exploit} command is extremely useful for gaining access to other computers.
-This executable is similar to the Metasploit framework which is commonly used in real-life penetration testing.
+This command is similar to the Metasploit framework which is commonly used in real-life penetration testing.
 In the game, it only has two possible exploits to choose from, and if ran against a vulnerable IP address with the proper port selection, will successfully open a new shell on the target computer.
@@
 
-Above is the code for the \textit{exploit} executable in the game.
+Above is the code for the \textit{exploit} command in the game.
 In terms of options, it does not compare to the Metasploit framework, but the goal was to create it to feel similarly in the terminal environment.
@@
 
-If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig 2).
+If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig. 2).
 
@@
 
-Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig 3).
+Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. 3).
 
-Most of the other executables play an important role in the game, with a few exceptions that were included for comedic value.
+Most of the other commands play an important role in the game, with a few exceptions that were included for comedic value.
 
@@
 \begin{figure}[htbp]
-	\centerline{\includegraphics[scale=1.36]{event3}}
+	\centerline{\includegraphics[scale=1.39]{event3}}
 	\caption{The dialogue for event 3}
@@
 
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
+This is the text for the third event (Fig. 4), which triggers after the user runs the command \textit{pscan} against the first target IP address.
 
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
+There are three special events that do not trigger in a normal play-through of the game.
+These events will only trigger if the player thinks for themselves and uses information found in the game creatively and without instruction from the administrator.
+Interestingly, if the user follows the instructions without diverging on their own, they will lose the game during the final hack.
+The only way to win is by finding what the information leads to and changing the fate of the game before attempting to exploit the final target.
 
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
+\subsection{Computers and Filesystems}
+AILEE uses a filesystem structure that feels like a Linux terminal.
+There are a total of four computers in the game, localhost (AILEE's home computer), the two targets, and one other computer.
+Each computer has a unique filesystem, with directories and files.
+As time was limited, the \textit{bin} and \textit{log} directories were left empty on all computers, but the \textit{home} directories all have files in them that either pertain to the gameplay or exist for comedic value or storyline development.
 
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
+To navigate the filesystems, the traditional Linux commands \textit{ls} and \textit{cd} are used, as well as the commands \textit{read} and \textit{run}, which display file text and run executable files, respectively.
 
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
+\lstinputlisting[language=Python]{filesystem.py}
 
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
+This is the code for the structure and mechanics of the computer filesystems.
 
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
+\begin{figure}[htbp]
+	\centerline{\includegraphics[scale=2]{filesystem-example}}
+	\caption{Filesystem navigation}
+	\label{fig}
+\end{figure}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+The directories are colored light blue, executable files are colored light green and all have a .exe extension, and regular files are colored white and must have a .something extension (Fig.
+5).
+One difference between AILEE and a real-life Linux terminal is that the \textit{ls} command cannot be given an argument in the game, and thus can only be used in the current directory.
 
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+\section{Conclusion}
+In summary, this project dives into many core concepts and facets of penetration testing, and simulates them to feel like the real-world counterparts.
+Many of the commands that simulate complicated software are coded creatively to look realistic even though they only work in the specific instances inside the game.
+AILEE is a demo, and there is much opportunity to expand the game into something far more complex and realistic if enough time and energy was dedicated to doing so.
 
@@
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2019-05-04 csci487/project/filesystem.py

@@ -1,0 +1,68 @@
+import termcolor
+
+class Directory:
+  '''
+    Tree structure of directories and files
+  '''
+  def __init__(self, name=None, parent=None, children=None):
+    self.name = name or ''
+    self.parent = parent or self # So root node points to itself as parent
+    self.children = {
+      '.':self,
+      '..':self.parent
+    }
+    if type(children) is dict:
+      self.children.update(children)
+
+  def mkdir(self, name):
+    assert (name not in self.children), 'Directory already exists'
+    newDir = Directory(name, self)
+    self.children.update({name:newDir})
+    return newDir
+
+  def addFile(self, fileName, fileContents):
+    assert (fileName not in self.children), 'File already exists'
+    assert ('.' in fileName), 'File has no type'
+    newFile = File(fileName, fileContents)
+    self.children.update({fileName:newFile})
+    return newFile
+  
+  def rmFile(self, fileName):
+    assert (fileName in self.children), "File does not exist"
+    assert ('.' in fileName), "File has no type"
+    del self.children[fileName]
+
+  def __iter__(self):
+    return (fName for fName in self.children)
+    
+  def __repr__(self, base=True):
+    return (self.parent.__repr__(base=False) + '/' if self.parent.name else '') + self.name + ('/' if base else '')
+  __str__ = __repr__ # set __str__ as the same method as __repr__
+  
+  def __getitem__(self, item):
+    assert (item in self.children), "File or Directory not found"
+    return self.children[item]
+
+  def __len__(self):
+    return len(self.children)
+
+
+class File:
+  '''
+    Stores things. Like data, machine code, and blackmail
+  '''
+  def __init__(self, name, data='', permissions='rw-rw-', owner=None):
+    self.name = name
+    self.data = data
+    self.permissions = permissions
+    self.owner = owner
+
+  def append(self, data):
+    self.data += data
+
+  def __repr__(self):
+    return self.name
+  __str__ = __repr__ # set __str__ as the same method as __repr__
+
+  def __len__(self):
+    return len(self.data)

### 2019-05-04 csci487/project/paper.tex
Add figures; small changes to paper
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

@@
 \IEEEauthorblockA{\textit{UND Computer Science} \\
-Grand Forks, USA \\
+Grand Forks, ND, USA \\
 grant.haataja@und.edu}
@@
 \IEEEauthorblockA{\textit{UND Computer Science} \\
-Grand Forks, USA \\
+Grand Forks, ND, USA \\
 david.andrew.wilson@und.edu}
@@
 \IEEEauthorblockA{\textit{UND Computer Science} \\
-Grand Forks, USA \\
+Monroe, NH, USA \\
 michael.turnbull@und.edu}
@@
 \end{abstract}
+
+\tableofcontents
 
@@
 
+\begin{figure}[h]
+    \centerline{\includegraphics[scale=0.7]{shellloop.png}}
+    \caption{Shell flow diagram}
+    \label{fig:shell-flow}
+\end{figure}
+
 \subsection{Gameplay and Commands}
@@
 
-In particular, the \textit{exploit} command is extremely useful for gaining access to other computers.
-This command is similar to the Metasploit framework which is commonly used in real-life penetration testing.
-In the game, it only has two possible exploits to choose from, and if ran against a vulnerable IP address with the proper port selection, will successfully open a new shell on the target computer.
+In particular, the \texttt{exploit} command is extremely useful for gaining access to other computers.
+This command is similar to the Metasploit framework, commonly used in real-life penetration testing.
+In the game, as the player uncovers exploits in different computers with the \texttt{vscan} command, those exploits are added to a global database of exploits which the user can then pick from in the \texttt{exploit} command.
+Exploits are specific to a port on a computer, and if correctly used, will successfully open a new shell on the target computer.
 
@@
 
+\begin{figure}[hp]
+    \centerline{\includegraphics[scale=0.5]{gameflow.png}}
+    \caption{The sequence of events in play order}
+    \label{fig:gameplay-sequence}
+\end{figure}
+
 There are three special events that do not trigger in a normal play-through of the game.
@@
 This is the code for the structure and mechanics of the computer filesystems. 
+Similar to Linux, both files and folders have and use discrete permissions, 
+marking certain files as executable and readable.  While there are not yet any
+provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
+creates a file \texttt{a.out}, which promptly throws a segmentation fault.},
+the permissions architecture is in place for adding future file-editing
+utilities.
+
+Executable files are created from a separate filesystem constructor.  Each
+executable file simply is a \texttt{File} object with the executable bit set in
+its permissions object, and the file contents are pure Python code that executes
+when the file is run via the \texttt{run} command.  To verify that arbitrary
+code is not run (which would break the game), executable files compare hashes
+from creation to runtime to and will not run if the contents have been
+altered.
 

### 2019-05-04 csci487/project/shell.py

@@ -1,8 +1,12 @@
+# -*- coding: utf-8 -*-
+
 from termcolor import colored
-import replit
+import funfunctions
 
 import time
-import traceback, sys, random
+import traceback
+import sys
+import random
 
 import executables
 import events
@@ -11,138 +15,142 @@ from MainMenuException import MainMenuException
 DEFAULT_PROMPT = colored("AILEE@{COMP}: {CWD}$ ", 'green')
 
 CMD_NOT_FOUND_STRS = [
-  "command not found"
+    "command not found",
+    "Nope, don't know that one",
+    "This isn't Google",
+    "NOOB!"
+    "Segmentation fault (core dumped)",
+
 ]
 
+
 class Shell(object):
-  """
-  Like a seashell.
-  """
-
-  def __init__(self, computer, user, agent=None, cwd=None, game=None):
     """
-    Create a shell.
+    Like a seashell.
     """
 
-    self.computer = computer
-    self.user = user
-    self.agent = agent
-    self.cwd = cwd or computer.fs
-    self.prompt = DEFAULT_PROMPT
-    self.running = False
-    self._command_dictionary = {}
-    self.variables = {}
-    self.game = game
-    self.history = []
+    def __init__(self, computer, user, agent=None, cwd=None, game=None):
+        """
+        Create a shell.
+        """
 
-    self._setup()
-  
-  def _setup(self):
-    replit.clear()
-    s = "Loading new shell"
+        self.computer = computer
+        self.user = user
+        self.agent = agent
+        self.cwd = cwd or computer.fs
+        self.prompt = DEFAULT_PROMPT
+        self.running = False
+        self._command_dictionary = {}
+        self.variables = {}
+        self.game = game
+        self.history = []
 
-    print(s, end='\r')
-    i = 0
+        self._setup()
 
-    # load command dictionary
-    for module in executables.__all__:
-      self._command_dictionary.update({module: getattr(executables, module).run})
-      print(s + '.'*i, end='\r')
-      i += 1
-      time.sleep(0.1)
-    time.sleep(0.3)
-    replit.clear()
-    #print(constants.title)
-  
-  def _get_command_from_str(self, command_str):
-    """
-    Takes a command name, returns the executable object.
-    """
-    
-    if command_str == '':
-      return False
-    if command_str not in self.game.allowed_commands:
-      return None
-    cmd = self._command_dictionary[command_str]
-    return cmd
-  
-  def run_command(self, command, args):
-    """
[…]

### 2019-05-05 csci487/project/paper.tex
Remove broken quotes, update paragraph on ls command to include colors
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

@@
 \usepackage{color}
+\usepackage{hyperref}
 
@@
 \definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+% came from the ANSI escape sequence color table as implemented by Ubuntu
+% used for colorizing the ls-description paragraph
+\definecolor{folder-blue}{RGB}{0,111,184}
+\definecolor{file-green}{RGB}{57,181,74}
 
@@
 \lstset{style=mystyle}
+
+% what does this do?  i commented it out and can't tell any difference -misha
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
@@
 
-The directories are colored light blue, executable files are colored light green and all have a .exe extension, and regular files are colored white and must have a .something extension (Fig.
-5).
-One difference between AILEE and a real-life Linux terminal is that the \textit{ls} command cannot be given an argument in the game, and thus can only be used in the current directory.
+Directories are colored \textcolor{folder-blue}{\textbf{light blue}}, executables a \textcolor{file-green}{\textbf{light green}}, and regular files are white.
+Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.
+However, due to the difficult implementation of a directory tree, the \textit{ls} command cannot be given a path argument as in real life, and thus can only be used in the current directory.
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} Repl.it, “The world's leading online coding platform,” repl.it. [Online]. Available: https://repl.it/site/features. [Accessed: 02-May-2019].
+\bibitem{b1} Repl.it, ``The world's leading online coding platform,'' repl.it. [Online]. Available: \url{https://repl.it/site/features}. [Accessed: 02-May-2019].
 
@@
 S.
-Raymond, “Curses Programming with Python¶,” Curses Programming with Python - Python 3.7.3 documentation.
+Raymond, ``Curses Programming with Python,'' Curses Programming with Python - Python 3.7.3 documentation.
 [Online].
-Available: https://docs.python.org/3/howto/curses.html.
+Available: \url{https://docs.python.org/3/howto/curses.html}.
 [Accessed: 02-May-2019].
-
 \end{thebibliography}

### 2019-05-06 csci487/project/paper.tex
Editing
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

@@
 
-\tableofcontents
+%\tableofcontents
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h]
 	\centerline{\includegraphics[scale=2]{exploit-pic}}
 	\caption{Running the \textit{exploit} executable}
-	\label{fig}
+	\label{fig:exploit-pic}
 \end{figure}
@@
 Then, the target IP address is entered, followed by the specific port, and finally the command 'run' must be entered and the exploitation software will attempt to gain access to the target (Fig.
-1).
+\ref{fig:exploit-pic})
 
-\begin{figure}[htbp]
+\begin{figure}[h]
 	\centerline{\includegraphics[scale=2]{loading-new-shell}}
 	\caption{Gaining a shell on target machine}
-	\label{fig}
+	\label{fig:loading}
 \end{figure}
 
-If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig. 2).
+If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig. \ref{fig:loading})
 
-\begin{figure}[htbp]
+\begin{figure}[h]
 	\centerline{\includegraphics[scale=2]{access-granted}}
 	\caption{A new shell on an exploited target}
-	\label{fig}
+	\label{fig:access}
 \end{figure}
 
-Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. 3).
+Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. \ref{fig:access}).
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h]
 	\centerline{\includegraphics[scale=1.39]{event3}}
 	\caption{The dialogue for event 3}
-	\label{fig}
+	\label{fig:event3}
 \end{figure}
 
-This is the text for the third event (Fig. 4), which triggers after the user runs the command \textit{pscan} against the first target IP address.
+This is the text for the third event (Fig. \ref{fig:event3}), which triggers after the user runs the command \textit{pscan} against the first target IP address.
 
-\begin{figure}[hp]
+\begin{figure}[h]
     \centerline{\includegraphics[scale=0.5]{gameflow.png}}
@@
 Similar to Linux, both files and folders have and use discrete permissions, 
-marking certain files as executable and readable.  While there are not yet any
+marking certain files as readable, writable, and executable.  While there are not yet any
 provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
@@
 	\caption{Filesystem navigation}
-	\label{fig}
+	\label{fig:ls-command}
 \end{figure}
 
-Directories are colored \textcolor{folder-blue}{\textbf{light blue}}, executables a \textcolor{file-green}{\textbf{light green}}, and regular files are white.
+Directories are colored light blue, executables are light green, and regular files are white.
 Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.

### 2019-05-06 csci487/project/shell.py
Remove fun
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

@@ -14,15 +14,6 @@ from MainMenuException import MainMenuException
 
 DEFAULT_PROMPT = colored("AILEE@{COMP}: {CWD}$ ", 'green')
 
-CMD_NOT_FOUND_STRS = [
-    "command not found",
-    "Nope, don't know that one",
-    "This isn't Google",
-    "NOOB!"
-    "Segmentation fault (core dumped)",
-
-]
-
 
 class Shell(object):
     """
@@ -131,7 +122,6 @@ class Shell(object):
         self.history.append([None, []])
         self.game.history.append([None, []])
         print("Command not found")
-        # print(random.choice(CMD_NOT_FOUND_STRS))
 
     def start_shell_loop(self):
         self.running = True

### 2019-05-06 csci487/project/filesystem.py
Switch back to old code
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

@@ -1,205 +1,68 @@
-import hashlib
+import termcolor
+
+class Directory:
+  '''
+    Tree structure of directories and files
+  '''
+  def __init__(self, name=None, parent=None, children=None):
+    self.name = name or ''
+    self.parent = parent or self # So root node points to itself as parent
+    self.children = {
+      '.':self,
+      '..':self.parent
+    }
+    if type(children) is dict:
+      self.children.update(children)
+
+  def mkdir(self, name):
+    assert (name not in self.children), 'Directory already exists'
+    newDir = Directory(name, self)
+    self.children.update({name:newDir})
+    return newDir
+
+  def addFile(self, fileName, fileContents):
+    assert (fileName not in self.children), 'File already exists'
+    assert ('.' in fileName), 'File has no type'
+    newFile = File(fileName, fileContents)
+    self.children.update({fileName:newFile})
+    return newFile
+  
+  def rmFile(self, fileName):
+    assert (fileName in self.children), "File does not exist"
+    assert ('.' in fileName), "File has no type"
+    del self.children[fileName]
+
+  def __iter__(self):
+    return (fName for fName in self.children)
+    
+  def __repr__(self, base=True):
+    return (self.parent.__repr__(base=False) + '/' if self.parent.name else '') + self.name + ('/' if base else '')
+  __str__ = __repr__ # set __str__ as the same method as __repr__
+  
+  def __getitem__(self, item):
+    assert (item in self.children), "File or Directory not found"
+    return self.children[item]
+
+  def __len__(self):
+    return len(self.children)
 
 
-class Permissions(object):
-    """
-    rwxrwx
-    |||||\ Owner exec
-    ||||\ Owner write
-    |||\ Owner read
-    ||\ General user exec
-    |\ General user write
-    \ General user read
-    """
+class File:
+  '''
+    Stores things. Like data, machine code, and blackmail
+  '''
+  def __init__(self, name, data='', permissions='rw-rw-', owner=None):
+    self.name = name
+    self.data = data
+    self.permissions = permissions
+    self.owner = owner
 
-    def __init__(self, perms):
-        self._bits = perms
-        assert len(self._bits) == 6
+  def append(self, data):
+    self.data += data
 
-    def _set_bit(self, n, newval):
-        bits = list(self._bits)
-        bits[n] = newval
-        self._bits = ''.join(bits)
+  def __repr__(self):
+    return self.name
+  __str__ = __repr__ # set __str__ as the same method as __repr__
 
-    def __str__(self):
-        return self._bits
-
[…]

### 2019-05-06 csci487/project/shell.py

@@ -1,12 +1,8 @@
-# -*- coding: utf-8 -*-
-
 from termcolor import colored
-import funfunctions
+import replit
 
 import time
-import traceback
-import sys
-import random
+import traceback, sys, random
 
 import executables
 import events
@@ -14,133 +10,139 @@ from MainMenuException import MainMenuException
 
 DEFAULT_PROMPT = colored("AILEE@{COMP}: {CWD}$ ", 'green')
 
+CMD_NOT_FOUND_STRS = [
+  "command not found"
+]
 
 class Shell(object):
+  """
+  Like a seashell.
+  """
+
+  def __init__(self, computer, user, agent=None, cwd=None, game=None):
     """
-    Like a seashell.
+    Create a shell.
     """
 
-    def __init__(self, computer, user, agent=None, cwd=None, game=None):
-        """
-        Create a shell.
-        """
+    self.computer = computer
+    self.user = user
+    self.agent = agent
+    self.cwd = cwd or computer.fs
+    self.prompt = DEFAULT_PROMPT
+    self.running = False
+    self._command_dictionary = {}
+    self.variables = {}
+    self.game = game
+    self.history = []
 
-        self.computer = computer
-        self.user = user
-        self.agent = agent
-        self.cwd = cwd or computer.fs
-        self.prompt = DEFAULT_PROMPT
-        self.running = False
-        self._command_dictionary = {}
-        self.variables = {}
-        self.game = game
-        self.history = []
+    self._setup()
+  
+  def _setup(self):
+    replit.clear()
+    s = "Loading new shell"
 
-        self._setup()
+    print(s, end='\r')
+    i = 0
 
-    def _setup(self):
-        funfunctions.clear()
-        s = "Loading new shell"
+    # load command dictionary
+    for module in executables.__all__:
+      self._command_dictionary.update({module: getattr(executables, module).run})
+      print(s + '.'*i, end='\r')
+      i += 1
+      time.sleep(0.1)
+    time.sleep(0.3)
+    replit.clear()
+    #print(constants.title)
+  
+  def _get_command_from_str(self, command_str):
+    """
+    Takes a command name, returns the executable object.
+    """
+    
+    if command_str == '':
+      return False
+    if command_str not in self.game.allowed_commands:
+      return None
+    cmd = self._command_dictionary[command_str]
+    return cmd
+  
+  def run_command(self, command, args):
+    """
+    Runs a command.
 
-        print(s, end='\r')
-        i = 0
[…]

### 2019-05-06 csci487/project/paper.tex
texttt appropriate commands
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>
Removed paragraphs about the new code that we're not using anymore :(
Signed-off-by: Grant Haataja <grant.haataja@gmail.com>

@@
 
+Go to \cite{b1} to see the complete source code for AILEE on Repl.it and play the game. It is recommended to play the game in a new tab for a better graphical experience.
+
 \section{Investigation}
@@
 The website Repl.it was decided upon, due to their extensive language support and the ability for multiple people to work simultaneously and have all changes automatically saved to the cloud.
-\cite{b1} The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.
+\cite{b2} The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.
 
@@
 To enable smooth graphics for the intro screen and the game’s ending events, the Python Curses library was referenced and used extensively.
-\cite{b2} This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.
+\cite{b3} This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.
 
@@
 
-Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. \ref{fig:access}).
+Once the shell loads, the name of the computer exploited will be shown before the \texttt{/\$} symbol where commands are typed (Fig. \ref{fig:access}).
 
@@
 
-This is the code for the structure and mechanics of the computer filesystems. 
-Similar to Linux, both files and folders have and use discrete permissions, 
-marking certain files as readable, writable, and executable.  While there are not yet any
-provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
-creates a file \texttt{a.out}, which promptly throws a segmentation fault.},
-the permissions architecture is in place for adding future file-editing
-utilities.
-
-Executable files are created from a separate filesystem constructor.  Each
-executable file simply is a \texttt{File} object with the executable bit set in
-its permissions object, and the file contents are pure Python code that executes
-when the file is run via the \texttt{run} command.  To verify that arbitrary
-code is not run (which would break the game), executable files compare hashes
-from creation to runtime to and will not run if the contents have been
-altered.
+Above is the code for the structure and mechanics of the computer filesystems.
 
@@
 
-Directories are colored light blue, executables are light green, and regular files are white.
-Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.
-However, due to the difficult implementation of a directory tree, the \textit{ls} command cannot be given a path argument as in real life, and thus can only be used in the current directory.
+Directories are colored light blue, executables are light green, and regular files are white (Fig.
+\ref{fig:ls-command}).
+Unlike a real Linux terminal, the \textit{ls} command only works in the current directory and takes no arguments.
 
@@
 Many of the commands that simulate complicated software are coded creatively to look realistic even though they only work in the specific instances inside the game.
-AILEE is a demo, and there is much opportunity to expand the game into something far more complex and realistic if enough time and energy was dedicated to doing so.
+AILEE is a demo, but there is much opportunity to expand the game into something far more complex and realistic if enough time and energy was dedicated to doing so.
 
 \begin{thebibliography}{00}
-\bibitem{b1} Repl.it, ``The world's leading online coding platform,'' repl.it. [Online]. Available: \url{https://repl.it/site/features}. [Accessed: 02-May-2019].
+\bibitem{b1} G. Haataja, D. Wilson, and M. Turnbull, “AILEE,” repl.it, 18-Apr-2019. [Online]. Available: \url{https://repl.it/@grantHaataja/AILEE}.
 
-\bibitem{b2} A.
+\bibitem{b2} Repl.it, ``The world's leading online coding platform,'' repl.it. [Online]. Available: \url{https://repl.it/site/features}. [Accessed: 02-May-2019].
+
+\bibitem{b3} A.
 M.
@@
 [Accessed: 02-May-2019].
+
 \end{thebibliography}

### 2019-05-06 csci487/project/paper.tex
Ooopsie
Signed-off-by: Grant Haataja <grant.haataja@gmail.com>

@@
 
-The user is encouraged to try out the various possible commands, which can be displayed using the \textit{help} command.
+The user is encouraged to try out the various possible commands, which can be displayed using the \texttt{help} command.
 The story continues after the user has ran ten commands, (they can be the same or different commands, it doesn't matter).
@@
 
-Above is the code for the \textit{exploit} command in the game.
+Above is the code for the \texttt{exploit} command in the game.
 In terms of options, it does not compare to the Metasploit framework, but the goal was to create it to feel similarly in the terminal environment.
@@
 	\centerline{\includegraphics[scale=2]{exploit-pic}}
-	\caption{Running the \textit{exploit} executable}
+	\caption{Running the \texttt{exploit} executable}
 	\label{fig:exploit-pic}
@@
 Each event after that has a condition that must be met to trigger it.
-The second event runs after ten commands have been run, the third event runs after the \textit{pscan} command runs, and so on.
+The second event runs after ten commands have been run, the third event runs after the \texttt{pscan} command runs, and so on.
 Each event runs instructions for the user that should allow them to trigger the next event and progress in the game.
@@
 
-This is the text for the third event (Fig. \ref{fig:event3}), which triggers after the user runs the command \textit{pscan} against the first target IP address.
+This is the text for the third event (Fig. \ref{fig:event3}), which triggers after the user runs the command \texttt{pscan} against the first target IP address.
 
@@
 Each computer has a unique filesystem, with directories and files.
-As time was limited, the \textit{bin} and \textit{log} directories were left empty on all computers, but the \textit{home} directories all have files in them that either pertain to the gameplay or exist for comedic value or storyline development.
+As time was limited, the \texttt{bin} and \texttt{log} directories were left empty on all computers, but the \texttt{home} directories all have files in them that either pertain to the gameplay or exist for comedic value or storyline development.
 
-To navigate the filesystems, the traditional Linux commands \textit{ls} and \textit{cd} are used, as well as the commands \textit{read} and \textit{run}, which display file text and run executable files, respectively.
+To navigate the filesystems, the traditional Linux commands \texttt{ls} and \texttt{cd} are used, as well as the commands \texttt{read} and \texttt{run}, which display file text and run executable files, respectively.
 
@@
 \ref{fig:ls-command}).
-Unlike a real Linux terminal, the \textit{ls} command only works in the current directory and takes no arguments.
+Unlike a real Linux terminal, the \texttt{ls} command only works in the current directory and takes no arguments.
 

### 2019-05-26 past_classes/csci260/wordCountingApp/twitter.tex
The semester is over

--- 2019-05-04 csci260/wordCountingApp/twitter.tex
@@
 \tab In order to collect the tweet data for the analysis, this study chose to use the Twitter API [2].
-This required a twitter developer account, and security keys to access the API using HTTP requests.
+This required a twitter developer account and security keys to access the API using HTTP requests.
 A twitter developer was created, and the project was registered under Twitter to get the access keys.
-\tab After aquiring the access keys, the project utilized the command line program "Twurl" to send Twitter search requests to the API.
+
+After acquiring the access keys, the project utilized the command line program "Twurl" to send Twitter search requests to the API.
 Results were returned in a json file format.
-Unfortunately, because the project didn't aquire the premium form of the Twitter API, each search request was limited to 15 results.
-\tab Because of this, the project was instead composed of a hundred seperate search requests, using Wikipedia's list of the most common words in english [3].
+Unfortunately, because the project didn't acquire the premium form of the Twitter API, each search request was limited to 15 results.
+
+Because of this, the project was instead composed of a hundred separate search requests, using Wikipedia's list of the most common words in English [3].
 Then, a python script was created to parse the json files retrieved, and search the tweets for the profane words.
@@
 \lstinputlisting[language=Python]{jsonreader.py}
-The following picture shows the output of the above code when ran on the 100 json files that were created from the queries.
 
@@
 \end{figure}
+
+The above picture shows the output of the above code when ran on the 100 json files that were created from the queries.
 
@@
 \tab Below are the recorded percentages of various profanity from the 1136 tweets in the sample size. A total of 37 tweets were found to be profane.
-
 \begin{figure}[h]
-	\includegraphics[scale=1]{Figure_1}
+	\includegraphics[scale=.7]{Figure_1}
 \end{figure}
 
+\newpage
 Shown in the next chart are the actual numbers of occurrences of the various profanity in the 37 profane tweets found from the sample.
@@
 	Wikimedia Foundation. (2018, December 12). Most common words in English. 
-	Retrieved from {https://en.wikipedia.org/wiki/Most_common_words_in_English}
+	Retrieved from {https://en.wikipedia.org/wiki/Most\_common\_words\_in\_English}
 

### 2020-02-13 csci364/hw1/src/HaatajaGrant_NumberGuessClient.java
Fixed the merge conflict from hell
Signed-off-by: Haataja <grant.haataja@undcemlh110-07l.ad.und.edu>

@@ -1,0 +1,67 @@
+//CSCI364 Assignment 1 Client
+//Grant Haataja
+
+import java.util.Random;
+import java.net.ServerSocket;
+import java.net.Socket;
+import java.io.IOException;
+import java.net.UnknownHostException;
+import java.io.PrintWriter;
+import java.io.BufferedReader;
+import java.io.InputStreamReader;
+
+public class HaatajaGrant_NumberGuessClient {
+	public static void main(String[] args) {
+		//verify user-entered arguments
+		if ((args.length != 2) || Integer.parseInt(args[1]) <= 0) {
+			System.err.println("Usage: java HaatajaGrant_NumberGuessClient" + 
+				" <host name> <port number>");
+			System.exit(0);
+		}
+		
+		String hostName = args[0];
+		int portNumber = Integer.parseInt(args[1]);
+		
+		try {
+			//make new Socket object and connect to the server
+			Socket guessSocket = new Socket(hostName, portNumber);
+			
+			//set up PrintWriter stuff
+			PrintWriter out = 
+				new PrintWriter(guessSocket.getOutputStream(), true);
+			BufferedReader in = new BufferedReader(
+				new InputStreamReader(guessSocket.getInputStream()));
+			BufferedReader stdIn = new BufferedReader(
+				new InputStreamReader(System.in));
+			
+			//print welcome message
+			System.out.println(in.readLine());
+			System.out.println(in.readLine());
+			System.out.println(in.readLine());
+			System.out.println(in.readLine());
+			
+			String userInput;
+			String temp;
+			while ((userInput = stdIn.readLine()) != null) {
+				out.println(userInput);
+				temp = in.readLine();
+				if (temp.contains("correct")) {
+					System.out.println(temp);
+					System.exit(0);
+				}
+				else {
+					System.out.println(temp);
+				}	
+			}
+			//catch exceptions because I can't catch a ball
+		} catch (UnknownHostException e) {
+			System.err.println("Couldn't find host " + hostName);
+			System.exit(0);
+		} catch (IOException e) {
+			System.err.println("Input/Output failure for connection to " + 
+				hostName);
+			System.exit(0);
+		} 
+	
+	}
+}

### 2020-02-13 csci364/hw1/src/HaatajaGrant_NumberGuessServer.java

@@ -1,0 +1,88 @@
+//CSCI364 Assignment 1 Server
+//Grant Haataja
+
+import java.util.Random;
+import java.net.ServerSocket;
+import java.net.Socket;
+import java.io.IOException;
+import java.io.PrintWriter;
+import java.io.BufferedReader;
+import java.io.InputStreamReader;
+
+public class HaatajaGrant_NumberGuessServer {
+	public static void main(String[] args) {
+		//verify user-entered arguments
+		if ((args.length != 2) || Integer.parseInt(args[0]) <= 0 || 
+			Integer.parseInt(args[1]) <= 0) {
+			System.err.println("Usage: java HaatajaGrant_NumberGuessServer" + 
+				" <port number> <maximum value>");
+			System.exit(0);
+		}
+		//declare the port number
+		int portNumber = Integer.parseInt(args[0]);
+		
+		//select random target integer
+		Random randy = new Random();
+		int target = randy.nextInt(Integer.parseInt(args[1]));
+		
+		//server outer loop
+		while (true) {
+		
+			try {
+				//make new serverSocket object
+				ServerSocket serverSocket = new ServerSocket(portNumber);
+			
+				System.out.println("NumberGuessServer is listening at: " + 
+					serverSocket.getInetAddress() + " on port " + 
+					serverSocket.getLocalPort());
+			
+				//wait for client	
+				Socket clientSocket = serverSocket.accept();
+			
+				//set up PrintWriter stuff
+				PrintWriter out = 
+					new PrintWriter(clientSocket.getOutputStream(), true);
+				BufferedReader in = new BufferedReader(
+					new InputStreamReader(clientSocket.getInputStream()));
+			
+				//send welcome message
+				out.println("Welcome to the High-Low Guessing Game.\n");
+				out.println("Enter an integer greater than 0 and less than " + 
+					Integer.parseInt(args[1]) + ".\n");
+			
+				//after receiving response from client, check against target
+				String input;
+				int guesses = 0;
+				while ((input = in.readLine()) != null) {
+					System.out.println("Server received: " + input);
+					int number = -1;
+					try {
+						number = Integer.parseInt(input);
+					} catch (Exception e) {
+						System.err.println("Invalid input: Enter an integer.");
+					}
+					//do the checking
+					if (number < target) {
+						out.println("Guess higher.");
+						guesses++;
+					}
+					else if (number > target) {
+						out.println("Guess lower.");
+						guesses++;
+					}
[…]

### 2020-02-13 csci364/playground/Deadlock.java

@@ -1,0 +1,37 @@
+public class Deadlock { 
+	static class Friend { 
+		private final String name; 
+		public Friend(String name) { 
+			this.name = name; 
+		} 
+		public String getName() { 
+			return name; 
+		} 
+		public synchronized void bow(Friend bower) { 
+			System.out.format("%s: %s has bowed to me!%n",name,bower.getName()); 
+			bower.bowBack(this); 
+		} 
+		public synchronized void bowBack(Friend bower) { 
+			System.out.format("%s: %s has bowed back to me!%n",
+				this.name, bower.getName()); 
+        } 
+	}
+		
+	public static void main(String[] args) { 
+		final Friend alphonse = new Friend("Alphonse"); 
+		final Friend gaston = new Friend("Gaston"); 
+		Runnable r1 = new Runnable() { 
+			public void run() { 
+			alphonse.bow(gaston); 
+			} 
+        };
+        
+		new Thread(r1).start(); 
+		Runnable r2 = new Runnable() { 
+			public void run() { 
+			gaston.bow(alphonse); 
+			} 
+		};
+		new Thread(r2).start(); 
+	} 
+}

### 2020-02-13 csci364/playground/HelloRunnable.java

@@ -1,0 +1,22 @@
+public class HelloRunnable implements Runnable {
+
+	private int val;
+	
+	public HelloRunnable(int val) {
+	this.val = val;
+	}
+
+	public void run() {
+		String name = Thread.currentThread().getName();
+		System.out.println("Hello from thread " + name +
+			". My val is " + val);
+	}
+
+	public static void main(String[] args) {
+		for (int i = 0; i < 5; i++) {
+			Runnable runnable = new HelloRunnable(i);
+			Thread thread = new Thread(runnable);
+			thread.start();
+		}
+	}
+}

### 2020-02-13 csci364/playground/hello.cpp

@@ -1,0 +1,30 @@
+#include<iostream>
+#include<thread>
+#include<sstream>
+
+int num_threads = 10;
+void hello(int tid) {
+	std::ostringstream oss;oss << "Hello from thread " << tid << std::endl;
+	std::cout << oss.str();
+}
+
+int main(int argc, char *argv[]) {
+	// keep track of the threads
+	std::thread t[num_threads];
+	
+	// launch the threads
+	for (int i = 0; i < num_threads; i++) {
+		t[i] = std::thread(hello, i);
+	}
+
+	std::ostringstream oss;
+	oss << "Hello from main" << std::endl;
+	std::cout << oss.str();
+
+	// have main wait for the hello threads
+	for (int i = 0; i < num_threads; i++) {
+		t[i].join();
+	}
+
+	return 0;
+}

### 2020-02-13 csci364/secureclient/src/SecureClient.java

@@ -1,0 +1,47 @@
+// Grant Haataja
+
+import java.io.*;
+import java.net.*;
+import javax.net.ssl.*;
+
+public class SecureClient {
+    public static void main(String[] args) throws IOException {
+        
+        if (args.length != 2) {
+            System.err.println(
+                "Usage: java EchoClient <host name> <port number>");
+            System.exit(1);
+        }
+
+        String hostName = args[0];
+        int portNumber = Integer.parseInt(args[1]);
+        
+        SSLSocketFactory factory = 
+        	(SSLSocketFactory)SSLSocketFactory.getDefault();
+
+        try {
+            SSLSocket socket = 
+            	(SSLSocket)factory.createSocket(hostName, portNumber);
+            
+            PrintWriter out = 
+            	new PrintWriter(socket.getOutputStream(), true);
+            BufferedReader in = new BufferedReader(
+                    new InputStreamReader(socket.getInputStream()));
+            BufferedReader stdIn = new BufferedReader(
+                    new InputStreamReader(System.in));
+
+            String userInput;
+            while ((userInput = stdIn.readLine()) != null) {
+                out.println(userInput);
+                System.out.println("echo: " + in.readLine());
+            }
+        } catch (UnknownHostException e) {
+            System.err.println("Don't know about host " + hostName);
+            System.exit(1);
+        } catch (IOException e) {
+            System.err.println("Couldn't get I/O for the connection to " +
+                hostName);
+            System.exit(1);
+        } 
+    }
+}

### 2020-02-13 csci364/secureclient/src/SecureServer.java

@@ -1,0 +1,47 @@
+//Grant Haataja
+//In-Class Exercise
+
+import java.net.*;
+import java.io.*;
+import javax.net.ssl.*;
+
+public class SecureServer {
+    public static void main(String[] args) throws IOException {
+       if (args.length != 1) {
+            System.err.println("Specify a port number.");
+            System.exit(1);
+        }
+        
+        int portNumber = Integer.parseInt(args[0]);
+        
+        SSLServerSocketFactory factory = 
+        	(SSLServerSocketFactory)SSLServerSocketFactory.getDefault();
+        
+        try {
+            SSLServerSocket serverSocket = 
+            	(SSLServerSocket)factory.createServerSocket(portNumber);
+
+            System.out.println("The server is listening at: " + 
+                    serverSocket.getInetAddress() + " on port " + 
+                    serverSocket.getLocalPort());
+
+            SSLSocket clientSocket = (SSLSocket)serverSocket.accept();  
+               
+            PrintWriter out =
+                new PrintWriter(clientSocket.getOutputStream(), true);                   
+            BufferedReader in = new BufferedReader(
+                new InputStreamReader(clientSocket.getInputStream()));
+
+            String inputLine;
+            while ((inputLine = in.readLine()) != null) {
+                System.out.println("I received: " + inputLine);
+
+                out.println(inputLine.toUpperCase());
+            }
+        } catch (IOException e) {
+            System.out.println("Exception caught when trying to listen on port "
+                + portNumber + " or listening for a connection");
+            System.out.println(e.getMessage());
+        }
+    }
+}

### 2020-02-13 csci365/Program1/Program1.java

@@ -1,0 +1,82 @@
+//Grant Haataja
+//Program 1
+import java.util.Random;
+public class Program1 {
+	//function to fill the array
+	static void fillArray(int[] arr) {
+		//instantiate random
+		Random randy = new Random();
+		
+		int temp = 0;
+		for (int i = 0; i < arr.length; i++) {
+			temp = randy.nextInt(101);
+			arr[i] = temp;
+		}
+	}	
+	//function to find and return highest value in array
+	static int findHighest(int[] arr) {
+		int max = 0;
+		for (int i = 0; i < arr.length; i++) {
+			if (arr[i] > max) {
+				max = arr[i];
+			}
+		}
+		return max;
+	}
+	//function to find and return lowest value in array
+	static int findLowest(int[] arr) {
+		int min = 100;
+		for (int i = 0; i < arr.length; i++) {
+			if (arr[i] < min) {
+				min = arr[i];
+			}
+		}
+		return min;
+	}
+	//function to find and return average value in array
+	static double findAverage(int[] arr) {
+		double avg = 0.0;
+		double sum = 0.0;
+		for (int i = 0; i < arr.length; i++) {
+			sum += arr[i];
+			avg = sum / arr.length;
+		}
+		return avg;
+	}
+	//function to print counting values and the array values
+	static void printValues(int[] arr) {
+		System.out.println("\nValues");
+		for (int i = 0; i < arr.length; i++) {
+			System.out.printf("%2d " + " %3d\n", i+1, arr[i]);
+		}
+	}
+		
+	public static void main(String args[]) {
+		//create array
+		int[] dopeArray = new int[20];
+		
+		//call function to fill array with random values
+		fillArray(dopeArray);
+		
+		//call function to return high value of array
+		int highValue = findHighest(dopeArray);
+		
+		//print highest value
+		System.out.print("High value " + highValue + "\n");
+		
+		//call function to return low value of array
+		int lowValue = findLowest(dopeArray);
+
+		//print lowest value
+		System.out.print("Low value " + lowValue + "\n");
+		
+		//call function to return average value of array
+		double avgValue = findAverage(dopeArray);
+		
+		//print average value
+		System.out.print("Average " + avgValue + "\n");
+		
+		//call function to print out the values of array
+		printValues(dopeArray);	
+	}
+}

### 2020-02-13 csci365/Program2/Program2.java

@@ -1,0 +1,26 @@
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.io.FileNotFoundException;
+
+public class Program2 {
+	public static void main(String[] args) throws IOException {
+		String fileName = args[0];
+		
+		try {
+			File f = new File(fileName);     
+			System.out.println("File name: " + f.getName());
+			System.out.println("Is writeable: " + f.canWrite());
+			System.out.println("Is readable: " + f.canRead());
+			System.out.println("Is a directory: " + f.isDirectory());
+			System.out.println("File size in bytes: " + f.length());
+		} catch (FileNotFoundException e) {
+			System.err.println(e);
+		}
+	
+			BufferedReader br = new BufferedReader(new InputStreamReader(System.in));
+		
+
+	}
+}

### 2020-02-13 past_classes/complete/csci161/Driver.java

@@ -1,0 +1,640 @@
+/* Lab 9
+ * Name: Grant Haataja
+ * Date: 11/02/18
+ */
+import java.util.*;
+import java.io.*;
+import java.awt.Desktop;
+
+public class Driver {
+	static ArrayList<Opponent> opponentArray = new ArrayList<Opponent>();
+	static boolean fubar = true;	
+	
+	// Method to display map to screen (Lab 5) (Lab 6)
+	public static void displayMap(Room[][] map) {
+		for (int i = 0; i < map.length; ++i) {
+			//print left boundary for map
+			System.out.print("|");
+			for (int j = 0; j < map.length; ++j) {
+				//get ID for each space of map to print corresponding symbol
+				switch (map[i][j].getID()) {
+					case -1: 
+						System.out.print("#"); //wall
+					break;
+						
+					case 0:
+						System.out.print(" "); //empty space
+					break;
+						
+					case 1:
+						System.out.print("@"); //player character
+					break;
+					
+					case 2:
+						System.out.print("!"); //enemy character
+					break;
+					
+					case 3:
+						System.out.print("*"); //end goal
+					break;
+						
+					default:
+						System.out.print("?"); //error
+					break;
+				}	
+			}	
+			//print right boundary for map
+			System.out.println("|");
+		}
+	}
+	
+	//Starting Menu method (Lab 8)
+	public static char mainMenu(Scanner scnr) {
+		System.out.println("Welcome to Pizza Run!");
+		System.out.println();
+		System.out.println("Press 'N' to start new game");
+		System.out.println("Press 'L' to load game from file");
+		System.out.println("Press 'Z' to save game at any time");
+		
+		//get user input
+		char input = scnr.nextLine().charAt(0);
+		return input;
+	}
+	
+	//Method to load map from file (Lab 8)
+	public static void loadMap(Player playerCharacter, Room[][] map) {
+		Scanner mapScnr = null; 
+		Scanner newScnr = new Scanner(System.in);
+		String fileName = "";
+		//variable to make sure code doesn't run twice
+		fubar = true;
+		
+		//try to open file (Lab 9)
+		System.out.println("Enter file name in the form of file.txt");
+		System.out.println(fileName);
+		fileName = newScnr.nextLine();
+		System.out.println("Opening file " + fileName + "...");
+			
+		try {
+			File mapFile = new File(fileName);
+			mapScnr = new Scanner(mapFile);
+		} catch (FileNotFoundException excpt) {
[…]

### 2020-02-13 past_classes/complete/csci161/HistogramViewer.java

@@ -1,0 +1,19 @@
+import javax.swing.JFrame;
+
+public class HistogramViewer {
+   public static void main(String[] args) {
+      JFrame appFrame = new JFrame();
+      HistogramComponent histogramComponent = new HistogramComponent();
+
+      appFrame.setSize(400, 600);
+      //appFrame.pack();
+      appFrame.setTitle("Histogram Viewer");
+      appFrame.setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
+      
+      // Add the HistogramComponent object to the frame
+      appFrame.add(histogramComponent);
+      
+      // Set the frame and its contents visible
+      appFrame.setVisible(true);
+   }
+}

### 2020-02-13 past_classes/complete/csci161/InvalidMoveException.java

@@ -1,0 +1,11 @@
+public class InvalidMoveException extends Exception {
+
+	public InvalidMoveException() {
+        super("Please input the move command again"); 
+    }
+    
+    public InvalidMoveException(String stuff) {
+        super(stuff); 
+    }
+}
+

### 2020-02-13 past_classes/complete/csci161/Junk/Helloo.java

@@ -1,0 +1,37 @@
+
+/* CSCI 161 Lab 1: Helloo
+ * Name: Grant Haataja
+ * Date: 08/29/18 */
+
+import java.util.Scanner;
+
+public class Helloo {
+	public static void main(String[] args) {
+		Scanner scnr = new Scanner(System.in);
+		int getNum;
+
+		System.out.println("What is your name, friend: ");
+		String userName = scnr.nextLine(); // Receives Name from user
+
+		System.out.println("Give me a number less than 10 and greater than 5: ");
+		getNum = scnr.nextInt(); // Takes number between 5 and 10 from user
+
+		if ((getNum > 5) && (getNum < 10)) {
+
+			/*
+			 * The following lines print the information to the computer screen and
+			 * calculate the basic Math functions
+			 */
+
+			System.out.println("Hello, " + userName + " ,");
+			System.out.println("you have input the number: " + getNum);
+			System.out.println("your number divided by 2 is: " + (getNum / 2.0));
+			System.out.println("your number plus 5 is: " + (getNum + 5));
+			System.out.println("your number squared is " + (Math.pow(getNum, 2)));
+
+		} else {
+			System.out.println("that number is not in the right range, silly ");
+			System.exit(0);
+		}
+	}
+}

### 2020-02-13 past_classes/complete/csci161/Junk/Randomm.java

@@ -1,0 +1,24 @@
+import java.util.Random;
+
+public class Randomm {
+   public static void main (String[] args) {
+      Random randGen = new Random(); //New random number generator 
+	  
+	  int dice1;
+	  int dice2;
+	  int dice3;
+	  int dice4;
+	  
+	  dice1 = randGen.nextInt(6) + 1; // Simulates a D6
+	  dice2 = randGen.nextInt(6) + 1;
+	  dice3 = randGen.nextInt(6) + 1;
+	  dice4 = randGen.nextInt(20) + 1; //Simulates a D20
+	  
+	  System.out.println("dice1 rolls a " + dice1);
+	  System.out.println("dice2 rolls a " + dice2);
+	  System.out.println("dice3 rolls a " + dice3);
+	  System.out.println("dice4 rolls a " + dice4);
+
+	   
+   }
+}   

### 2020-02-13 past_classes/complete/csci161/Junk/StatsRoll.java

@@ -1,0 +1,154 @@
+/* Lab 2 - Stats Roll
+ * Name: Grant Haataja
+ * Date: 09/05/18
+ */
+
+import java.util.Random;
+
+public class StatsRoll {
+	
+	//public global variables
+	char createCharacter; // stores variable to confirm or deny character creation
+	int strength;
+	int dexterity;
+	int constitution;
+	int intelligence
+	int wisdom;
+	int charisma;
+	String nameOfCharacter;
+	int statsAvg = 0;
+	
+	//object constructor takes in user-typed name
+	public StatsRoll(String inputName) {
+		
+		//assign inputName to a variable
+		nameOfCharacter = inputName;
+	
+		//generate stats
+		Random rndm = new Random(); // new random number generator
+		strength = roll();
+		dexterity = roll();
+		constitution = roll();
+		intelligence = roll();
+		wisdom = roll();
+		charisma = roll();
+		String nameOfCharacter;
+		statsAvg = (strength + dexterity + constitution + intelligence + wisdom + charisma)/6;
+		
+		
+	}
+	
+	
+	//public method to get stats value
+	public int getstatsAvg() {
+		return statsAvg;
+	}
+	
+	public String getnameOfCharacter() {
+		return nameOfCharacter;
+	}
+
+
+		// The following statements check user decision to create character and run program
+
+        // ask if user wants to create character
+
+        System.out.println("To create new character, press a");
+		System.out.println("To exit, press b");
+
+		while (true) {
+
+            createCharacter = scnr.nextLine().charAt(0);
+    
+			if (createCharacter == 'a') {
+				
+				System.out.println("Enter your character's name: "); // get character name
+				nameOfCharacter = scnr.nextLine();
+				
+				 // print results to the screen
+				
+				System.out.println("Bathe in the glory of " + nameOfCharacter + "!");
+				System.out.println();
+				System.out.println("Your strength is " + strength);
+				System.out.println("Your dexterity is " + dexterity);
+				
+				System.out.println("Your constitution is " + constitution);
+				System.out.println("Your intelligence is " + intelligence);
+				System.out.println("Your wisdom is " + wisdom);
+				System.out.println("Your charisma is " + charisma);
+				System.out.println();
+				
+				// compute average stats and print result to screen
+				
[…]

### 2020-02-13 past_classes/complete/csci161/NewCharacter.java

@@ -1,0 +1,169 @@
+/* Lab 9
+ * Name: Grant Haataja
+ * Date: 11/02/18
+ */
+import java.util.Random;
+
+public class NewCharacter {
+		
+	//private and protected variables
+	protected int strength;
+	protected int dexterity;
+	protected int constitution;
+	protected int intelligence;
+	protected int wisdom;
+	protected int charisma;
+	protected String nameOfCharacter;
+	protected int totalStats = 0;
+	//hitpoint and armor class variables (Lab 4)
+	protected int hitPoints;
+	protected int armorClass;
+	
+	//create public integers to store X and Y coordinates of player character (Lab 6)
+	public int xPlayerVal = 0;
+	public int yPlayerVal = 0;
+	
+	//CHARACTER CREATION: default constructor if user does not input a name 
+	public NewCharacter() {
+		//assign inputName to a variable
+		nameOfCharacter = "";
+		//generate random stats
+		strength = roll();
+		dexterity = roll();
+		constitution = roll();
+		intelligence = roll();
+		wisdom = roll();
+		charisma = roll();
+		//calculate total stat value	
+		totalStats = (strength + dexterity + constitution + intelligence 
+			+ wisdom + charisma);	
+		//generate hipoints
+		hitPoints = 10 + ((constitution - 10) / 2);
+	}
+	
+	//CHARACTER CREATION: object constructor takes in user-typed name
+	public NewCharacter(String inputName) {
+		//assign inputName to a variable
+		nameOfCharacter = inputName;
+		//generate random stats
+		strength = roll();
+		dexterity = roll();
+		constitution = roll();
+		intelligence = roll();
+		wisdom = roll();
+		charisma = roll();
+		//calculate total stat value	
+		totalStats = (strength + dexterity + constitution + intelligence 
+			+ wisdom + charisma);	
+		//generate hipoints
+		hitPoints = 10 + ((constitution - 10) / 2);	
+	}
+	
+	//method to display information about character (Lab 6)
+	public String toString() {
+	    String output = "";
+	    output = ("" + nameOfCharacter + "\'s Stats: \n");
+	    output += ("Strength: " + strength + "\n");
+	    output += ("Dexterity: " + dexterity + "\n");
+	    output += ("Constitution: " + constitution + "\n");
[…]

### 2020-02-13 past_classes/complete/csci161/NewDriver.java

@@ -1,0 +1,91 @@
+/* Lab 10
+ * Name: Grant Haataja
+ * Date: 11/14/18
+ */
+import java.util.*;
+
+public class NewDriver {
+	public static void main(String[] args) {
+		
+		//create new linked list of characters
+		LinkedList<NewCharacter> characterList = new LinkedList<NewCharacter>();
+		
+		//create queue and deque
+		Queue<NewCharacter> pleaseHold = new LinkedList<NewCharacter>();
+		Deque<NewCharacter> yourCallIsImportantToUs = new LinkedList<NewCharacter>();
+		
+		//create and add 10 characters to list
+		NewCharacter themis = new NewCharacter("Themis");
+		characterList.add(themis);
+		NewCharacter atlas = new NewCharacter("Atlas");
+		characterList.add(atlas);
+		NewCharacter prom = new NewCharacter("Prometheus");
+		characterList.add(prom);
+		NewCharacter hecate = new NewCharacter("Hecate");
+		characterList.add(hecate);
+		NewCharacter epim = new NewCharacter("Epimetheus");
+		characterList.add(epim);
+		NewCharacter meno = new NewCharacter("Menoetius");
+		characterList.add(meno);
+		NewCharacter hype = new NewCharacter("Hyperion");
+		characterList.add(hype);
+		NewCharacter theia = new NewCharacter("Theia");
+		characterList.add(theia);
+		NewCharacter iape = new NewCharacter("Iapetus");
+		characterList.add(iape);
+		NewCharacter crius = new NewCharacter("Crius");
+		characterList.add(crius);
+		
+		int count = 1;
+		
+		//for loop to print stats of each character
+		for (NewCharacter characterName : characterList) {
+			System.out.println(characterName);
+			if (count % 2 == 0) {
+				pleaseHold.add(characterName);
+			}
+			else {
+				yourCallIsImportantToUs.add(characterName);
+			}
+			count++;
+		}
+		
+		//for loop to display contents of queue
+		System.out.println("Contents of Queue: ");
+		System.out.println();		
+		for (NewCharacter characterName : pleaseHold) {
+			System.out.println(characterName);
+		}
+		//for loop to display contents of deque
+		System.out.println("Contents of Deque: ");
+		System.out.println();
+		for (NewCharacter characterName : yourCallIsImportantToUs) {
+			System.out.println(characterName);
+		}
+		
+		//remove 3 characters from the queue
+		pleaseHold.poll();
[…]

### 2020-02-13 past_classes/complete/csci161/Player.java

@@ -1,0 +1,24 @@
+/* Lab 9
+ * Name: Grant Haataja
+ * Date: 11/02/18
+ */
+public class Player extends Character {
+
+	//CHARACTER CREATION: default constructor if user does not input a name 
+	public Player() {
+		armorClass = 15 + ((dexterity - 10) / 2);
+	}
+
+	//CHARACTER CREATION: object constructor takes in user-typed name
+	public Player(String inputName) {
+		//assign inputName to a variable
+		nameOfCharacter = inputName;
+		armorClass = 15 + ((dexterity - 10) / 2);	
+	}
+	
+	//set character name
+	public String setName(String input) {
+		nameOfCharacter = input;
+		return nameOfCharacter;
+	}
+}

### 2020-02-13 past_classes/complete/csci161/Room.java

@@ -1,0 +1,22 @@
+/* Lab 7
+ * Name: Grant Haataja
+ * Date: 10/17/18
+ */
+public class Room {
+	
+	//public global variables
+	int roomID = 0;
+	public Character opponent;
+	
+	//constructor to set ID number for each space on map
+	public Room(int ID) {
+		roomID = ID;
+	}
+	
+	//FIXME add toString() method to display room information?
+	
+	//method to get ID number for each space on map for generating map
+	public int getID() {
+		return roomID;
+	}
+}

### 2020-02-13 past_classes/complete/csci161/SubCharacter.java

@@ -1,0 +1,28 @@
+public class SubCharacter extends Character {
+
+	public SubCharacter () {
+		armorClass = 15 + ((dexterity - 10) / 2);
+	}
+	
+	//CHARACTER CREATION: object constructor takes in user-typed name
+	public SubCharacter(String inputName) {
+		//assign inputName to a variable
+		nameOfCharacter = inputName;
+		armorClass = 15 + ((dexterity - 10) / 2);	
+	}
+	
+	@Override
+	public String toString(){
+			String string = "My name is definitely not : "+nameOfCharacter
+				+" and these are definitely not my stats,\n";
+			string += "["+strength+", "+dexterity+", "+constitution+", "+intelligence
+				+", "+wisdom+", "+charisma+"]\n";
+			if(hitPoints <= 0){
+				string += "I'm so alive right now\n";
+			}else{
+				string += "I'm almost dead with only "+hitPoints+" HP left\n";
+			}
+			return string;
+		}
+
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/HistogramComponent.java

@@ -1,0 +1,37 @@
+import java.awt.Color;
+import java.awt.Graphics;
+import java.awt.Graphics2D;
+import java.awt.Rectangle;
+import javax.swing.JComponent;
+
+// HistogramComponent extends the functionality of a JComponent
+// in order to draw a histogram.
+public class HistogramComponent extends JComponent {
+   
+   // Paints a histogram with three bins
+   public void paintComponent(Graphics g) {  
+      // Cast to Graphics2D
+      Graphics2D graphicsObj = (Graphics2D) g;
+      
+      // Draw 1st bin as an olive colored rectangle at (10,10)
+      // with width = 200 and height = 50
+      Rectangle binRectangle1 = new Rectangle(10, 10, 150, 150); 
+      Color binColor1 = new Color(250, 0, 0);
+      graphicsObj.setColor(binColor1);
+      graphicsObj.fill(binRectangle1);
+      
+      // Draw 2nd bin as a teal blue rectangle at (10,75)
+      // with width = 150 and height = 50
+      Rectangle binRectangle2 = new Rectangle(10, 200, 150, 150); 
+      Color binColor2 = new Color(0, 70, 70);
+      graphicsObj.setColor(binColor2);
+      graphicsObj.fill(binRectangle2);
+      
+      // Draw 3rd bin as a gray rectangle at (10,140)
+      // with width = 350 and height = 50
+      Rectangle binRectangle3 = new Rectangle(10, 400, 150, 150); 
+      Color binColor3 = new Color(150, 0, 100);
+      graphicsObj.setColor(binColor3);
+      graphicsObj.fill(binRectangle3);
+   }
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Datum.java

@@ -1,0 +1,84 @@
+import java.util.Scanner;
+
+public class Datum {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		int day = scn.nextInt();
+		int month = scn.nextInt();
+		String weekday = "";
+		int[] year = new int[365];
+		int count = 4;
+		int tracker = 0;
+		
+		//fill array
+		for (int i = 0; i < 365; i++) {
+			year[i] = count % 7;
+			count++;
+		}
+			
+		//find position
+		if (month == 1) {
+			tracker = year[day-1];
+		}
+		else if (month == 2) {
+			tracker = year[day+31-1];
+		}
+		else if (month == 3) {
+			tracker = year[day+31+28-1];
+		}
+		else if (month == 4) {
+			tracker = year[day+31+28+31-1];
+		}
+		else if (month == 5) {
+			tracker = year[day+31+28+31+30-1];
+		}
+		else if (month == 6) {
+			tracker = year[day+31+28+31+30+31-1];
+		}
+		else if (month == 7) {
+			tracker = year[day+31+28+31+30+31+30-1];
+		}
+		else if (month == 8) {
+			tracker = year[day+31+28+31+30+31+30+31-1];
+		}
+		else if (month == 9) {
+			tracker = year[day+31+28+31+30+31+30+31+31-1];
+		}
+		else if (month == 10) {
+			tracker = year[day+31+28+31+30+31+30+31+31+30-1];
+		}
+		else if (month == 11) {
+			tracker = year[day+31+28+31+30+31+30+31+31+30+31-1];
+		}
+		else if (month == 12) {
+			tracker = year[day+31+28+31+30+31+30+31+31+30+31+30-1];
+		}
+		
+		if (tracker == 6) {
+			weekday = "Saturday";
+		}
+		else if (tracker == 0) {
+			weekday = "Sunday";
+		}
+		else if (tracker == 1) {
+			weekday = "Monday";
+		}
+		else if (tracker == 2) {
+			weekday = "Tuesday";
+		}
+		else if (tracker == 3) {
+			weekday = "Wednesday";
+		}
+		else if (tracker == 4) {
+			weekday = "Thursday";
+		}
+		else if (tracker == 5) {
+			weekday = "Friday";
+		}
+		System.out.print(weekday);
+		
+		
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Dice.java

@@ -1,0 +1,32 @@
+import java.util.Scanner;
+
+public class Dice {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		int dice1 = scn.nextInt();
+		int dice2 = scn.nextInt();		
+		int bound1 = dice1 + 1;
+		int bound2 = dice2 + 1;
+		int number = 0;
+		
+		if (bound1 == bound2) {
+			System.out.println(bound1);
+		}
+		else if (bound1 < bound2) {
+			number = bound1;
+			while (number <= bound2) {
+				System.out.println(number);
+				number++;
+			}
+		}
+		else {
+			number = bound2;
+			while (number <= bound1) {
+				System.out.println(number);
+				number++;
+			}
+		}		
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Filip.java

@@ -1,0 +1,35 @@
+import java.util.Scanner;
+
+public class Filip {
+	
+	//method to reverse 3-digit numbers
+	public static int reverseNumber(Scanner scn, int number) {
+		
+		int digit1 = number % 10;
+		number = number / 10;
+		int digit10 = number % 10;
+		int digit100 = number / 10;
+		int newNumber = (digit1 * 100) + (digit10 * 10) + digit100;
+		
+		return newNumber;	
+	}
+	
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		int num1 = scn.nextInt();
+		int num2 = scn.nextInt();
+		
+		//reverse the 2 numbers
+		int newNumber1 = reverseNumber(scn, num1);
+		int newNumber2 = reverseNumber(scn, num2);
+		
+		//compare reversed numbers and print greatest value
+		if (newNumber1 > newNumber2) {
+			System.out.print(newNumber1);
+		}
+		else
+			System.out.print(newNumber2);
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Grass.java

@@ -1,0 +1,32 @@
+import java.util.Scanner;
+
+public class Grass {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		double cost = scn.nextDouble();
+		int numLawns = scn.nextInt();
+		double[][] dimensions = new double[numLawns][2];
+		double[] area = new double[numLawns];
+		double totalArea = 0;
+		double totalCost = 0; 
+		
+		//loop to get width (i) and length (j) of the lawns
+		for (int i = 0; i < numLawns; i++) {
+			for (int j = 0; j < 2; j++) {
+				dimensions[i][j] = scn.nextDouble();
+			}
+		}
+		
+		//loop to calculate areas
+		for (int i = 0; i < numLawns; i++) {
+			area[i] = dimensions[i][0] * dimensions[i][1];
+			totalArea += area[i];
+		}
+		
+		totalCost = cost * totalArea;
+		System.out.printf("%10.7f",totalCost);
+		
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Ladder.java

@@ -1,0 +1,20 @@
+import java.util.Scanner;
+
+public class Ladder {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		short wallHeight = scn.nextShort();	
+		byte ladderAngle = scn.nextByte();
+		double convert = (Math.PI / 180.0);
+		int ladderLength = 0;
+		ladderLength = (int)(wallHeight / (Math.sin(ladderAngle * convert)));
+		
+		if (Math.abs((wallHeight / (Math.sin(ladderAngle * convert))) - ladderLength) > 0.000000000000001) {
+			System.out.print(ladderLength + 1);
+		}
+		else 
+			System.out.print(ladderLength);
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/NastyHacks.java

@@ -1,0 +1,37 @@
+import java.util.Scanner;
+
+public class NastyHacks {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		int numCases = scn.nextInt(); //number of cases given to test
+		int [] baseRevenue = new int[numCases];
+		int [] advRevenue = new int[numCases];
+		int [] advCost = new int[numCases];
+		
+		//loop to get input
+		for (int i = 0; i < numCases; i++) {
+			baseRevenue[i] = scn.nextInt(); //expected revenue without advertising
+			advRevenue[i] = scn.nextInt(); //expected revenue with advertising
+			advCost[i] = scn.nextInt(); //cost of advertising
+		}
+		
+		//calculate and display results
+		for (int i = 0; i < numCases; i++) {
+			
+			//advertise
+			if (baseRevenue[i] < (advRevenue[i] - advCost[i])) {
+				System.out.println("advertise");
+			}
+			//does not matter
+			else if (baseRevenue[i] == (advRevenue[i] - advCost[i])) {
+				System.out.println("does not matter");
+			}
+			//do not advertise
+			else {
+				System.out.println("do not advertise");
+			}
+		}
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Odd.java

@@ -1,0 +1,23 @@
+import java.util.Scanner;
+
+public class Odd {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//get input
+		int cases = scn.nextInt();
+		int[] numbers = new int[cases];
+		
+		for (int i = 0; i < cases; i++) {
+			numbers[i] = scn.nextInt();
+		}
+		
+		for (int i = 0; i < cases; i++) {
+			if (numbers[i] % 2 == 0) {
+				System.out.println(numbers[i] + " is even");
+			}
+			else 
+				System.out.println(numbers[i] + " is odd");
+		}		
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Pet.java

@@ -1,0 +1,46 @@
+import java.util.Scanner;
+
+public class Pet {
+	
+	//method to get input and calculate score for contestants
+		public static int getScore(Scanner scn) {
+			int score1 = scn.nextInt();
+			int score2 = scn.nextInt();
+			int score3 = scn.nextInt();
+			int score4 = scn.nextInt();
+			
+			return (score1 + score2 + score3 + score4);
+		
+		}	
+	
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//declare variables for each of the 5 players
+		int player1 = getScore(scn);
+		int player2 = getScore(scn);
+		int player3 = getScore(scn);
+		int player4 = getScore(scn);
+		int player5 = getScore(scn);
+		int[] player = new int[] {player1, player2, player3, player4, player5};
+		int winner =  player[0];
+		int playerNum = 1;
+		
+		if (player1 == player2 && player2 == player3 && player3 == player4 && player4 == player5) {
+			System.out.print("1 " + player1);
+		}
+		else {
+			//compare player scores to find the winning player
+			for (int i = 1; i < player.length; i++) {
+				if (winner < player[i]) {
+					winner = player[i];
+					playerNum = i+1;
+				}
+			}
+		
+			//print output
+			System.out.print(playerNum + " " + winner);
+		}
+	
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Planina.java

@@ -1,0 +1,20 @@
+import java.util.Scanner;
+
+public class Planina {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);	
+		
+		//get input (number of iterations)
+		int iterations = scn.nextInt();
+		int sidePoints = 2;
+		
+		//count number of points on one side
+		for (int i = 0; i < iterations; i++) {
+			sidePoints = sidePoints + (sidePoints - 1);
+		}
+		
+		// calculate and print answer
+		System.out.println(sidePoints * sidePoints);
+		
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/SevenWonders.java

@@ -1,0 +1,45 @@
+import java.util.*;
+
+public class SevenWonders { 
+    public static void main(String[] args) {
+    Scanner scnr = new Scanner(System.in);
+    
+        //get input and declare variables
+        String playerCards = scnr.nextLine();
+        int numTablets = 0;
+        int numCompasses = 0;
+        int numGear = 0;
+        int playerScore = 0;
+    
+        //loop to calculate number of cards
+        for (int i = 0; i < playerCards.length(); ++i)  {
+            if (playerCards.charAt(i) == 'T') {
+                ++numTablets;
+            }
+            if (playerCards.charAt(i) == 'C') {
+                ++numCompasses;
+            }
+            if (playerCards.charAt(i) == 'G') {
+                ++numGear;
+            }
+        }   
+        //declare counting variables to count combos
+        int countT = numTablets;
+        int countC = numCompasses;
+        int countG = numGear;
+        int numCombos = 0;
+        
+        //loop to calculate number of combos
+        while (countT != 0 && countC != 0 && countG != 0) {
+            --countT;
+            --countC;
+            --countG;
+            ++numCombos;
+        }
+        //calculate and output player score
+        playerScore = ((int)Math.pow(numTablets, 2) + (int)Math.pow(numCompasses, 2) + 
+        (int)Math.pow(numGear, 2)) + numCombos * 7;
+        System.out.print(playerScore); 
+    }
+
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Spavanac.java

@@ -1,0 +1,34 @@
+import java.util.*;
+
+public class Spavanac {
+    public static void main(String[] args) {
+    Scanner scnr = new Scanner(System.in);
+    
+    // declare variable and get input
+    int hours = scnr.nextInt();
+    int minutes = scnr.nextInt();
+    int temp;
+    
+    // easy case where time is 45 minutes or more
+    if (minutes > 44) {
+        minutes = minutes - 45;
+        System.out.print(hours + " " + minutes);
+    }
+    // harder case where minutes is less than 45 and hours must change
+    else if (hours > 0) {
+        temp = 45 - minutes;
+        minutes = 60 - temp;
+        hours = hours - 1;
+        System.out.print(hours + " " + minutes);
+    }
+    // other harder case where minutes is less than 45 and hours is at 0
+    else if (hours == 0) {
+        temp = 45 - minutes;
+        minutes = 60 - temp;
+        hours = 23;
+        System.out.print(hours + " " + minutes);
+    }
+    
+    }
+
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Workspace.java

@@ -1,0 +1,34 @@
+import java.util.Scanner;
+
+public class Workspace {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);
+		
+		//scan in number of stars on the flag
+		int stars = scn.nextInt();
+		int row1 = 2;
+		int row2 = 1;
+		int col = 0;
+		int count = stars;
+		
+		//print out the leading stuff
+		System.out.println(stars + ":");
+		
+		for (int i = 0; i < (stars / 2) + 1; i++) {
+			for (int j = 0; j < stars / 2; j++) {
+				if (stars % (row1 + row2 + row1) == 0) {
+					System.out.println(row1 + "," + row2);
+				} 
+				else if (stars % row1 == 0 && stars % row2 == 0) {
+					System.out.println(row1 + "," + row2);
+				}
+				else if (stars % (row1 + row2) == 0) {
+					System.out.println(row1 + "," + row2);
+				}
+				row2++;
+			}
+			row1++;
+		}
+	
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/Katiss/Zanzibar.java

@@ -1,0 +1,36 @@
+import java.util.Scanner;
+import java.util.ArrayList;
+
+public class Zanzibar {
+	public static void main(String[] args) {
+		Scanner scn = new Scanner(System.in);	
+	
+		//get input 
+		int testCases = scn.nextInt();
+		
+		//loop through all test cases
+		for (int i = 0; i < testCases; i++) {
+			//create array list booklet of total number of turtles every new year's day
+			ArrayList<Integer> booklet = new ArrayList<Integer>();
+			int numElements = 0; //variable to count number of elements (turtles) in the bookletr
+			//test to see if there is more numbers
+			int temp = scn.nextInt(); //variable to store keyboard input and compare it
+			while (temp != 0) {
+				//compare to check for end of test case
+				booklet.add(temp); //add element to array list
+				numElements++; //count number of elements in array list
+				temp = scn.nextInt(); 
+			}
+			//once a zero is reached and booklet contains a single entire test case
+			int importCount = 0; //number of turtles who imported to Zanzibar
+			//parse through booklet
+			for (int j = 0; j < numElements - 1; j++) {
+				//if the number of turtles could occur naturally, do nothing
+				if (booklet.get(j+1) > ((booklet.get(j)) * 2)) {
+					importCount += booklet.get(j+1) - (booklet.get(j) * 2);
+				}
+			}
+			System.out.println(importCount);
+		}
+	}
+}

### 2020-02-13 past_classes/complete/csci161/WorkSpace/SalaryLabelGUI.java

@@ -1,0 +1,100 @@
+import java.awt.GridBagConstraints;
+import java.awt.GridBagLayout;
+import java.awt.Insets;
+import javax.swing.JFrame;
+import javax.swing.JLabel;
+import javax.swing.JTextField;
+
+public class SalaryLabelGUI {
+
+   public static void main(String[] args) {
+      int hourlyWage; 
+      int yearlyBonus;            
+      JFrame topFrame = null;                // Application window
+      JLabel wageLabel = null;               // Label for hourly salary
+      JLabel salLabel = null;   			 // Label for yearly salary
+      JLabel bonusLabel = null;              // Label for yearly bonus
+      JTextField salField = null;            // Displays hourly salary 
+      JTextField wageField = null;           // Displays yearly salary
+      JTextField bonusField = null;			 // Displays yearly bonus
+      GridBagConstraints layoutConst = null; // GUI component layout
+
+      hourlyWage = 20;
+      yearlyBonus = 1000;
+
+      // Set hourly and yearly salary
+      wageLabel = new JLabel("Hourly wage:");
+      salLabel = new JLabel("Yearly salary:");
+      bonusLabel = new JLabel("Yearly bonus:");
+
+      wageField = new JTextField(15);
+      wageField.setEditable(false);
+      wageField.setText(Integer.toString(hourlyWage));
+
+      salField = new JTextField(15);
+      salField.setEditable(false);
+      salField.setText(Integer.toString((hourlyWage * 40 * 50)));
+      
+      bonusField = new JTextField(15);
+      bonusField.setEditable(false);
+      bonusField.setText(Integer.toString(yearlyBonus));
+
+      // Create frame and add components using GridBagLayout
+      topFrame = new JFrame("Salary and Shit");
+      
+      // Use a GridBagLayout
+      topFrame.setLayout(new GridBagLayout());
+
+      // Create GridBagConstraints
+      layoutConst = new GridBagConstraints();
+      
+      // Specify component's grid location
+      layoutConst.gridx = 0;
+      layoutConst.gridy = 0;
+      
+      // 10 pixels of padding around component
+      layoutConst.insets = new Insets(10, 10, 10, 10);
+      
+      // Add component using the specified constraints
+      topFrame.add(wageLabel, layoutConst);
+
+      layoutConst = new GridBagConstraints();
[…]

### 2020-02-13 past_classes/complete/engr_200/A9_grant_haataja.m

@@ -1,0 +1,106 @@
+%**************************************************************************
+%ENGR 200-02                                                DATE:12/05/2017
+% 
+%ASSIGNMENT: #9                         Author: Grant Haataja
+%**************************************************************************
+
+%PROGRAM DESCRIPTION:
+%This program will load input file of river data containing days data was
+%collected, river heights in meters, and river velocitie in meters per
+%second squared. It will then transpose and size the matrix, and compute
+%average heights and velocities, maximum and minimum heights and
+%velocities, matrix locations of maximums and minimums, river flow rate,
+%and volume of water over a one-year period. Finally this program will
+%develop a plot for flow rate versus time. The results will be printed to
+%the Command Window.
+
+%VARIABLE DESCRIPTIONS:
+%NAME         | TYPE   | DESCRIPTION
+%--------------------------------------------------------------------------
+%riv          | double  | transposed 2-dimensional matrix from input file
+%flowrate     | double | one-dimensional matrix for flowrate in cubic m /s
+%width        | double | channel width in meters
+%volume       | double | volume of water in cubic meters for 1 year period
+%avht         | double | average height
+%avvel        | double | average velocity
+%minht        | double | minimum height
+%minvel       | double | minimum velocity
+%maxht        | double | maximum height
+%maxvel       | double | maximum velocity
+%minhtrow     | double | row location for minimum height
+%minhtcol     | double | column location for minimum height
+%maxhtrow     | double | row location for maximum height
+%maxhtcol     | double | column location for maximum height
+%minvelrow    | double | row location for minimum velocity
+%minvelcol    | double | column location for minimum velocity
+%maxvelrow    | double | row location for maximum velocity
+%maxvelcol    | double | column location for maximum velocity
+%k            | int    | outer for loop control variable
+%m            | int    | inner for loop control variable
+%**************************************************************************
+
+%Clear Command Window, clear memory, and close plots
+clc
+clear
+close all
+
+%Load input file
+load river.txt;
+
+%Transpose matrix
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 1/2_1_grant_haataja.cpp

@@ -1,0 +1,66 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 09/05/2017
+
+PROGRAM: #1                               Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This program will allow the user to calculate intermediate  coefficients of lift 
+by   inputting  2  angles  of  attack,  2  known  coefficients  of  lift, and an 
+interpolate angle. The results are printed to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME        | TYPE     | DESCRIPTION                                
+--------------------------------------------------------------------------------
+com_co_lift | double   | computed coefficient of lift
+co_lift1    | double   | first known coefficient of lift
+co_lift2    | double   | second known coefficient of lift
+int_angle   | double   | interpolation angle in degrees
+angle1      | double   | first angle in degrees
+angle2      | double   | second angle in degrees	
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+
+    /* Declare variables */
+    double com_co_lift, co_lift1, co_lift2, int_angle, angle1, angle2;
+    
+    /* Print main heading */
+    printf("******************************************");
+    printf("\n       LINEAR INTERPOLATION PROGRAM");
+    
+    /* Input values */
+    printf("\n\nEnter first angle in degrees        : ");
+    scanf("%lf",&angle1);
+    printf("Enter first coefficient of lift     : ");
+    scanf("%lf",&co_lift1);
+    printf("Enter second angle in degrees       : ");
+    scanf("%lf",&angle2);
+    printf("Enter second coefficient of lift    : ");
+    scanf("%lf",&co_lift2);
+    printf("Enter interpolation angle in degrees: ");
+    scanf("%lf",&int_angle);
+
+    /* Compute linear interpolation value */
+    com_co_lift = ((co_lift2-co_lift1)*(int_angle-angle1)/(angle2-angle1))+co_lift1;
+    
+    /* Print output values */
+    printf("\n\nRESULTS");
+    printf("\nFirst angle in degrees         = %6.3f ",angle1);
+    printf("\nFirst coefficient of lift      = %6.3f ",co_lift1);
+    printf("\n\nSecond angle in degrees        = %6.3f ",angle2);
+    printf("\nSecond coefficient of lift     = %6.3f ",co_lift2);
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 2/2_2_grant_haataja.cpp

@@ -1,0 +1,89 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 09/12/2017
+
+PROGRAM: #2                               Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION
+This  program  will use known cylinder radius and spherical cap  radius to 
+allow user to  calulate cylinder height, spherical  cap height, surface area 
+and total volume of concrete needed for building. Results are printed to the 
+computer screen.
+
+DESCRIPTION OF VARIABLES
+NAME    | TYPE     | DESCRIPTION 
+--------------------------------------------------------------------------------
+r_cyl   | double   | Inner radius of cylinder in feet
+r_cap   | double   | Inner radius of spherical cap in feet
+h_cyl   | double   | Height of cylindrical portion in feet
+h_cap   | double   | Height of inner spherical cap in feet
+v_cap   | double   | Inner volume spherical cap
+h_cap2  | double   | Height of spherical cap including wall thickness in feet
+r_cap2  | double   | Radius of spherical cap including wall thickness in feet 
+r_cyl2  | double   | Radius of clylindrical portion plus wall thickness in feet 
+pi      | symbolic | Value for pi  
+s_inner | double   | Inner surface area of the building in square feet
+wll_thk | double   | Wall thickness in feet
+v_bldng | double   | Inner volume of the building in cubic feet 
+theta   | double   | Angle theta for cap in degrees  
+alpha   | double   | Angle alpha for cap plus wall thickness in degrees
+v_conc  | double   | Total volume of concrete needed    
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+
+/* Main function */
+int main(void)
+{
+
+    /* Declare variables */
+    double r_cyl, r_cap, h_cyl, h_cap, v_cap, h_cap2, r_cap2, r_cyl2, s_inner,
+	       wll_thk, v_bldng, theta, alpha, v_conc;
+
+    /* Print main heading */
+    printf("********************************************************");
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 3/2_3_grant_haataja.cpp

@@ -1,0 +1,105 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 09/26/2017
+
+PROGRAM: #3                               Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This  program  will allow  the user  to obtain  useful seismic  readings for oil 
+exploration  by  computing  specific  ratios between depth of hole and amount of 
+dynamite. It will read in values from an input file, calculate the hole to depth
+ration, ideal number of sticks,  ideal powder charge, actual powder charge,  and 
+the actual number of sticks. The results will be printed to the  computer screen
+and to an output data file.
+
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+sn      | integer  | well site number from first column of input file
+hd      | double   | hole depth of well from second column of input file
+ipthdr  | double   | ideal powder to hole depth ratio
+inos    | double   | ideal number of sticks of dynamite
+ipc     | double   | ideal powder charge
+i       | integer  | loop control variable
+anos    | integer  | actual number of sticks of dynamite
+apc     | integer  | actual powder charge
+ndata   | integer  | number of record lines in the input file
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define inputfile "u:\\engr 200\\oil_explore.txt"
+#define outputfile "u:\\engr 200\\oil_report.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double hd, ipthdr, inos, ipc;
+   int i, sn, anos, apc, ndata;
+   FILE *oile, *oilr;
+
+   /* Open input & output files */
+   oile = fopen(inputfile,"r");
+   oilr = fopen(outputfile,"w");
+   
+   /* Verify input file */
+   if(oile == NULL)
+   {
+      printf("\n\nERROR READING INPUT FILE\n\nPROGRAM TERMINATED\n\n");
+      return 0;
+   }
+   
+   /* Read control number */
+   fscanf(oile,"%i",&ndata);
+   
+   /* Print main headings and column headings */
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 4/2_4_grant_haataja.cpp

@@ -1,0 +1,161 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 10/03/2017
+
+PROGRAM: #4                              Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This program will read radius and  height of the cylinder, the radius and height
+of the  frustrum, the control  number and  the float heights from an input file,
+and pass these values to a user-defined function. The user-defined function will
+compute  the volume  of water in cubic  meters in the tank and pass the computed 
+volume back to the main function. The results are printed to the computer screen
+and to an output file.
+         
+DESCRIPTION OF VARIABLES:
+NAME            | TYPE    | DESCRIPTION
+--------------------------------------------------------------------------------
+pi              | symbolic| value for pi
+vc              | double  | water volume of cylindrical portion
+rc              | double  | radius of the cylinder
+hf              | double  | height of the frustum
+vcf             | double  | total water volume of tank
+computed_volume | double  | computed volume of water in tank
+hc              | double  | height of the cylinder
+rw              | double  | radius of water in frustum 
+rf              | double  | raidus of frustum
+hfl             | double  | height of float
+i               | integer | for loop control variable
+ndata           | integer | number of record lines in input file
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+#define inputfile "u:\\engr 200\\Assignment 4\\water_level.txt"
+#define outputfile "u:\\engr 200\\Assignment 4\\water_volume.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double volume(double rc, double hc, double hf, double hfl);   
+   double computed_volume, vc, rc, hfl, hf, vcf, hc, rw, rf;
+   int i, ndata;
+   FILE *wlev, *wvol;
+
+   /* Open input and output files */
+   wlev = fopen(inputfile, "r");
+   wvol = fopen(outputfile, "w");
+   
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 5/2_5_grant_haataja.cpp

@@ -1,0 +1,142 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 10/10/2017
+
+PROGRAM: #5                              Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This program will read rainfall amounts from 2013 - 2017 into 5 one-dimensional
+arrays, calculate the total rainfall for each year, average rainfall for each 
+year, and determine the minimum and maximum rainfall values for the year 2015. 
+The results will be printed to the screen and an output file. 
+
+DESCRIPTION OF VARIABLES:
+NAME       | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+avg13      | double | computed average rainfall for 2013
+avg14      | double | computed average rainfall for 2014
+avg15      | double | computed average rainfall for 2015
+avg16      | double | computed average rainfall for 2016
+avg17      | double | computed average rainfall for 2017
+yr13       | double | one-dimensional array of rainfall data for year 2013
+yr14       | double | one-dimensional array of rainfall data for year 2014
+yr15       | double | one-dimensional array of rainfall data for year 2015
+yr16       | double | one-dimensional array of rainfall data for year 2016
+yr17       | double | one-dimensional array of rainfall data for year 2017
+tot13      | double | total rainfall for all months in 2013
+tot13      | double | total rainfall for all months in 2013
+tot14      | double | total rainfall for all months in 2014
+tot15      | double | total rainfall for all months in 2015
+tot16      | double | total rainfall for all months in 2016
+tot17      | double | total rainfall for all months in 2017
+min        | double | minimum rainfall for 2015
+max        | double | maximum rainfall for 2015
+i          | int    | for loop control variable
+ndata      | int    | number of months in a year
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 6/2_6_grant_haataja.cpp

@@ -1,0 +1,221 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 10/24/2017
+
+PROGRAM: #6                              Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This  program  reads  in  data  concerning  lake  powell  from an input file and 
+computes the average water height for an eight-year period. It will also compute
+the  average water  height for  each year  and for  each  month, as  well as the 
+minimum and maximum water heights for the eight-year period, and how many months
+the water level exceeded  the eight-year average. The results are printed to the 
+computer screen and an ouput file.
+
+DESCRIPTION OF VARIABLES
+NAME      | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+height    | double | two-dimensional array for heights in feet above sea level
+month     | char   | two-dimensional character array for month names
+year_avg  | double | one-dimensional array for yearly average water height
+month_avg | double | one-dimensional array for monthly average water height
+year_tot  | double | one-dimensional array for yearly avg water height values
+month_tot | double | one-dimensional array for monthly avg water height values
+minwh     | double | minimum water height above sea level value
+maxwh     | double | maximum water height above sea level value
+nrows     | int    | number of rows in the array
+ncols     | int    | number of columns in the array
+i         | int    | outer for loop control variable
+j         | int    | inner for loop control variable
+num_month | int    | number of months that exceeded avg height above sea level
+tot_wh    | double | total water height for 8 year period
+avg_wh    | double | computed average for all water height values
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define inputfile "u:\\engr 200\\lake_powell.txt"
+#define outputfile "u:\\engr 200\\lake_powell_report.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double height[12][8], year_avg[8], month_avg[12], month_tot[12], year_tot[8],
+          avg_wh, minwh, maxwh, tot_wh=0.0;
+   int i, j, nrows, ncols, num_month=0;
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 7/2_7_grant_haataja.cpp

@@ -1,0 +1,201 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 11/02/2017
+
+PROGRAM: #7                              Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This program will read data from from an input file into an array of structures,
+sort elements by atomic number, compute mean atomic weight of elements, compute
+median atomic weight of elements, determine the element with the maximum atomic
+weight, and determine the element with the minimum density. The results will be 
+printed to the computer screen and to an output file named element_report.
+
+DESCRIPTION OF VARIABLES
+NAME      | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+elem      | struct | array structure for element data
+temp      | struct | temporary structure for sorting element data
+ename     | char   | array containing element name
+sname     | char   | array containing element symbol
+anum      | int    | atomic number of element
+aweight   | double | atomic weight of element
+density   | double | density of element
+crystal   | char   | array containing crystal structure of element
+aw_avr    | double | mean atomic weight
+aw_med    | double | median atomic weight
+min_den   | char   | element with minimum density
+max_aw    | char   | element with maximum atomic weight
+aw_tot    | double | array of totals for atomic weights
+ndata     | int    | number of elements in the input file
+i         | int    | outer for loop control variable
+j         | int    | inner for loop control variable
+k         | int    | subscript variable
+min_row   | int    | row position where minimum density occurs
+max_row   | int    | row position where maximum atomic weight occurs	
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include<stdio.h>
+#include<math.h>
+#define inputfile "u:\\ENGR 200\\Assignment 7\\elements.txt"
+#define outputfile "u:\\ENGR 200\\Assignment 7\\element_report.txt"
+
+/* Define structure to represent elements */
[…]

### 2020-02-13 past_classes/complete/engr_200/Assignment 8/A8_grant_haataja.m

@@ -1,0 +1,82 @@
+%**************************************************************************
+%ENGR 200-02                                                DATE:12/05/2017
+% 
+%ASSIGNMENT: #9                         Author: Grant Haataja
+%**************************************************************************
+
+%PROGRAM DESCRIPTION:
+%This program will 
+
+%VARIABLE DESCRIPTIONS:
+%NAME         | TYPE   | DESCRIPTION
+%--------------------------------------------------------------------------
+%density      | double | density of air in kg/m^3 at sea level and 15°C
+%power10      | double | power in watts for 10% power
+%power20      | double | power in watts for 20% power
+%power40      | double | power in watts for 40% power
+%power59      | double | power in watts for 59% power
+%area         | double | swept area of rotating blades in square meters
+%speed        | double | wind speed in meters per second
+%blade_radii  | double | one-dimensional matrix for blade radii in cm
+%wind_speeds  | double | one-dimensional matrix for wind speed in mph
+%k            | int    | outer for loop control variable
+%m            | int    | inner for loop control variable
+%ofile        | char   | file location of printed output
+%**************************************************************************
+
+%Clear Command Window, clear memory, and close plots
+clc
+clear
+close all
+
+%Load input files
+load blade_radii.txt;
+load wind_speeds.txt;
+
+%Open output file
+ofile = fopen('power_results.txt','wt');
+
+%Assign air density value to a variable
+density = 1.225;
+
+%Print main heading and column headings to Command Window and output file
+fprintf('**************************************************');
+fprintf('\n      ELECTRICAL POWER CALCULATIONS IN WATTS');
+fprintf('\n\nWind(m/h)     10pct     20pct     40pct     59pct\n\n');
+fprintf(ofile,'**************************************************');
+fprintf(ofile,'\n      ELECTRICAL POWER CALCULATIONS IN WATTS');
+fprintf(ofile,'\n\nWind(m/h)     10pct     20pct     40pct     59pct\n\n');
+
+%Compute and print power output to Command Window and output file
+for k=1:1:length(blade_radii)
+    fprintf('Blade radius #%1i = %3i centimeters',k,blade_radii(k));
+    fprintf(ofile,'Blade radius #%1i = %3i centimeters',k,blade_radii(k));
+    area = pi*(blade_radii(k)*0.01)^2;
+    
+    for m=1:1:length(wind_speeds)
+        speed = (wind_speeds(m))*1609/3600;
[…]

### 2020-02-13 past_classes/complete/engr_200/Exams/exam_1_grant_haataja.cpp

@@ -1,0 +1,85 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 09/18/2017
+
+EXAM: #1                               Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This program  looks  at a situation  where a train is  heading toward a crossing 
+from south to north, and a car is heading toward the crossing from west to east.
+It  allows the  user to compute  the positions of both the  car  and  train,  as 
+well  as the distance  between them at any given time,  by entering the speed of 
+the car,  acceleration of the car,  distance of the car from the crossing, speed 
+of the train, distance of the train from the crossing, and the time. The results
+are printed to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME        | TYPE     | DESCRIPTION                                
+--------------------------------------------------------------------------------
+spe_c       | double   | Initial speed of the car in miles per hour
+acc_c       | double   | Acceleration of the car in feet per second per second
+dis_c       | double   | Initial distance of the car from the crossing in feet
+spe_t       | double   | Initial speed of the train in miles per hour
+dis_t       | double   | Initial distance of the train from the crossing in feet
+time        | double   | Time in seconds
+pos_c       | double   | Computed position of car from crossing in feet
+pos_t       | double   | Computed position of train from crossing in feet	
+vel_c       | double   | Initial speed of the car in feet per second
+vel_t       | double   | Initial speed of the train in feet per second
+distance    | double   | Computed distance between car and train 
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+	
+	/* Declare variables */
+	double spe_c, acc_c, dis_c, spe_t, dis_t, time, pos_c, pos_t, vel_c, vel_t,
+	       distance;
+	
+	/* Print main heading */
+	printf("*********************************************************");
+	printf("\n                  MOTION OF TWO VEHICLES\n\n");
+	
+	/* Input values */
+	printf("Enter the car speed in mph                : ");
[…]

### 2020-02-13 past_classes/complete/engr_200/Exams/exam_3_grant_haataja.cpp

@@ -1,0 +1,203 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 11/11/2017
+
+EXAM: #3                           Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This program will read data from from an input file into an array of structures
+and sort data by latitude degrees. It will then utilize a user-defined function
+to compute angle gamma between two cities and return gammma to the main function
+to calculate the great circle distance between pairs of cities. The results will
+be printed to the computer screen and an output file.
+
+DESCRIPTION OF VARIABLES
+NAME      | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+pi      | symbol | the value for pi
+rho     | symbol | the radius of the earth
+phi1    | double | angle phi to compute rectangular coordinates for location 1
+phi2    | double | angle phi to compute rectangular coordinates for location 2
+theta1  | double | angle theta to compute rect. coordinates for location 1
+theta2  | double | angle theta to compute rect. coordinates for location 2
+x1      | double | x-coordinate for location 1
+x2      | double | x-coordinate for location 2
+y1      | double | y-coordinate for location 1
+y2      | double | y-coordinate for location 2
+z1      | double | z-coordinate for location 1
+z2      | double | z-coordinate for location 2
+dotp    | double | dot product to compute gamma
+dist1   | double | magnitude of vector for location 1
+dist2   | double | magnitude of vector for location 2
+gamma   | double | angle between vectors 1 and 2 
+gcd     | double | great circle distance
+ndata   | int    | number of elements in the input file
+i       | int    | outer for loop control variable
+j       | int    | inner for loop control variable
+city    | struct | array structure for city data
+temp    | struct | temporary structure for sorting element data
+cname   | char   | array for city names
+latdeg  | int    | latitude degrees 
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Balloon_Mass_User_Fn.cpp

@@ -1,0 +1,130 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES A user-defined FUNCTION
+
+PROGRAM DESCRIPTION:
+This program will read pressure, volume, and temperature from an input file,
+and pass these values to a user-defined function. The user-defined function
+will compute the mass of a balloon and pass the computed value back to the
+main function.  The main function will compute the average of all the balloon
+masses.  The program will check for missing input data and count the number of
+values missing.  The results are printed to the computer screen and to an
+output file.
+         
+DESCRIPTION OF VARIABLES:
+NAME              | TYPE    | DESCRIPTION
+--------------------------------------------------------------------------------
+computed_mass     | double  | computed mass of the balloon
+balloon_mass_aver | double  | computed average balloon mass
+total_mass        | double  | computed total mass of balloons with valid data
+press             | double  | pressure inside the balloon in pounds/ft^3
+temp              | double  | temperature inside the balloon in degrees
+vol               | double  | volume of the balloon in ft^3
+i                 | integer | for loop control variable
+ndata             | integer | number of record lines in input file
+bnum              | integer | balloon number
+missing_data      | integer | missing input data in input file
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define inputfile "u:\\engr 200\\balloon.txt"
+#define outputfile "u:\\engr 200\\balloon_table.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double mass(double, double, double);
+   double computed_mass, balloon_mass_aver, total_mass=0.0, press, vol, temp;
+   int i, ndata, bnum, missing_data=0;
+   FILE *balloon, *table;
+
+   /* Open input and output files */
+   balloon = fopen(inputfile, "r");
+   table = fopen(outputfile, "w");
+   
+   /* Verify input file and read input data */
+   if(balloon == NULL)
+   {
+      printf("\n\n\nERROR OPENING INPUT FILE.");
+      printf("\n\nPROGRAM TERMINATED.\n\n\n");
+      return 0;
+   }
+   
+   /* Print headings */
+   printf("************************************************");
+   printf("\n             TABLE OF BALLOON MASSES"
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Basic_Program_Structure_1.cpp

@@ -1,0 +1,38 @@
+/*******************************************************************************        
+DEMO: BASIC PROGRAM STRUCTURE
+
+PROGRAM DESCRIPTION:
+This program requires the user to specify the length of his or her leg in feet.
+The program computes the time required for a walking stride and prints the
+results to the computer screen.
+  
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE   | DESCRIPTION                                
+--------------------------------------------------------------------------------
+leg_len | double | length of a leg in feet                                           
+time    | double | time required for a stride                                           
+pi      | double | mathematical constant                                      
+gravity | double | gravitational constant (ft/s/s)
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+   /* Declare and initialize variables */
+   double leg_len=?????, gravity=32.2, pi=3.141593, time;
+   
+   /* Calculate time */
+   time = pi*sqrt((2.0*leg_len)/(3.0*gravity));
+
+   /* Print results to computer screen */
+   printf("\n\nThe stride time is %4.2f seconds for a leg length of %3.1f "
+          "feet.\n\n\n",time,leg_len);
+
+   /* Exit program */
+   return 0;
+}
+/******************************************************************************/

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Character_1.cpp

@@ -1,0 +1,52 @@
+/*******************************************************************************
+DEMO: SIMPLE CHARACTER INPUT AND OUTPUT
+
+PROGRAM DESCRIPTION
+This program reads a character from the keyboard, computes a new character, and
+prints the results to the computer screen.                                      
+
+DESCRIPTION OF VARIABLES
+NAME          | TYPE | DESCRIPTION 
+--------------------------------------------------------------------------------
+any_character | char | a character enter from the keyboard                 
+new_character | int  | calculation of new character
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   char any_character;
+   int new_character;
+  
+   /* Get character from the keyboard */
+   printf("***************************************************");
+   printf("\nEnter a character from the keyboard: ");
+   scanf("%c",&any_character);
+  
+   /* Print character */
+   printf("\n\nThe character entered is %c",any_character);
+   printf("\nThe ASCII integer value of the character is %3i",any_character);
+   
+   /* Compute new character */
+   new_character = any_character + 7;
+
+   /* Print new character */
+   printf("\n\nThe ASCII integer value of the new character is %3i",
+          new_character);
+   printf("\nThe new character is %c",new_character);
+   printf("\n***************************************************\n\n\n");
+        
+   /* Exit the program */
+   return 0;
+}
+/******************************************************************************/
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Character_2.cpp

@@ -1,0 +1,51 @@
+/*******************************************************************************
+DEMO: SIMPLE CHARACTER INPUT AND OUTPUT USING getchar AND putchar FUNCTIONS
+
+PROGRAM DESCRIPTION:
+This program reads a character from the keyboard, computes a new character, and
+prints the results to the computer screen.                                      
+
+DESCRIPTION OF VARIABLES:
+NAME          | TYPE | DESCRIPTION 
+--------------------------------------------------------------------------------
+any_character | char | a character enter from the keyboard                 
+new_character | int  | calculation of new character
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#include <ctype.h>
+
+/* Main function */
+int main (void)
+{
+   /* Declare variables */
+   char any_character;
+   int new_character;
+  
+   /* Get character from the keyboard */
+   printf("***************************************************");
+   printf("\nEnter a character from the keyboard: ");
+   any_character = getchar();  
+  
+   /* Print character */
+   printf("\n\nThe character entered is ");
+   putchar(any_character);
+   printf("\nThe ASCII integer value of the character is %-3i",
+          any_character);
+   
+   /* Compute new character */
+   new_character = any_character + 7;
+
+   /* Print new character */
+   printf("\n\nThe ASCII integer value of the new character is %-3i",
+          new_character);
+   printf("\nThe new character is ");
+   putchar(new_character);
+   printf("\n***************************************************\n\n\n");
+        
+   /* Exit the program */
+   return 0;
+}
+/******************************************************************************/

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Math_Function.cpp

@@ -1,0 +1,74 @@
+/*******************************************************************************
+DEMO: DEMONSTRATES MATH FUNCTIONS
+
+PROGRAM DESCRIPTION
+This program computes the volume of a sphere, and the sine, cosine, and tangent
+values of an angle.  The results are printed to the computer screen.
+
+DESCRIPTION OF VARIALBES
+NAME    | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+volume  | double   | calculated volume of a sphere
+radius  | double   | radius of a sphere
+pi      | symbolic | mathematical constant
+sine    | double   | computed sin of an angle
+cosine  | double   | computed cos of an angle
+tangent | double   | compute tan of an angle
+angle   | double   | input angle in degrees
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+
+/* Main function */
+int main(void)
+{
+   /* Declare identifiers */
+   double angle, volume, radius, sine, cosine, tangent;
+
+   /* Input radius from the keyboard */
+   printf("********************************************");
+   printf("\nEnter sphere radius in feet [< 10]: ");
+   scanf("%lf",&radius);
+
+   /* Compute volume of sphere */
+   volume = 4.0/3.0*pi*pow(radius,3);
+
+   /* Print volume of the sphere */
+   printf("\n\nVolume = %7.2f cubic feet",volume);
+   printf("\n********************************************");
+   printf("\n\n********************************************");
+   
+   /* Enter angle */
+   printf("\nEnter angle in degrees: ");
+   scanf("%lf",&angle);
+   
+   /* Compute sine, cosine, and tangent */
+   sine = sin(angle*pi/180.0);
+   cosine = cos(angle*pi/180.0);
+   tangent = tan(angle*pi/180.0);
+   
+   /* Print angle, sine, cosine, and tangent */
+   printf("\nSine of %3.1f degrees    = %6.4f\nCosine of %3.1f degrees  = %6.4f"
+          "\nTangent of %3.1f degrees = %6.4f",angle,sine,angle,cosine,
+          angle,tangent);
+   printf("\n********************************************\n\n\n");
+   
+   /* Exit the program */
+   return 0;
+}
+/******************************************************************************/
+
+
+
+
+
+
+
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_PC_System_Limits.cpp

@@ -1,0 +1,46 @@
+/*******************************************************************************
+Demo: PC System Analysis
+
+This program determines PC system limitations for integer and floating-point
+numbers using Bloodshed's Dev-C++ 5.8.3 compiler.  The results are printed to
+the computer screen.                    
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <limits.h>
+#include <float.h>
+
+/* Main Function */
+int main(void)
+{
+  /* Print main heading */
+  printf("\n*********************************************");
+  printf("\n            PC SYSTEM LIMITATIONS");
+  printf("\n (using Bloodshed's Dev C++ 5.8.3 compiler)");
+  
+  /* Print integer type maximums */
+  printf("\n\nShort integer maximum: %5i",SHRT_MAX);
+  printf("\nInteger maximum      : %10i",INT_MAX);
+  printf("\nLong integer maximum : %10i",LONG_MAX);
+  
+  /* Print float precision, range, maximum */
+  printf("\n\nFloat precision digits: %1i",FLT_DIG);
+  printf("\nFloat maximum exponent: %2i",FLT_MAX_10_EXP);
+  printf("\nFloat maximum         : %13.6e",FLT_MAX);
+  
+  /* Print double precision, range, maximum */
+  printf("\n\nDouble precision digits: %2i",DBL_DIG);
+  printf("\nDouble maximum exponent: %3i",DBL_MAX_10_EXP);
+  printf("\nDouble maximum         : %13.6e",DBL_MAX);
+  
+  /* Print long precision, range, maximum */
+  printf("\n\nLong double precision digits: %2i",LDBL_DIG);
+  printf("\nLong double maximum exponent: %4i",LDBL_MAX_10_EXP);
+  printf("\nLong double maximum         : %13.6e",LDBL_MAX);
+  printf("\n*********************************************\n\n\n");
+  
+  /* Exit program */
+  return 0;
+}
+/******************************************************************************/

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Polar1_Read_From_File_Control_Number.cpp

@@ -1,0 +1,76 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES READING FROM AN INPUT DATA FILE USING A
+      "control" NUMBER AND A "for" LOOP.
+
+PROGRAM DESCRIPTION:
+This program will convert cartesian coordinates to polar coordinates.  It will
+read the cartesian data from an input data file and it will print the cartesian
+and polar data to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+xcoord  | double   | cartesian x coordinate
+ycoord  | double   | cartesian y coordinate
+radius  | double   | calculated polar coordinate
+radians | double   | calculated arc value
+degrees | double   | calculated polar coordinate
+i       | integer  | loop control variable
+ndata   | integer  | number of data record lines in the input file
+pi      | symbolic | mathematical constant
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+#define inputfile "u:\\engr 200\\xy_coordinates.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double xcoord, ycoord, radius, radians, degrees;
+   int i, ndata;
+   FILE *xy;
+  
+   /* Open input file */
+   xy = fopen(inputfile,"r");
+     
+   /* Verify input file */
+   if(xy == NULL)
+   {
+      printf("\n\nERROR OPENING INPUT FILE"
+             "\n\nPROGRAM TERMINATED\n\n");
+      return 0;
+   }
+   
+   /* Read control number from input file */
+   fscanf(xy,"%i",&ndata);
+      
+   /* Print main headings to computer screen */
+   printf("******************************************");
+   printf("\n  CONVERSION TABLE -- CARTESIAN TO POLAR"
+          "\n\n  Cartesian                  Polar"
+          "\n  X       Y          Radius     Angle(deg)");
+      
+   /* Read x-y coordinates, compute polar coordinates, and print results */
+   for(i=1; i<=ndata; i++)
+   {
+      fscanf(xy,"%lf,%lf",&xcoord,&ycoord);
+      radius = sqrt(pow(xcoord,2) + pow(ycoord,2));
+      radians = atan2(ycoord,xcoord);
+      degrees = radians *180.0/pi;
+      printf("\n%5.1f   %5.1f      %8.3f      %8.3f",
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Polar2_Read_From_File_Sentinel_Number.cpp

@@ -1,0 +1,72 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES READING FROM AN INPUT FILE USING A "while" LOOP
+      AND A "sentinel" NUMBER.
+
+PROGRAM DESCRIPTION:
+This program will convert cartesian coordinates to polar coordinates.  It will
+read the cartesian data from an input data file and it will print the cartesian
+and polar data to the computer screen.
+   
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+xcoord  | double   | cartesian x coordinate
+ycoord  | double   | cartesian y coordinate
+radius  | double   | calculated polar coordinate
+radians | double   | calculated arc value
+degrees | double   | calculated polar coordinate
+pi      | symbolic | math constant
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+#define inputfile "u:\\engr 200\\xy_coordinates.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double xcoord, ycoord, radius, radians, degrees;
+   FILE *xy;
+   
+   /* Open input file */
+   xy = fopen(inputfile,"r");
+   
+   /* Verify input file */
+   if(xy == NULL)
+   {
+      printf("\n\n\nERROR OPENING INPUT FILE.");
+      printf("\n\nPROGRAM TERMINATED.\n\n\n");
+      return 0;
+   }
+   
+   /* Print main headings to computer screen */
+   printf("******************************************");
+   printf("\n  CONVERSION TABLE -- CARTESIAN TO POLAR"
+          "\n\n  Cartesian                  Polar"
+          "\n  X       Y          Radius     Angle(deg)");
+   
+   /* Read first x-y coordinates from input file */
+   fscanf(xy,"%lf,%lf",&xcoord,&ycoord);
+               
+   /* Compute polar coordinates, print results, and read more x-y data */
+   while(xcoord!=-999.0 && ycoord!=-999.0)
+   {
+      radius = sqrt(pow(xcoord,2) + pow(ycoord,2));
+      radians = atan2(ycoord,xcoord);
+      degrees = radians *180.0/pi;
+      printf("\n%5.1f   %5.1f       %8.3f     %8.3f",
+             xcoord,ycoord,radius,degrees);
+      fscanf(xy,"%lf,%lf",&xcoord,&ycoord);
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Polar3_Read_From_Write_To_File.cpp

@@ -1,0 +1,94 @@
+/*******************************************************************************
+ENGR 200.02                                                     DATE: 09/26/2017
+
+PROGRAM: #3                               Author: Grant Haataja
+********************************************************************************
+
+PROGRAM DESCRIPTION:
+This  program  will allow  the user  to obtain  useful seismic  readings for oil 
+exploration  by  computing  specific  ratios between depth of hole and amount of 
+dynamite. It will read in values from an input file, calculate the hole to depth
+ration, ideal number of sticks,  ideal powder charge, actual powder charge,  and 
+the actual number of sticks. The results will be printed to the  computer screen
+and to an output data file.
+
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+xcoord  | double   | cartesian x coordinate
+ycoord  | double   | cartesian y coordinate
+radius  | double   | calculated polar coordinate
+radians | double   | calculated arc value
+degrees | double   | calculated polar coordinate
+i       | integer  | loop control variable
+ndata   | integer  | number of record lines in the input file
+pi      | symbolic | math constant
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+#define inputfile "u:\\engr 200\\xy_coordinates.txt"
+#define outputfile "u:\\engr 200\\polar_coordinates.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double xcoord, ycoord, radius, radians, degrees;
+   int i, ndata;
+   FILE *xy, *polar;
+
+   /* Open input & output files */
+   xy = fopen(inputfile,"r");
+   polar= fopen(outputfile,"w");
+   
+   /* Verify input file */
+   if(xy == NULL)
+   {
+      printf("\n\n\nERROR OPENING INPUT FILE.");
+      printf("\n\nPROGRAM TERMINATED.\n\n\n");
+      return 0;
+   }
+   
+   /* Read control number */
+   fscanf(xy,"%i",&ndata);
+   
+   /* Print main headings and column headings */
+   printf("******************************************");
+   printf("\n  CONVERSION TABLE -- CARTESIAN TO POLAR"
+          "\n\n  Cartesian                  Polar"
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Power_Plant.cpp

@@ -1,0 +1,125 @@
+/*******************************************************************************
+DEMO: DEMONSTRATION OF ONE-DIMENSIONAL ARRAYS
+
+PROGRAM DESCRIPTION:
+This program reads identification numbers and power output for 10 power plants
+into two one-dimensional arrays.  Average, minimun, and maximum power is
+computed.  The number of days power output is greater than average is also
+determined.  The program prints a composite report summarizing power plant
+output data to the computer screen and an output file.
+
+DESCRIPTION OF VARIABLES:
+NAME       | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+average    | double | computed average of all power output
+power_data | int    | one-dimensional array of power data
+plant_id   | int    | one-dimensional array of plant ID numbers
+minimum    | int    | minimum power output
+maximum    | int    | maximum power output
+total      | int    | summation of all power output
+i          | int    | for loop control variable
+ndays      | int    | number of days power is greater than average
+ndata      | int    | number of power plants
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define inputfile "u:\\engr 200\\power_plant.txt"
+#define outputfile "u:\\engr 200\\plant_report.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare and initialize variables */
+   double average;
+   int i, ndata, ndays=0, total=0, minimum, maximum, plant_id[10], 
+        power_data[10];
+   FILE *power, *report;
+
+   /* Open input and output files */
+   power = fopen(inputfile,"r");
+   report = fopen(outputfile,"w");
+
+   /* Verify input file */
+   if(power == NULL)
+   {
+      printf("\n\nERROR OPENING INPUT FILE");
+      printf("\n\nPROGRAM TERMINATED\n\n");
+      return 0;
+   }
+   
+   /* Read control number */
+   fscanf(power,"%i",&ndata);
+      
+   /* Read input data into array */
+   for (i=0; i<=ndata-1; i++)
+   {
+   	fscanf(power,"%i %i",&plant_id[i],&power_data[i]);
+   }
+
+   /* Compute total power and find the minimum and maximum power values */
+   minimum = power_data[0];
+   maximum = power_data[0];
+   for(i=0; i<=ndata-1; i++)
+   {
+   	  total = total+power_data[i];
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Power_Plant_Cooling.cpp

@@ -1,0 +1,157 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES A TWO-DIMENSIONAL ARRAY
+
+PROGRAM DESCRIPTION:
+This program computes the average horsepower that a power plant uses for
+multiple flow rates and cooling loops.  It determines the minimum and maximum
+horsepower values, and determines the associated cooling loop and flow rate
+for the minimum and maximum values.  A report is printed to the computer screen.
+
+DESCRIPTION OF VARIABLES
+NAME      | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+hpower    | double | two-dimensional array for horsepower values
+flow_tot  | double | one-dimensional array for flow rate totals in gps
+flow_aver | double | one-dimensional array for computed average flow rates
+cloop     | char   | two-dimensional character array for cooling loop names
+minhp     | double | minimum horsepower value
+maxhp     | double | maximum horsepower value
+nrows     | int    | number of rows in the array
+ncols     | int    | number of columns in the array
+i         | int    | outer for loop control variable
+j         | int    | inner for loop control variable
+minloop   | int    | cooling loop containing minimum horsepower
+minflow   | int    | flow rate containing minimum horsepower
+maxloop   | int    | cooling loop containing maximum horsepower
+maxflow   | int    | flow rate containing maximum horsepower
+avehp     | double | computed average for all horsepower values
+totalhp   | double | total for all horsepower values
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define inputfile "u:\\engr 200\\horsepower.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double minhp, maxhp, avehp, totalhp=0.0, hpower[5][6], flow_tot[6]={0.0},
+          flow_aver[6];
+   int i, j, nrows, ncols, minloop, minflow, maxloop, maxflow;
+   char cloop[5][10];
+   FILE *power;
+
+   /* Open input file */
+   power = fopen(inputfile,"r");
+   
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Programming_With_Structures_2.cpp

@@ -1,0 +1,138 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES PROGRAMMING USING AN ARRAY OF defined-data-
+      structures.
+
+PROGRAM DESCRIPTION:
+This program will read hurricane data from an input file, average the hurricane
+categories, and sort the hurricanes by year.  The program will determine the
+number of hurricanes that occurred in the Atlantic and the number that occurred
+in the Gulf.  The hurricane data, the average category, and the numbers of
+hurricanes by ocean are printed to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME      | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+hname     | char   | array containing a hurricane name
+ocean     | char   | originating ocean
+year      | int    | year the hurricane occurred
+category  | int    | hurricane category
+ndata     | int    | number of hurricanes in the input file
+i         | int    | outer for loop control variable
+j         | int    | inner for loop control variable
+avercat   | int    | average of all hurricane categories
+totalcat  | int    | total of all hurricane categories
+atlantic  | int    | number of Atlantic hurricanes
+gulf      | int    | number of Gulf hurricanes
+hurri     | struct | array structure for hurricane data
+temporary | struct | temporary structure for sorting hurricane data
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define inputfile "u:\\engr 200\\hurricanes.txt"
+
+/* Define the structure to represent a hurricane */
+struct hurricane
+{
+	char hname[9], ocean;
+	int year, category;
+};
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   struct hurricane hurri[7], temporary;
+   int ndata, i, j, totalcat=0, gulf=0, atlantic=0, avercat;
+   FILE *storms;
+
+   /* Open input file */
+   storms = fopen(inputfile,"r");
+   
+   /* Verify input file */
+   if(storms == NULL)
+   {
+      printf("\n\nERROR OPENING INPUT FILE.");
+      printf("\n\nPROGRAM TERMINATED.\n\n");
+      return 0;
+   }
+   
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Rocket_Do_While_Loop.cpp

@@ -1,0 +1,61 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES THE "do/while" LOOP STRUCTURE
+
+                         do
+                         {
+                            statements;
+                         }while(condition); <--- Must end with a semicolon.
+                         
+PROGRAM DESCRIPTION:
+This program simulates rocket flight by calculating distance, velocity, and
+acceleration, where time is in seconds with increments of one second.  The
+results are printed to the computer screen.  
+ 
+DESCRIPTION OF VARIABLES:
+NAME  | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+time  | double | time in seconds
+accel | double | calculated rocket acceleration in ft/sec^2
+velo  | double | calculated rocket velocity in ft/sec
+dist  | double | calculated rocket distance traveled in feet
+*******************************************************************************/
+               
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double accel, velo, dist, time=0.0;
+
+   /* Print main headings and column headings */
+   printf("********************************************"
+          "\n          ROCKET FLIGHT SIMULATION"
+          "\n\nTIME    ACCELERATION    VELOCITY    DISTANCE"
+          "\n(sec)    (ft/sec^2)     (ft/sec)      (ft)");
+
+   /* Calculate acceleration, velocity, distance, and print results */
+   do
+   {
+      accel = 4.25 - 0.015*pow(time,2);
+      velo = 4.25*time - .005*pow(time,3);
+      dist = 90.0 + 2.125*pow(time,2) - 0.00125*pow(time,4);
+      printf("\n%4.1f     %7.2f        %7.2f    %8.2f",
+             time, accel, velo, dist);
+      time++;
+	}while(time <= 25.0);
+   printf("\n********************************************\n\n\n");
+        
+   /* Exit program */
+   return 0;
+}
+/******************************************************************************/
+
+
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Rocket_For_Loop.cpp

@@ -1,0 +1,58 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES THE "for" LOOP STRUCTURE
+
+         for(expression_1;expression_2;expression_3)
+         {
+            statements;
+         }
+                         
+PROGRAM DESCRIPTION:
+This program simulates rocket flight by calculating distance, velocity, and
+acceleration, where time is in seconds with increments of one second.  The
+results are printed to the computer screen.
+ 
+DESCRIPTION OF VARIABLES:
+NAME  | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+time  | double | time in seconds
+accel | double | calculated rocket acceleration in ft/sec^2
+velo  | double | calculated rocket velocity in ft/sec
+dist  | double | calculated rocket distance traveled in feet
+*******************************************************************************/
+               
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double accel, velo, dist, time;
+
+   /* Print main headings and column headings */
+   printf("********************************************"
+          "\n\n          ROCKET FLIGHT SIMULATION"
+          "\n\n\nTIME    ACCELERATION    VELOCITY    DISTANCE"
+          "\n(sec)   (ft/sec*sec)    (ft/sec)      (ft)");
+
+   /* Calculate acceleration, velocity, distance, and print results */
+   for(time=0.0;time<=25.0;time++) 
+   {
+      accel = 4.25 - 0.015*pow(time,2);
+      velo = 4.25*time - .005*pow(time,3);
+      dist = 90.0 + 2.125*pow(time,2) - 0.00125*pow(time,4);
+      printf("\n%4.1f     %7.2f        %7.2f    %8.2f",
+             time, accel, velo, dist);
+   }
+   printf("\n********************************************\n\n\n");
+     
+   /* Exit program */
+   return 0;
+}
+/******************************************************************************/
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Rocket_While_Loop.cpp

@@ -1,0 +1,59 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES THE "while" LOOP STRUCTURE
+
+                        while(condition)
+                        {
+                           statements;
+                        }
+                         
+PROGRAM DESCRIPTION:
+This program simulates rocket flight by calculating distance, velocity, and
+acceleration, where time is in seconds with increments of one second.  The
+results are printed to the computer screen.
+ 
+DESCRIPTION OF VARIABLES:
+NAME  | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+time  | double | time in seconds 
+accel | double | calculated rocket acceleration in ft/sec^2
+velo  | double | calculated rocket velocity ft/sec
+dist  | double | calculated rocket distance traveled in feet
+*******************************************************************************/
+               
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double accel, velo, dist, time=0.0;
+   
+   /* Print main headings and column headings */
+   printf("********************************************"
+          "\n          ROCKET FLIGHT SIMULATION"
+          "\n\nTIME    ACCELERATION    VELOCITY    DISTANCE"
+          "\n(sec)    (ft/sec^2)     (ft/sec)      (ft)");
+
+   /* Calculate acceleration, velocity, distance, and print results */
+   while(time <= 25.0)
+   {
+      accel = 4.25 - 0.015*pow(time,2);
+      velo = 4.25*time - .005*pow(time,3);
+      dist = 90.0 + 2.125*pow(time,2) - 0.00125*pow(time,4);
+      printf("\n%4.1f     %7.2f        %7.2f    %8.2f",
+             time, accel, velo, dist);
+      time = time+1.0;
+   }
+   printf("\n********************************************\n\n\n");
+   
+   /* Exit program */
+   return 0;
+}
+/******************************************************************************/
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Rocket_Write_to_File.cpp

@@ -1,0 +1,75 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES WRITING TO AN OUTPUT FILE USING THE file, fopen,
+      fprintf, AND fclose statements.
+
+PROGRAM DESCRIPTION:
+This program simulates rocket flight by calculating distance, velocity, and
+acceleration, where time is in seconds with increments of one second.  The
+results are printed to the computer screen and to an output file.
+
+DESCRIPTION OF VARIABLES:
+NAME  | TYPE   | DESCRIPTION
+--------------------------------------------------------------------------------
+time  | double | time in seconds
+accel | double | rocket acceleration in ft/sec^2
+velo  | double | rocket velocity in ft/sec
+dist  | double | rocket distance traveled in feet
+*******************************************************************************/
+               
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define outputfile "u:\\engr 200\\rocket_flight.txt"
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double accel, velo, dist, time;
+   FILE *rocket;
+   
+   /* Open output file */
+   rocket = fopen(outputfile,"w");
+   
+   /* Print main headings to computer screen and output file */
+   printf("********************************************");
+   printf("\n          ROCKET FLIGHT SIMULATION\n\n"
+          "TIME    ACCELERATION    VELOCITY    DISTANCE\n"
+          "(sec)    (ft/sec^2)     (ft/sec)      (ft)");
+   fprintf(rocket,"********************************************");
+   fprintf(rocket,"\n          ROCKET FLIGHT SIMULATION\n\n"
+          "TIME    ACCELERATION    VELOCITY    DISTANCE\n"
+          "(sec)    (ft/sec^2)     (ft/sec)      (ft)");
+                 
+   /* Calculate and print results to computer screen and output file */
+   for(time=0.0; time<=25.0; time++)
+   {
+      accel = 4.25 - 0.015*pow(time,2);
+      velo = 4.25*time - .005*pow(time,3);
+      dist = 90.0 + 2.125*pow(time,2) - 0.00125*pow(time,4);
+      printf("\n%4.1f     %7.2f       %7.2f     %8.2f",
+             time, accel, velo, dist);
+     fprintf(rocket,"\n%4.1f     %7.2f       %7.2f     %8.2f",        
+     		 time, accel, velo, dist);
+   }
+   printf("\n********************************************\n\n\n");
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Train_1.cpp

@@ -1,0 +1,52 @@
+/*******************************************************************************
+DEMO: DEVELOPING A "C" PROGRAM
+
+PROGRAM DESCRIPTION:
+This program will calculate the centrifugal force of a train traveling around a
+level curved track.  The results are printed to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE  | DESCRIPTION 
+--------------------------------------------------------------------------------
+force   | float | calculated centrifugal force in pounds
+weight  | float | weight of the train in tons
+speed   | float | speed of the train in miles per hour
+radius  | float | radius of the track curve in feet
+gravity | float | gravitation constant (ft/s/s)
+*******************************************************************************/
+   
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+
+/* Main function */
+int main(void)
+{
+  /* Declare and initialize variables */
+  float force,weight=150.0,speed=65.2,radius=2640.0,gravity=32.0;
+  
+  /* Compute centrifugal force */
+  force=((weight*2000.0)/gravity)*(((speed*1.4667)*(speed*1.4667))/radius);
+   
+  /* Print weight, speed, radius, and force */
+  printf("%f   %f   %f   %f",weight,speed,radius,force);
+  
+  /* Exit program */
+  return 0;
+}
+/******************************************************************************/
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Train_2.cpp

@@ -1,0 +1,75 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES INPUT AND OUTPUT
+
+PROGRAM DESCRIPTION:
+This program will prompt the user to enter the weight of the train, the speed of
+the train, and the radius of the track curve.  It will calculate the centrifugal
+force of a train traveling around a level curved track.  The results are printed
+to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME    | TYPE     | DESCRIPTION 
+--------------------------------------------------------------------------------
+force   | double   | calculated centrifugal force in pounds
+weight  | double   | weight of the train in tons
+speed   | double   | speed of the train in miles per hour
+radius  | double   | radius of the track curve in feet
+gravity | symbolic | gravitation constant in ft/s/s
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define gravity 32.0
+
+/* Main function */
+int main(void)
+{
+  /* Declare variables */
+  double force, weight, speed, radius;
+
+  /* Print main heading */
+  printf("*****************************************");
+  printf("\n        CENTRIFUGAL FORCE PROGRAM");
+             
+  /* Enter weight, speed, radius */
+  printf("\n\nEnter weight of train in tons      : ");
+  scanf("%lf",&weight);
+  printf("Enter speed of train in mph        : ");
+  scanf("%lf",&speed);
+  printf("Enter radius of track curve in feet: ");
+  scanf("%lf",&radius);
+             
+  /* Compute centrifugal force */
+  force = (weight*2000.0/gravity)*pow(speed*1.4667,2)/radius;
+  	  
+  /* Print weight, speed, radius, and force */
+  printf("\n\nRESULTS");
+  printf("\nWeight of train   = %7.1f tons",weight);
+  printf("\nSpeed of train    = %7.1f mph",speed);
+  printf("\nRadius of curve   = %7.1f feet",radius);
+  printf("\nCentrifugal force = %7.1f pounds",force);
+  printf("\n*****************************************\n\n\n");
+        
+  /* Exit program */
+  return 0;
+}
+/******************************************************************************/
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/Demo_Trig_For_Loop_With_if.cpp

@@ -1,0 +1,68 @@
+/*******************************************************************************
+DEMO: THIS PROGRAM DEMONSTRATES THE "for" LOOP AND NESTED "if/else" STRUCTURE
+
+         for(expression_1;expression_2;expression_3)
+         {
+            statements;
+         }
+
+PROGRAM DESCRIPTION:
+This program calculates sine, cosine, and tangent values based on an angle in
+degrees.  The results are printed to the computer screen.
+
+DESCRIPTION OF VARIABLES:
+NAME     | TYPE     | DESCRIPTION
+--------------------------------------------------------------------------------
+angle    | double   | angle in degress
+sine     | double   | calculated sine value of angle
+cosine   | double   | calculated cosine value of angle
+tangent  | double   | calculated tangent value of angle
+radians  | double   | conversion of degrees to radians
+pi       | symbolic | mathematical constant
+*******************************************************************************/
+
+/* Preprocessor directives */
+#include <stdio.h>
+#include <math.h>
+#define pi 3.14159
+
+/* Main function */
+int main(void)
+{
+   /* Declare variables */
+   double sine, cosine, tangent, radians, angle=0.0;
+   int i; 
+   
+   /* Print main headings and column headings */
+   printf("*****************************************"
+          "\n          TABLE OF TRIG VALUES"
+          "\n\n Angle      Sine      Cosine     Tangent");
+
+   /* Calculate and print output results */   
+   for(i=1; i<=37; i++)
+   {
+      radians = angle*pi/180.0;
+      sine = sin(radians);
+      cosine = cos(radians);
+      tangent = tan(radians);
+      
+      
+      
+      if(radians < pi/2.0 || radians > pi/2.0)
+         printf("\n %5.1f    %7.4f    %7.4f     %7.4f",angle,sine,cosine,
+		       tangent);
+	  else
+		 printf("\n%5.1f    %7.4f    %7.4f     UNDEFINED",angle,sine,cosine);
+		 
+		 
+		 
+		 
+	  angle+=5.0;	 
+	}
+   printf("\n*****************************************\n\n\n");
+  
+   /* Exit program */
+   return 0;
+}
+/******************************************************************************/
+

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/power_plant_matlab_demo.m

@@ -1,0 +1,84 @@
+%**************************************************************************
+%MATLAB DEMO USING A TWO-DIMENSIONAL MATRIX
+   
+%PROGRAM DESCRIPTION:
+%This program will compute the average power output of a two-dimensional
+%power matrix.  The program will determine the minimum power, the maximum
+%power, the row and column location of the minimum power, and the row and
+%column location of the maximum power.  The results are printed to the
+%Command Window and to an output file.
+
+%DESCRIPTION VARIABLES:
+%NAME        | TYPE   | DESCRIPTION
+%--------------------------------------------------------------------------
+%power_plant | double | two-dimensional matrix of power in megawatts
+%nrows       | double | number of rows in the matrix
+%ncols       | double | number of columns in the matrix
+%minpow      | double | minimum power output
+%maxpow      | double | maximum power output
+%avepow      | double | calculated average power
+%minrow      | double | row location of minimum power
+%mincol      | double | column location of minimum power
+%maxrow      | double | row location of maximum power
+%maxcol      | double | column location of maximum power
+%m           | double | outer loop control variable
+%n           | double | inner loop control variable
+%outputfile  | char   | file location of printed output
+%**************************************************************************
+
+%Clear Command Window, clear memory, and close plots
+clc
+clear
+close all
+
+%Load input file
+load power_plant_data.txt;
+
+%Open outputfile
+outputfile = fopen('power_plant_report.txt','wt');
+
+%Size array
+[nrows,ncols] = size(power_plant_data);
+
+%Compute average power, find minimum and maximum power
+minpow = min(power_plant_data(:));
+maxpow = max(power_plant_data(:));
+avepow = mean(power_plant_data(:));
+
+%Find minimum and maximum power locations in array
+[minrow,mincol] = find(power_plant_data == minpow);
+[maxrow,maxcol] = find(power_plant_data == maxpow);
+
+%Print to Command Window
+disp('*********************************************');
+disp('          POWER OUTPUT IN MEGAWATTS');
+disp(' ');
+disp('  Day1  Day2  Day3  Day4  Day5  Day6  Day7');
+disp(power_plant_data);
+fprintf('Minimum power = %3i megawatts at week %1i, day %1i', ...
+        minpow,minrow,mincol);
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/rocket_matlab_demo.m

@@ -1,0 +1,70 @@
+%**************************************************************************
+%MATLAB DEMO USING MATRIX MULTIPLICATION, MATRIX WITHIN MATRIX, AND
+%MULTI-VARIABLE PLOTTING
+%   
+%PROGRAM DESCRIPTION:
+%This program will compute distance, velocity, and acceleration of a rocket
+%as time varies from 0 to 25 seconds in one second intervals.  The program
+%will plot the curves of distance, velocity, and acceleration vs time.  The
+%results are printed to the Command Window and to an output file.
+%
+%DESCRIPTION VARIABLES:
+%NAME        | TYPE   | DESCRIPTION
+%--------------------------------------------------------------------------
+%outputfile  | char   | file location of printed output
+%time        | double | one-dimensional matrix of time in seconds
+%accl        | double | one-dimensional matrix of acceleration in ft/sec^2
+%velo        | double | one-dimensional matrix of velocity in ft/sec
+%dist        | double | one-dimensional matrix of distance in ft
+%**************************************************************************
+
+%Clear Command Window, clear memory, and close plots
+clc
+clear
+close all
+
+%Open output file
+outputfile = fopen('rocket_output.txt','wt');
+
+%Print headings to Command Window
+disp('****************************************************************');
+disp('                    ROCKET FLIGHT SIMULATION');
+disp(' ');
+disp('          TIME   ACCELERATION   VELOCITY     DISTANCE');
+disp('          (sec)   (ft/sec^2)    (ft/sec)       (ft)');
+
+%Print headings to output file
+fprintf(outputfile,'**************************************************');
+fprintf(outputfile,'**************\n');
+fprintf(outputfile,'%44s\r\n\n%53s\r\n%51s','ROCKET FLIGHT SIMULATION',...
+        'TIME    ACCELERATION     VELOCITY      DISTANCE',...
+        '(sec)   (ft/sec*sec)     (ft/sec)        (ft)');
+
+%Compute distance, velocity, acceleration, and print results
+time = 0:1:25;
+dist = 90.0+2.125*time.^2-0.00125*time.^4;
+velo = 4.25*time-0.005*time.^3;
+accel = 4.25-0.015*time.^2;
+disp([time',accel',velo',dist']);
+flight = [time;accel;velo;dist];
+fprintf(outputfile,'\r\n %2i       %6.2f          %6.2f        %6.2f',...
+        flight);
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/temperature_matlab_demo.m

@@ -1,0 +1,81 @@
+%**************************************************************************
+%MATLAB DEMO USING A TWO-DIMENSIONAL MATRIX AND PLOTTING
+%   
+%PROGRAM DESCRIPTION:
+%This program will load experimental time and temperature data into a two-
+%dimensional matrix.  It will compute the summations of time, temperature,
+%time squared, and time x temperature values.  The program will compute the
+%slope and y-intercept of a linear equation and plot the experimental data 
+%and the linear equation to a graph.  The results are printed to the
+%Command Window and an x-y plot is generated.
+%
+%DESCRIPTION VARIABLES:
+%NAME        | TYPE   | DESCRIPTION
+%--------------------------------------------------------------------------
+%concrete    | double | two-dimensional array of time and temperature
+%sumtime     | double | summation of all time values
+%sumtemp     | double | summation of all temperature values
+%sumtimesq   | double | summation of all time squared values
+%sumtimetemp | double | summation of all time x temperature values
+%slope       | double | computed slope
+%yint        | double | computed y-intercept
+%computed    | double | one-dimensional array linear equation
+%nrows       | double | number of rows in the input file
+%ncols       | double | number of columns in the input file
+%**************************************************************************
+
+%Clear Command Window, clear memory, and close plots
+clc
+clear
+close all
+
+%Load input file
+load concrete.txt;
+
+%Size matrix
+[nrows,ncols] = size(concrete);
+
+%Compute summations
+sumtime = sum(concrete(:,1));
+sumtemp = sum(concrete(:,2));
+sumtimesq = sum(concrete(:,1).^2);
+sumtimetemp = sum(concrete(:,1).*concrete(:,2));
+
+%Compute slope and y-intercept
+slope = (sumtime*sumtemp - nrows*sumtimetemp)/...
+        (sumtime^2 - nrows*sumtimesq);
+yint = (sumtemp - slope*sumtime)/nrows;
+
+%Compute linear data
+computed = slope*concrete(:,1)+yint;
+
+%Print headings to the Command Window
+disp('************************************************');
+disp('    EXPERIMENTAL PROCESS TEMPERATURE CONTROL');
+disp(' ');
+disp('         Time     Temp     Computed');
+
+%Print results to Command Window
+for k=1:1:nrows
+    fprintf('        %5.1f    %5.1f        %5.1f\n',concrete(k,1),...
[…]

### 2020-02-13 past_classes/complete/engr_200/Previous Demos/train_matlab_demo.m

@@ -1,0 +1,70 @@
+%**************************************************************************
+%MATLAB DEMO PROGRAM
+%   
+%PROGRAM DESCRIPTION:
+%This program will calculate the centrifugal force of a train traveling
+%around a level curved track.  The weight and radius are entered through
+%the keyboard, and the matrix speed is loaded from the input file.  The
+%computed results are printed to the command window and to an output file.
+%The program will stop executing if an incorrect radius is entered.
+%
+%DESCRIPTION VARIABLES:
+%NAME         | TYPE   | DESCRIPTION
+%--------------------------------------------------------------------------
+%train_speeds | double | one-dimensional matrix of speeds in miles/hour
+%weight       | double | weight of train in tons
+%radius       | double | radius of track curve in feet
+%force        | double | calculated centrifugal force in pounds
+%gravity      | double | gravitation acceleration in ft/s^2
+%outputfile   | char   | file location of printed output
+%**************************************************************************
+
+%Clear Command Window, memory, and plots
+clc
+clear
+close all
+
+%Load input file
+load train_speeds.txt;
+
+%Open output file
+outputfile = fopen('train_report.txt','wt');
+
+%Initialize gravity variable
+gravity = 32;
+
+%Print main heading
+fprintf('**************************************');
+fprintf('\n      CENTRIFUGAL FORCE PROGRAM\n\n');
+fprintf(outputfile,'**************************************');
+fprintf(outputfile,'\n      CENTRIFUGAL FORCE PROGRAM\n\n');
+%Enter train weight and track radius
+weight = input('Enter train weight in tons: ');
+radius = input('Enter track radius in feet: ');
+
+%Print column headings
+fprintf('\nSpeed     Weight     Radius      Force');
+fprintf('\n(mph)     (tons)      (ft)       (lbs)');
+fprintf(outputfile,'\nSpeed     Weight     Radius      Force');
+fprintf(outputfile,'\n(mph)     (tons)      (ft)       (lbs)');
+
+%Verify radius of track curve
+while radius < 2640 || radius > 7920
+    clc;
+    fprintf('\n\nRadius error occurred\n\n');
+    radius = input('Enter track radius in feet: ');
+end
+
+%Compute centrifugal forces and print table
+for k=1:1:length(train_speeds)
+    force = (weight*2000/gravity)*(train_speeds(k)*1.4667^2)/radius;
+    fprintf('\n %4.1f     %5.1f     %6.1f    %7.1f',train_speeds(k),...
[…]

### 2020-02-13 research/moa-release-2019.05.0/doc/apidocs/package-search-index.js
Removed old MOA jar files that are not useful anymore
Signed-off-by: Haataja <grant.haataja@undcemlh110-07l.ad.und.edu>

@@ -1,1 +1,0 @@
-packageSearchIndex = [{"l":"com.github.javacliparser"},{"l":"com.github.javacliparser.gui"},{"l":"com.yahoo.labs.samoa.instances"},{"l":"moa"},{"l":"moa.capabilities"},{"l":"moa.classifiers"},{"l":"moa.classifiers.active"},{"l":"moa.classifiers.active.budget"},{"l":"moa.classifiers.bayes"},{"l":"moa.classifiers.core"},{"l":"moa.classifiers.core.attributeclassobservers"},{"l":"moa.classifiers.core.conditionaltests"},{"l":"moa.classifiers.core.driftdetection"},{"l":"moa.classifiers.core.splitcriteria"},{"l":"moa.classifiers.core.statisticaltests"},{"l":"moa.classifiers.drift"},{"l":"moa.classifiers.functions"},{"l":"moa.classifiers.lazy"},{"l":"moa.classifiers.lazy.neighboursearch"},{"l":"moa.classifiers.lazy.neighboursearch.kdtrees"},{"l":"moa.classifiers.meta"},{"l":"moa.classifiers.multilabel"},{"l":"moa.classifiers.multilabel.core.splitcriteria"},{"l":"moa.classifiers.multilabel.meta"},{"l":"moa.classifiers.multilabel.trees"},{"l":"moa.classifiers.multitarget"},{"l":"moa.classifiers.multitarget.functions"},{"l":"moa.classifiers.oneclass"},{"l":"moa.classifiers.rules"},{"l":"moa.classifiers.rules.core"},{"l":"moa.classifiers.rules.core.anomalydetection"},{"l":"moa.classifiers.rules.core.anomalydetection.probabilityfunctions"},{"l":"moa.classifiers.rules.core.attributeclassobservers"},{"l":"moa.classifiers.rules.core.changedetection"},{"l":"moa.classifiers.rules.core.conditionaltests"},{"l":"moa.classifiers.rules.core.splitcriteria"},{"l":"moa.classifiers.rules.core.voting"},{"l":"moa.classifiers.rules.driftdetection"},{"l":"moa.classifiers.rules.errormeasurers"},{"l":"moa.classifiers.rules.featureranking"},{"l":"moa.classifiers.rules.featureranking.messages"},{"l":"moa.classifiers.rules.functions"},{"l":"moa.classifiers.rules.meta"},{
[…]

### 2020-02-13 research/moa-release-2019.05.0/doc/apidocs/type-search-index.js

@@ -1,1 +1,0 @@
-typeSearchIndex = [{"p":"moa.streams.generators.cd","l":"AbruptChangeGenerator"},{"p":"moa.classifiers.rules","l":"AbstractAMRules"},{"p":"moa.classifiers.rules.multilabel.functions","l":"AbstractAMRulesFunctionBasicMlLearner"},{"p":"moa.classifiers.rules.core.anomalydetection","l":"AbstractAnomalyDetector"},{"p":"moa.clusterers.outliers.AbstractC","l":"AbstractC"},{"p":"moa.clusterers.outliers.AbstractC","l":"AbstractCBase"},{"p":"moa.classifiers.core.driftdetection","l":"AbstractChangeDetector"},{"p":"moa.classifiers","l":"AbstractClassifier"},{"p":"com.github.javacliparser","l":"AbstractClassOption"},{"p":"moa.options","l":"AbstractClassOption"},{"p":"moa.clusterers","l":"AbstractClusterer"},{"p":"moa.streams.generators.cd","l":"AbstractConceptDriftGenerator"},{"p":"moa.classifiers.rules.core.voting","l":"AbstractErrorWeightedVote"},{"p":"moa.classifiers.rules.multilabel.core.voting","l":"AbstractErrorWeightedVoteMultiLabel"},{"p":"moa.classifiers.rules.featureranking","l":"AbstractFeatureRanking"},{"p":"moa.gui.visualization","l":"AbstractGraphAxes"},{"p":"moa.gui.visualization","l":"AbstractGraphCanvas"},{"p":"moa.gui.visualization","l":"AbstractGraphPlot"},{"p":"moa.clusterers.macro","l":"AbstractMacroClusterer"},{"p":"moa","l":"AbstractMOAObject"},{"p":"moa.classifiers.rules.multilabel.errormeasurers","l":"AbstractMultiLabelErrorMeasurer"},{"p":"moa.classifiers","l":"AbstractMultiLabelLearner"},{"p":"moa.streams.filters","l":"AbstractMultiLabelStreamFilter"},{"p":"moa.classifiers.rules.multilabel.errormeasurers","l":"AbstractMultiTargetErrorMeasurer"},{"p":"com.github.javacliparser","l":"AbstractOption"},{"p":"moa.options","l":"AbstractOptionHandler"},{"p":"moa.recommender.rc.data","l":"AbstractRecomme
[…]

### 2020-02-13 research/moa-release-2019.05.0/examples/moa/classifiers/DecisionStumpTutorial.java

@@ -1,122 +1,0 @@
-package moa.classifiers;
-
-import com.github.javacliparser.FlagOption;
-import com.github.javacliparser.IntOption;
-import moa.classifiers.core.AttributeSplitSuggestion;
-import moa.classifiers.core.attributeclassobservers.AttributeClassObserver;
-import moa.classifiers.core.attributeclassobservers.GaussianNumericAttributeClassObserver;
-import moa.classifiers.core.attributeclassobservers.NominalAttributeClassObserver;
-import moa.classifiers.core.splitcriteria.SplitCriterion;
-import moa.core.AutoExpandVector;
-import moa.core.DoubleVector;
-import moa.core.Measurement;
-import moa.options.ClassOption;
-import com.yahoo.labs.samoa.instances.Instance;
-
-public class DecisionStumpTutorial extends AbstractClassifier implements MultiClassClassifier {
-
-	private static final long serialVersionUID = 1L;
-
-	public IntOption gracePeriodOption = new IntOption("gracePeriod", 'g',
-			"The number of instances to observe between model changes.",
-			1000, 0, Integer.MAX_VALUE);
-
-	public FlagOption binarySplitsOption = new FlagOption("binarySplits", 'b',
-			"Only allow binary splits.");
-
-	public ClassOption splitCriterionOption = new ClassOption("splitCriterion",
-			'c', "Split criterion to use.", SplitCriterion.class,
-			"InfoGainSplitCriterion");
-
-	protected AttributeSplitSuggestion bestSplit;
-
-	protected DoubleVector observedClassDistribution;
-
-	protected AutoExpandVector<AttributeClassObserver> attributeObservers;
-
-	protected double weightSeenAtLastSplit;
-
-	public boolean isRandomizable() {
-		return false;
-	}
-
-	@Override
-	public void resetLearningImpl() {
-		this.bestSplit = null;
-		this.observedClassDistribution = new DoubleVector();
-		this.attributeObservers = new AutoExpandVector<AttributeClassObserver>();
-		this.weightSeenAtLastSplit = 0.0;
-	}
-
-	@Override
-	public void trainOnInstanceImpl(Instance inst) {
-		this.observedClassDistribution.addToValue((int) inst.classValue(), inst
-				.weight());
-		for (int i = 0; i < inst.numAttributes() - 1; i++) {
-			int instAttIndex = modelAttIndexToInstanceAttIndex(i, inst);
[…]

### 2020-08-26 Records/scholarships/personal-statement.tex
Cleaned up old stuff and created 451 folder
Signed-off-by: Haataja <grant.haataja@undcemlh112-29l.cem.und.edu>

--- 2019-01-31 personal-statement.tex
@@
 My parents make enough money to prevent me from receiving financial aid, but not enough for them to help me pay for my school.
-I have worked summer internships for up to 100 hours a week, I have had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.
+I have worked summer internships for up to 100 hours a week, had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.
 

### 2020-08-26 Records/scholarships/resume2.tex
Cleaned up old stuff and created 451 folder
Signed-off-by: Haataja <grant.haataja@undcemlh112-29l.cem.und.edu>

--- 2019-02-05 resume.tex
@@
 \subsection{University of North Dakota:}
-Double major in Computer Science and Mathematics with a current cumulative GPA of 3.80. Expected Graduation Date: 12/2020
+Double major in Computer Science and Mathematics with a current cumulative GPA of 3.75. Expected Graduation Date: 12/2020
 
@@
 \subsection{Association of Computing Machinery:}
-Participate in regional programming competitions
+Acting president of club, organizing meetings and training and participating in regional programming competitions
 
@@
 \textbf{Math Tutor:} Helping students learn math concepts such as college algebra, calculus, discrete math, differential equations, set theory and logic, and abstract algebra
-
-\subsubsection{Helix Wine \& Bites (01/18/19 - Current)} 
-\textbf{Bartender/Server:} Providing exceptional food and drink service to customers
 

### 2020-08-26 Records/scholarships/statement_of_purpose.tex
Cleaned up old stuff and created 451 folder
Signed-off-by: Haataja <grant.haataja@undcemlh112-29l.cem.und.edu>

--- 2020-08-26 Records/scholarships/personal-statement.tex
@@
 %header of document
-\title{Personal Statement}
+\title{Statement of Purpose}
 \author{Grant Haataja}
@@
 That is why I have chosen to study Mathematics and Computer Science, whose very foundations are built on problem solving.
-My greatest interest is to study and research coding theory, which lies directly at the intersection of Math and Computer Science.
+My greatest interest is to study and research cutting-edge technologies for ciphers and cybersecurity, which lie directly at the intersection of Math and Computer Science.
 With a strong background in both subjects, I feel that I can bring a broader perspective to my research.
@@
 I am currently working 2 jobs for a total of around 40 hours per week, while taking 16 credits and acting as co-lead of the software development team for Advanced Rocketry Club on campus.
-The US MASTER scholarship would help immensely to take some of my workload stress off my shoulders and allow me to focus more deeply on my classes and exciting research opportunities.
+The NYIT REU program would be an exciting research opportunity for the summer where I could cut down on my responsibilities in order to focus exclusively on research and learning of topics I am fascinated with.
 
-My career goals are to graduate with a double major and research experience, work in my field to learn real-world applications and provide service to society, and eventually return to graduate school and become a professor at a university so I can continue to pursue my passion for Math and research, as well as help other students reach their full potential.
+My career goals are to graduate with a double major and research experience, work in my field to learn real-world applications and provide service to society, and eventually return to graduate school and become a professor at a university so I can continue to pursue my passion for cybersecurity and research, as well as help other students reach their full potential.
 
